### 2018-10-31 GSV-comment-brief.Rmd
Initial commit

---
title: "Lies and the lying liars who tell them: comment on Garbarino, Slonim and Villeval (2018)"
author: "David Hugh-Jones"
date: "`r Sys.Date()`"
output:
  bookdown::tufte_html2: 
    pandoc_args: ['--self-contained']
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: 
    pandoc_args: ['--self-contained']
bibliography: bibliography.bib
link-citations: yes
---

@Garbarino2018 -- GSV from here on -- introduce a method to estimate the prevalence of lying in coin flip style experiments,
where participants are paid for reporting a high outcome of a random variable, such as heads on a coin flip, 
and where the true coin outcome is not observed. The input of the method is the number of "heads" 
reports, $R$, from a sample of size $N$, along with the probability $P$ of the *low* outcome on
the random variable. They claim that their method can estimate the full distribution of
lying outcomes, and they recommend using it for confidence intervals, hypothesis testing and power 
calculations.

Table 3 of GSV reports Monte Carlo simulations, which show that the probability of a Type II error
can be up to 50 per cent. GSV define a Type II error as the 95% confidence interval not containing
the true value. A 95% confidence interval which only contains the true value 50% of the time
is unusual.

```{r setup, include = FALSE}

library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tufte'))
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(echo = FALSE)
options(huxtable.knitr_output_format = "html")
source("bayesian-heads.R")
suppressPackageStartupMessages({
  library(Hmisc)
  library(magrittr)
  library(dplyr)
  library(purrr)
  library(tidyr)
  library(readr)
  library(ggplot2)
  library(broom)
  library(huxtable)
})

huxtable::set_default_properties(position = "left")
set.seed(19751027)

nreps <- 1000L
rewrite_csv <- FALSE # set to TRUE to (re)create the simulations CSV file
cache_results <- FALSE # FALSE to recalculate all results. TRUE for speed.
```

```{r parameters}

params <-   list(
  N     = c(10, 50, 100, 500),
  Liars = seq(0, 1, 0.1),
  P     = c(.2, .5, .8)
)

ci_levels <- c(90L, 95L, 99L)
```

```{r generate-data, cache = cache_results}

true_data <- tidyr::crossing(
  N     = params$N,
  Liars = params$Liars,
  P     = params$P
)
true_data$Liars <- round(true_data$Liars * true_data$N, 0)

simulate_cointoss <- function (row) {
  row["Liars"] + sum(rbinom(row["N"] - row["Liars"], 1, 1 - row["P"]))
}

results <- replicate(nreps, apply(true_data, 1, simulate_cointoss))

sim_data <- true_data %>%  
      cbind(as_tibble(results)) %>% 
      tidyr::gather("sim", "R", starts_with("V")) %>% 
      mutate(
        sim = as.numeric(sub("^V", "", sim)),
      ) %>% 
      arrange(N, Liars, P)

nci_levels <- length(ci_levels)
sim_data <- sim_data[rep(seq_len(nrow(sim_data)), each = nci_levels), ]
sim_data$CI <- rep(ci_levels, nrow(sim_data)/nci_levels)

sim_data$P <- sim_data$P * 100 # input has to be in %

# algorithm is deterministic so we save time by 
# only printing out distinct lines
sim_output <- sim_data %>% 
      select(N, R, P, CI) %>% 
      distinct()

if (rewrite_csv) {
  readr::write_csv(sim_output, path = "sim-output.csv")

  # the java only lets you select a document from your home directory
  copied_to_home_dir_ok <- file.copy("sim-output.csv", normalizePath("~"), overwrite = TRUE)
  stopifnot(copied_to_home_dir_ok)
  # now run java -jar LyingCalculator.jar from the LyingCalculator directory
}
```

```{r sanity-checks, include = FALSE, cache = cache_results}
sim_data %<>% mutate(
  expected_R = Liars + (1 - P/100) * (N - Liars)
)
summary(lm(R ~ expected_R, sim_data))
sim_data %>% 
      group_by(P, N) %>% 
      do(
        broom::tidy(lm(R ~ expected_R, .))
      ) %>% 
      filter(term == "expected_R")

sim_data$expected_R <- NULL

```

```{r gather-estimates, cache = cache_results}

gsv_estimates <- suppressMessages(readr::read_csv(normalizePath("~/sim-outputOutput.csv")))

sim_est <- left_join(sim_data, gsv_estimates, by = c("N", "R", "P", "CI"))

# work with probs not percentages:
sim_est %<>% 
      mutate(
        LB = LB /100,
        UB = UB / 100,
        EV = EV / 100
      ) %>% 
      rename(
        LB.gsv = LB,
        UB.gsv = UB,
        EV.gsv = EV
      )
```

```{r bayesian-estimates, cache = cache_results}

my_prior <- uniform_prior
# alternative:
# my_prior <- function (N) dbinom(0:N, N, p = 0.5)

bayes_est <- sim_output %>% 
      rowwise() %>% 
      do({
        pstr <- update_prior(
                heads = .$R, 
                N = .$N, 
                P = .$P/100, 
                prior = my_prior(.$N)
              )
        ci <- .$CI / 100
        ci_qs <- c(1/2 - ci/2, 1/2 + ci/2)
        cis <- posterior_quantile(ci_qs, pstr)
        # calculate quantities as prop dishonest
        tibble(
          EV.ubayes = posterior_mean(pstr)/.$N,
          LB.ubayes = cis[1]/.$N, 
          UB.ubayes = cis[2]/.$N
        )
      })
bayes_est <- cbind(sim_output, bayes_est)
sim_est <- left_join(sim_est, bayes_est, by = c("N", "P", "R", "CI"))

```

```{r simple-estimates, cache = cache_results}

heads_to_liars <- function (prop_heads, p) {
  # excess good outcomes reported over what you'd expect: prop_heads - (1 - p)
  # over the expected proportion of outcomes that were bad: p
  # if there's no excess, assume everyone is honest
  pmax(0, (prop_heads - (1 - p)) / p)
}

simple_est <- sim_output %>%
      mutate(
        EV.simple = heads_to_liars(R/N, P/100)
      )

heads_confints <- apply(sim_output, 1, function (row) {
  ci <- binom.test(row["R"], row["N"], conf.level = row["CI"]/100)$conf.int
  res <- heads_to_liars(ci, row["P"]/100)
  names(res) <- c("LB.simple", "UB.simple")
  res
})

simple_est <- cbind(simple_est, t(heads_confints))
sim_est <- left_join(sim_est, simple_est, by = c("N", "P", "R", "CI"))
```

```{r recalculate-gsv-functions}

dist_L_gsv <- function(heads, N, P) {
  # L liars means that T = heads - L
  # T is distributed binomially conditional on being no more than `heads`
  L = 0:heads
  result <- rep(NA_real_, length(L))
  result <- dbinom(heads - L, N, 1 - P) / sum(dbinom(L, N, 1 - P))

  result
}

prop_liars <- function(L, heads, N) {
  stopifnot(all(L <= heads), heads >= 0, heads <= N)
  # for any number of liars L, reported heads, and N:
  # true heads T = heads - L
  # number observing low outcome = N - T
  # proportion lying is L/(N-T)
  T <- heads - L
  prop_lied <- L/(N - T)
  prop_lied[N == T] <- 1 # if everyone saw true heads, then   
                         # we can't estimate how many might have
                         # GSV code solves this by assuming 1

  prop_lied
}

prop_liars_ci_gsv <- function (ci, heads, N, P) {
  stopifnot(0 <= ci, ci <= 1, heads <= N, 0 <= heads, 0 <= P, P <= 1)

  dist_L <- dist_L_gsv(heads, N, P)
  check_posterior(dist_L)
  stopifnot(length(dist_L) == heads + 1)

  pl <- prop_liars(0:heads, heads, N)
  stopifnot(length(pl) == heads + 1)

  pl <- pl[dist_L > 0] # get rid of 0-probability events
  dist_L <- dist_L[dist_L > 0]
  dist_L <- dist_L[order(pl)]
  pl <- sort(pl)

  cdf <- cumsum(dist_L)

  # we know pl is always positive, so represent that:
  cdf <- c(0, cdf)
  pl  <- c(0, pl)

  tail <- (1 - ci)/2
  # lower bound: no more than tail% of probability has less than this
  lb_idx <- max(which(cdf <= tail)) # must exist since cdf starts at 0.
  lb <- pl[lb_idx]

  # upper bound: no more than 1-tail% of probability has more
  ub_idx <- min(which(cdf >= 1 - tail))
  ub <- pl[ub_idx]

  return(c(lb, ub))
}

prop_liars_ev_gsv <- function(heads, N, P) {
  dist_L <- dist_L_gsv(heads, N, P)
  prop_lied <- prop_liars(0:heads, heads, N)
  sum(dist_L * prop_lied)
}

```

```{r recalc-estimates, cache = cache_results}

sim_tmp <- sim_output[, c("R", "N", "P", "CI")]
recalc <- apply(sim_tmp, 1, function (x) {
  x <- c(
    prop_liars_ev_gsv(x["R"], x["N"], x["P"]/100),
    prop_liars_ci_gsv(x["CI"]/100, x["R"], x["N"], x["P"]/100)
  )
  names(x) <- paste0(c("EV", "LB", "UB"), ".recalc")
  x
}) 
sim_tmp <- cbind(sim_tmp, t(recalc))
sim_est <- left_join(sim_est, sim_tmp, by = c("N", "P", "R", "CI"))

```

```{r reshape-results, cache = cache_results}

# reshape to long by method
sim_est %<>%
      tidyr::gather(measure, value, contains(".")) %>% 
      tidyr::extract(measure, into = c("statistic", "method"), regex = "(.*)\\.(.*)") %>% 
      tidyr::spread(statistic, value)

sim_est %<>% mutate(
        true_prop = Liars/N,
        within_ci = true_prop >= LB & true_prop <= UB,
        error     = EV - true_prop,
        error_sq  = error^2
      )

# only use recalc in appendix
sim_est_recalc <- sim_est %>% filter(method %in% c("gsv", "recalc"))
sim_est <- sim_est %>% filter(method != "recalc")
```

I ran simulations to check the overall performance of the GSV confidence intervals. 
For each simulation and confidence interval, I computed whether the confidence interval 
contained the true value. Table \@ref(tab:coverage-overall) shows the results.

```{r coverage-overall}

coverage <- sim_est %>% 
      group_by(method, CI) %>% 
      summarize(mean_in_ci = mean(within_ci))

cov_overall <- coverage %>% 
      ungroup() %>% 
      mutate(
        CI = paste0("CI ", CI, "%"),
        method = recode(method, gsv = "GSV", simple = "Frequentist", ubayes = "Bayesian")
      ) %>% 
      spread(CI, mean_in_ci) %>% 
      arrange(factor(method, levels = c("GSV", "Frequentist", "Bayesian")))

pct_format <- function (x) sprintf("%.1f%%", x * 100)

ht_overall <- as_huxtable(cov_overall, add_colnames = TRUE) %>% 
      set_caption("(#tab:coverage-overall) Proportion of true results within confidence interval.") %>% 
      set_label("tab:coverage-overall") %>% 
      set_number_format(-1, -1, list(pct_format)) %>% 
      theme_article()

ht_just_gsv <- ht_overall[1:2,]
ht_just_gsv[1, 1] <- ""
ht_just_gsv
```

By definition, 95% of 95% confidence intervals ought to contain the true value, on average. GSV
intervals are far from this. The confidence intervals are too narrow. Further analysis shows that
this problem holds across all simulated probabilities of the low outcome $P$, confidence
levels, and sample sizes $N$ (up to 500).^[In the appendix.]

Why does this happen? We can get a clue by running the GSV method when there are 10 reports of 
"heads" out of 10 for a fair coin flip ($R = N = 10, P = 0.5$). The resulting point estimate is that
100% of subjects lied. The upper and lower confidence intervals are also 100%. Really? Can we rule out
that 8 subjects lied, and the two honest subjects both saw heads?

The GSV method works like this. First, given $R$ reports of heads, the probability that a total 
of $T$ heads was observed is calculated as:

\[
Z_{T,R,N,p} = \frac{
  \textrm{binom}(T,N,p)
}{
  \sum^R_{k=0}\textrm{binom}(k,N,p)
}
\]

This is the binomial distribution, truncated at $R$, because by assumption, nobody "lies downward"
and reports tails when they really saw heads.

Next, from $T$ the number of liars is calculated as $R-T$; and the proportion of liars is calculated
as $(R-T)/(N-T)$, because $N-T$ people saw the low outcome and had the chance to lie. Combining this
with the truncated binomial gives a cumulative distribution function of the proportion of liars.
This can then be used to estimate means and confidence intervals.

There are two problems with this approach.

First, if 10 out of 10 heads are reported, you should learn two things. On the one hand, there
are probably many liars in your sample. On the other hand, probably a lot of coins really landed heads.
The probability distribution above does not take account of this. In particular, for $R=N$, 
the equation above reduces to the binomial distribution.

Second, suppose $R = 10$ heads out of 10 are reported, and suppose 9 heads were really observed, $T
= 9$. The proportion of people who actually lied in the sample is indeed 100%. But it is 100% of 1
person -- the only person who saw tails. As an estimate of the proportion of liars in the sample --
i.e. the proportion who would have lied, had they seen tails -- that is very noisy.^[The
true number of liars in the sample is unobserved, and needs to be estimated, even if we are not trying
to make inferences to a larger population.]  The GSV method treats it as certain. In other words, GSV estimates the proportion of lies, rather than the proportion of lying 
liars who tell them. But the latter is the statistic we care about.

Putting these together, for $R = N = 10$, the estimated distribution of liars is calculated as follows:

* With probability $\frac{1}{2^{10}}$, there were really $T = 10$ heads. Nobody lied in the sample,
but the proportion of people who lied *out of those who could*, $\frac{R-T}{N-T}$, is undefined because
nobody got the chance to lie.^[The GSV software seems to resolve this by fixing the proportion of 
lies to 100%.]

* Otherwise, 1 or more people saw tails, and they all lied. The proportion of liars is 100%.

Hence, the lower and upper confidence intervals are all 100%.

```{r disagg-coverage}
disagg <- sim_est %>% 
      filter(method=="gsv") %>% 
      group_by(
        `R/N:` = R/N, N, P, CI
      ) %>% 
      summarize(mean_in_ci = mean(within_ci), prop = n()/nrow(.)) %>% 
      mutate(CI = paste0("CI ", CI, "%")) %>% 
      spread(CI, mean_in_ci) %>% 
      mutate(ok  = `CI 95%` > 0.95)

prop_ok <- disagg %>%  
      ungroup() %>% 
      summarize(prop_ok = sum(prop[ok])) %>% 
      pull(prop_ok)
```

The same problem happens in less extreme form whenever $R$ is high relative to $N$. Table 
\@ref(tab:coverage-rn) shows this by splitting the simulations by $R/N$. When $R/N$ is
less than 0.5, coverage levels are OK. When it is greater than 0.5, they are not. Note that
for fair coin flips, $R/N$ is typically greater than 0.5, in the simulations and in reality.^[
If we disaggregate by $N$, $P$, and $R/N$, 95% confidence intervals achieve their nominal 
coverage level in only `r round(prop_ok*100, 1)`% of cases.]

```{r coverage-rn}
coverage_rn <- sim_est %>% 
      filter(method=="gsv") %>% 
      group_by(
        `R/N:` = factor(Hmisc::cut2(R/N, cuts = c(0, 1/2, 1)), labels = c("< 0.5", "&ge; 0.5"))      
      ) %>% 
      mutate(pct_cases = n()/nrow(.)) %>% 
      group_by(`R/N:`, CI) %>% 
      summarize(mean_in_ci = mean(within_ci), `Pct cases` = pct_cases[1]) %>% 
      mutate(CI = paste0("CI ", CI, "%")) %>% 
      spread(CI, mean_in_ci)

as_huxtable(coverage_rn, add_colnames = TRUE) %>% 
      set_caption("(#tab:coverage-rn) GSV confidence interval coverage by low and high R/N") %>% 
      set_label("tab:coverage-rn") %>% 
      set_escape_contents(2:3, 1, FALSE) %>% 
      set_number_format(-1, -1, list(pct_format)) %>% 
      theme_article()
```

# Alternative methods

Can we do better? There are two alternative methods one might use to calculate confidence intervals.
The first is simply to calculate confidence bounds $\bar{R},\underline{R}$ for the proportion of
heads reported in the population, given the number reported in the sample. One can then back out
confidence bounds for the proportion of liars as $\frac{R - (1-P)}{P}$, as in
@abeler2016preferences.^[Confidence bounds lower than 0 can be set to 0.]  As GSV point out, this
assumes that the sample proportion of high outcomes was equal to its expected proportion. We'll see 
whether this matters.

There are numerous ways to calculate confidence intervals in a test of proportions. See e.g.
@agresti1998approximate. Here, I use the binomial exact test of @clopper1934use, which is 
known to be conservative. I call this the "frequentist" method.

The second method is to use Bayes' rule. Start with a prior probability distribution over
the number of liars $L$, $\textrm{Pr}(L)$. The posterior probability is then:

\[
\textrm{Pr}(L | R; N,P) = \frac{
  \textrm{Pr}(R|L; N,P) \textrm{Pr}(L)
}{
  \sum_{L'=0}^N \textrm{Pr}(R|L'; N,P) \textrm{Pr}(L')
}
\]

where the probability of getting $R$ reports of heads in total for given $L$ is just
the probability that the $N - L$ honest people saw $R - L$ heads:

\[
\textrm{Pr}(R|L; N,P) = \textrm{binom}(R - L, N - L,1 - P)
\]

One can then calculate the proportions of liars as $L/N$. Note that we are now directly estimating
how many liars are in the whole sample $N$, where a liar is someone who always reports heads. From
this, one can derive confidence intervals and expected values in the usual way.

For the estimation here, I used a uniform prior, with $Pr(L) = \frac{1}{N+1}$ for $L$ in  0
to $N$.

Results are shown in Table \@ref(tab:coverage-allmethods). Both
frequentist and  Bayesian methods mostly achieve the nominal confidence level, with
more than 90/95/99% of intervals containing the true value. The exception is the frequentist
99% confidence interval, which is too narrow.

```{r coverage-allmethods}
ht_overall %>% 
      set_caption("(#tab:coverage-allmethods) Coverage levels for GSV and alternative methods")
```

Frequentist confidence intervals could be less accurate when N is low, since that leads to more
sampling variation in the number of true heads. Table \@ref(tab:coverage-N) checks this by looking
separately at simulations with $N=10$ and $N=50$. Frequentist 99% confidence intervals indeed appear
slightly too narrow for this range. Bayesian confidence intervals are fine. Both alternatives
perform much better than the GSV approach.

```{r coverage-N}

coverage_N <- sim_est %>% 
      filter(N <= 50) %>% 
      group_by(method, CI, N) %>% 
      summarize(mean_in_ci = mean(within_ci)) %>% 
      ungroup() %>% 
      mutate(
        CI = paste0("CI ", CI, "%"),
        Method = recode(method, gsv = "GSV", simple = "Frequentist", ubayes = "Bayesian"),
        method = NULL
      ) %>% 
      select(Method, N, CI, mean_in_ci) %>% 
      spread(CI, mean_in_ci) %>% 
      arrange(factor(Method, levels = c("GSV", "Frequentist", "Bayesian")))

as_huxtable(coverage_N, add_colnames = TRUE) %>% 
      set_rowspan(c(2, 4, 6), "Method", 2) %>% 
      set_number_format(-1, contains("CI"), list(pct_format)) %>% 
      set_caption("(#tab:coverage-N) Confidence interval coverage by sample size") %>% 
      set_label("table:coverage-N") %>% 
      theme_article()
```

# Point estimation

We can also compare the accuracy of point estimates of the proportion of liars. Table
\@ref(tab:point-estimates) shows the mean squared error for methods by different $N$. For low $N$,
the best method is Bayesian and the worst is Frequentist, with GSV in between. When $N$ gets large all
methods give about the same estimates and are equally accurate.

The Bayesian method might have an advantage here, since it assumes a uniform prior and the
simulations indeed used a uniform distribution of the proportion of liars $L/N$. In fact, further
analysis reveals that the Bayesian method is best across all specific values of $L/N$ up to
80%.^[When $L/N = 1$, all subjects deterministically report heads, and both Frequentist and
Bayesian point estimates are exactly correct.] So, the Bayesian method is likely to be best unless
one is sure that the true $L/N$ is rather high.

```{r point-estimates}

sim_est %>% 
      filter(CI == 90) %>% 
      group_by(method, N) %>% 
      summarize(mean_sq_error = mean(error_sq)) %>% 
      spread(N, mean_sq_error, sep = ": ") %>% 
      ungroup() %>% 
      mutate(
        method = recode(method, gsv = "GSV", simple = "Frequentist", ubayes = "Bayesian")
      ) %>% 
      as_huxtable(add_colnames = TRUE) %>% 
      set_caption("(#tab:point-estimates) Mean squared errors by method and N") %>% 
      theme_article()
```

# Empirical Bayes

Bayesian estimates are accurate, but rely on a choice of prior.
A non-informative prior is a reasonable choice. Alternatively one might use information
from previous meta-analyses such as @abeler2016preferences. If the sample size is large enough,
the choice of prior should not matter much.

When comparing the dishonesty rates of different groups, a possible approach is to use the
"empirical Bayes" method [@casella1985introduction]. This means that one estimates a common prior
from the pooled data, before updating the prior for each individual group.

```{r hj-data}

load("honesty.RData")
dfr <- dfr %>% 
      filter(heads %in% 1:2, ! is.na(resnat) , age %in% 2:6)

nats <- dfr %>%  
      group_by(resnat) %>% 
      summarize(
        heads = sum(heads==1), 
        N = n(),
        prop_heads = heads/N,
        prop_liars = 2*prop_heads - 1
      )
pooled_prop_liars <- mean(dfr$heads == 1) * 2 - 1

distribs <- apply(nats[, c("heads", "N")], 1, function (r) {
  N <- r["N"]
  update_prior(
      heads = r["heads"],
      N = N,
      P = 0.5, 
      prior = dbinom(0:N, N, p = pooled_prop_liars)
  )
})
names(distribs) <- nats$resnat

nat_means <- sapply(distribs, posterior_mean)
nat_cis <- sapply(distribs, posterior_quantile, q = c(0.025, 0.975))
rownames(nat_cis) <- c("ci.low", "ci.high")

nats <- cbind(nats, t(nat_cis), mean = nat_means)

nats %<>% 
      mutate(
        mean = mean/N,
        ci.low = ci.low/N,
        ci.high = ci.high/N
      ) %>% 
      arrange(mean)

# nats$resnat <- factor(nats$resnat, levels = nats$resnat)
```

For example, @hugh2016honesty estimates the dishonesty rates of 15 nations using a coin flip
experiment. The pooled estimate of the proportion of liars in the sample is given by $2R/N - 1$ = 
`r round(pooled_prop_liars, 2)`. With $N$ = `r nrow(dfr)`, this will not be much affected by 
sampling variation in the number of heads. We can use a binomial distribution with this as the prior.

```{r hj2016-pic, fig.cap = "Posterior means and confidence intervals for proportion dishonest in 15 countries. Crosses are naive estimates."}

ggplot(nats, aes(x = factor(resnat, levels = resnat), y = mean, fill = mean)) +
      geom_col(alpha = 0.8) +
      geom_linerange(aes(ymin = ci.low,ymax = ci.high)) +
      geom_point(aes(y = prop_liars), shape = 4, size = 3) +
      xlab("Nation") + ylab("Prop. liars") +
      viridis::scale_fill_viridis(option = "E", guide = FALSE) + 
      theme_light() +
      coord_flip()

```

Results are shown in Figure \@ref(fig:hj2016-pic), with means and 95% confidence intervals. There
is substantial shrinkage from the "naive" per-country estimates (using $2R/N - 1$). One of the strengths of empirical Bayes,  as @casella1985introduction points out, is that it "anticipates
regression to the mean". In other words, if we start from the prior that everyone is the same,
we will end up believing that the British are less honest, and the Chinese people are more honest,
than the experimental data *per se* suggest.

# Bayesian hypothesis testing

We can also test hypotheses using the Bayesian approach. If two samples are independent, then the 
probability that e.g. the true proportion of liars in sample 1 is smaller than in sample 2 can be
calculated from the marginal distributions in each sample:

\[
\sum_{L = 0}^{N_{1}} \sum_{M=0}^{N_{2}} Pr(L_{1} = L) Pr(L_{2} = M) \;
  \mathbb{1}({\frac{L}{N_{1}} < \frac{M}{N_{2}})}
\]

Table \@ref(tab:country-comparisons) shows Bayesian comparisons for selected countries. Even though
estimates have "shrunk" towards the pooled mean from the naive estimates, differences remain
significant, partly because the pooled prior has made posterior confidence intervals narrower.

```{r country-comparisons}

prob_country_less <- function (ctry1, ctry2) {
  stopifnot(ctry1 %in% nats$resnat, ctry2 %in% nats$resnat)

  prob_first_less <- 0
  N_1 <- nats$N[nats$resnat == ctry1]
  N_2 <- nats$N[nats$resnat == ctry2]
  for (L_1 in seq(0, length.out = length(distribs[[ctry1]]))) {
    for (L_2 in seq(0, length.out = length(distribs[[ctry2]]))) {
      l_1 <- L_1/N_1
      l_2 <- L_2/N_2
      if (l_1 < l_2) {
        prob_first_less <- prob_first_less + 
            (distribs[[ctry1]][L_1 + 1] * distribs[[ctry2]][L_2 + 1])
      }
    }
  }

  return(prob_first_less)
}

ctry_comp <- outer(nats$resnat, nats$resnat, Vectorize(prob_country_less))
diag(ctry_comp) <- NA
rownames(ctry_comp) <- nats$resnat
colnames(ctry_comp) <- nats$resnat

selected <- c("GB", "ZA", "GR", "BR", "CN")
ctry_comp <- ctry_comp[selected, selected]
cc_hux <- as_huxtable(ctry_comp, add_colnames = TRUE, add_rownames = TRUE) %>% 
      set_caption("(#tab:country-comparisons) Bayesian country comparisons. 
            Cells give the probability that row country has fewer liars than column country.") %>% 
      set_label("tab:country-comparisons") %>% 
      set_na_string("--") %>% 
      theme_basic()

cc_hux[1, 1] <- ''

cc_hux
```

# Recommendations

To sum up, these results suggest some simple recommendations when you are analysing a coin flip
style experiment.

1. Do not use the GSV confidence intervals.
2. If your N is reasonably large, say at least 100, you can safely use standard frequentist 
  confidence intervals and tests.
3. If your N is too small for point 2 to apply, it may be too small, since results will 
  depend on methods used and on one's priors.
4. If increasing your N is not possible for whatever reason, consider using Bayesian methods to find
  confidence intervals and point estimates. To estimate differences between subgroups, consider
  empirical Bayes with a prior derived from the pooled sample.

# Appendix

## Methods

Simulations parameters are shown in Table \@ref(tab:params-table).

```{r params-table}

huxtable(
        Parameter = c(
          "Sample size (N)", 
          "Proportion of liars (R/N)", 
          "Probability of bad outcome (P)"
        ),
        Values    = c(
          paste(params$N, collapse = ", "),
          paste(params$Liars, collapse = ", "),
          paste(params$P, collapse = ", ")
        ),
        add_colnames = TRUE
      ) %>% 
      set_caption("(#tab:params-table) Parameter values") %>% 
      theme_article()
```

For each parameter combination, I ran 1000 simulations. All liars always reported heads. Non-liars
reported tails with probability $P$ and heads otherwise.

## More results

The errors in GSV confidence intervals could be due to a programming error rather than to the
algorithm. I could reproduce GSV's expected value to 4 or 5 significant figures by following their
method, but I could not reproduce their confidence intervals. For example, 
when $R = 3, N = 6, P = 0.5$, GSV's Java program gives the upper bound of the 95% confidence 
interval for the proportion of liars as 49.91%. But the possible proportions of liars when there
are $T=0,1,2,3$ true heads, are $(R-T)/(N-T) =$ 
`r paste0(prop_liars(3:0, 3, 6) * 100, "%", collapse = ", ")`.
It may be that some linear interpolation is being done.

Nevertheless, if I use GSV's method as stated, rather than their program, confidence intervals
remain too small, as shown in Table \@ref(tab:coverage-recalc).

```{r coverage-recalc}

coverage_recalc <- sim_est_recalc %>% 
      filter(method == "recalc") %>% 
      group_by(CI) %>% 
      summarize(mean_in_ci = mean(within_ci)) %>% 
      ungroup() %>% 
      mutate(
        CI = paste0("CI: ", CI, "%"),
      ) %>% 
      spread(CI, mean_in_ci)

as_huxtable(coverage_recalc, add_colnames = TRUE) %>% 
      set_caption("(#tab:coverage-recalc) Proportion of true results within confidence interval, recalculated GSV method") %>% 
      set_label("tab:coverage-recalc") %>% 
      set_number_format(-1, everywhere, list(pct_format)) %>% 
      theme_article(header_col = FALSE)

```

Figure \@ref(fig:coverage-pic) shows the proportions of true values within the confidence interval for the GSV method,
split by $N$, $P$ and confidence level. Dashed lines show the nominal confidence level.

Figure \@ref(fig:coverage-grp-pic) splits this still further, by the true proportion of liars within each
simulation. This makes the pattern clear: coverage gets worse as the proportion of liars increases (until 100% where it jumps back up as results become deterministic).

```{r coverage-pic, fig.cap = "GSV confidence interval coverage by confidence level, N and P"}

coverage_treat_gsv <- sim_est %>% 
      filter(method == "gsv") %>% 
      group_by(CI, N, P) %>% 
      summarize(mean_in_ci = mean(within_ci)) %>% 
      ungroup() %>% 
      mutate(
        P = factor(paste0(P, "%")),
        ci = CI,
        CI = paste0(CI, "%")
      )

ggplot(coverage_treat_gsv, aes(P, mean_in_ci, colour = P)) +
      geom_point(size = 2) +  
      geom_hline(aes(yintercept = ci/100), linetype = 2) +
      facet_grid(N ~ CI, labeller = "label_both") +
      xlab("Probability of low outcome (P)") + ylab("Proportion within C.I.")
```

```{r coverage-grp-pic, fig.cap = "GSV confidence interval coverage by confidence level, N, P and true proportion of liars"}

coverage_grp_gsv <- sim_est %>% 
      filter(method == "gsv") %>% 
      group_by(CI, N, Liars, P) %>% 
      summarize(mean_in_ci = mean(within_ci)) %>% 
      ungroup() %>% 
      mutate(
        P = factor(paste0(P, "%")),
        ci = CI,
        CI = paste0(CI, "%")
      )

ggplot(coverage_grp_gsv, aes(Liars/N, mean_in_ci, colour = P)) +
      geom_point() + geom_line() + 
      geom_hline(aes(yintercept = ci/100), linetype = 2) +
      facet_grid(N ~ CI, labeller = "label_both") +
      xlab("True proportion of liars L/N") + ylab("Proportion within C.I.")

```

Figure \@ref(fig:errors-by-true-prop) shows mean squared error by estimation method and 
true proportion of liars in the sample (True $L/N$), for $N$ &le; 50. The Bayesian method is best 
for all values of $L/N$ up to 80%.

```{r errors-by-true-prop, fig.cap = "Errors by method and true proportion of liars, N &le; 50"}
errors_true_prop <- sim_est %>%       
      filter(CI == 90, N <= 50) %>% 
      group_by(method, true_prop) %>% 
      summarize(mean_sq_error = mean(error_sq)) %>% 
      ungroup() %>% 
      mutate(
        method = recode(method, gsv = "GSV", simple = "Frequentist", ubayes = "Bayesian")
      ) %>% 
      rename(`True L/N` = true_prop, Method = method)

ggplot(errors_true_prop, aes(`True L/N`, mean_sq_error, colour = Method)) + 
      geom_line() + 
      geom_point() +
      ylab("Mean square error") + 
      scale_x_continuous(breaks = 0:5/5)
```

```{r errors-disagg, include = FALSE}

errors_disagg <- sim_est %>%       
      filter(CI == 90, N <= 50) %>% 
      group_by(rn = findInterval(R/N, 0:10/10, rightmost.closed = TRUE), N, P, method) %>% 
      summarize(mean_sq_error = mean(error_sq)) %>% 
      mutate(
        method = recode(method, gsv = "GSV", simple = "Frequentist", ubayes = "Bayesian")
      ) %>% 
      rename(`R/N` = rn, Method = method)

ggplot(errors_disagg, aes(`R/N`, mean_sq_error, colour = Method)) + 
      geom_line() + 
      geom_point() +
      ylab("Mean square error") + facet_wrap(~N + P, scales = "free_y")
```

### 2018-10-31 bayesian-heads.R

@@ -1,0 +1,105 @@
+
+#' Calculate the probability of observing `heads`
+#' good outcomes out of `N` total outcomes, conditional
+#' on `L` subjects being liars.
+#'
+#' @param L Number of Liars. Can be a vector.
+#' @param heads Number of heads reported
+#' @param N Total number in sample
+#' @param P Probability of *bad* outcome
+#'
+#' @return
+#' @export
+#'
+#' @examples
+#' prob_report_given_L(0:3, 2, 3, 0.5)
+prob_report_given_L <- function (L, heads, N, P) {
+  stopifnot(all(L <= N), heads <= N)
+  # can't be true if L > heads: liars always report heads
+  result <- rep(NA_real_, length(L))
+  result[L > heads] <- 0
+  # if heads reported out of N, and L are liars
+  # then N-L people flipped a coin; of them heads - L got heads.
+  # coin flip is binomially distributed.
+  # the chance of this is the probability of getting heads - L
+  
+  low_L <- L[L <= heads]
+  result[L <= heads] <- sapply(low_L, function (l) {
+    dbinom(heads - l, size = N - l, prob = 1 - P)
+  })
+
+  return(result)
+}
+
+
+#' Calculate posterior of Ls given prior, and heads reports of good
+#' outcome
+#'
+#' @param L Number of liars. Can be a vector
+#' @param heads Number of heads reported
+#' @param N Total in sample.
+#' @param P Probability of *bad* outcome
+#' @param prior Prior over L. Must be a N+1 length vector that sums to 1. 
+#'   `prior[1]` is the prior probability that L == 0
+#'   `prior[2]` is the prob that L == 1, etc.
+#'
+#' @return
+#' @export
+#'
+#' @examples
+prob_L_given_report <- function(L, heads, N, P, prior) {
+  check_posterior(prior)
+  stopifnot(length(prior) == N + 1)
+  stopifnot(L <= N, L >= 0, heads <= N, heads >= 0, P <= 1, P >= 0)
+
+  evidence <- prob_report_given_L(0:N, heads, N, P)
+  numerator <- prior[L + 1] * evidence[L + 1]
+  denominator <- sum(prior*evidence)
+  
+  return(numerator/denominator)
+}
+
+uniform_prior <- function (N) rep(1/(N + 1), N + 1)
+
+
[…]

### 2018-10-31 bayesian-heads.R
document bayesian-heads.R

@@ -43,10 +43,11 @@ prob_report_given_L <- function (L, heads, N, P) {
 #'   `prior[1]` is the prior probability that L == 0
 #'   `prior[2]` is the prob that L == 1, etc.
 #'
-#' @return
+#' @return A vector of posterior probabilities
 #' @export
 #'
 #' @examples
+#' probs_0_to_10 <- prob_L_given_report(0:10, 13, 20, 0.5, uniform_prior(20))
 prob_L_given_report <- function(L, heads, N, P, prior) {
   check_posterior(prior)
   stopifnot(length(prior) == N + 1)
@@ -59,8 +60,20 @@ prob_L_given_report <- function(L, heads, N, P, prior) {
   return(numerator/denominator)
 }
 
-uniform_prior <- function (N) rep(1/(N + 1), N + 1)
-
+#' Uniform prior on 0 to N
+#' 
+#' Creates a prior with equal probability of every number from 0 to N inclusive.
+#'
+#' @param N sample size
+#'
+#' @return The prior
+#' @export
+#'
+#' @examples
+#' uniform_prior(5)
+uniform_prior <- function (N) {
+  rep(1/(N + 1), N + 1)
+}
 
 #' Update prior distribution given heads/N heads reported
 #' 
@@ -69,10 +82,19 @@ uniform_prior <- function (N) rep(1/(N + 1), N + 1)
 #' @param prior By default, a uniform prior on there being between 
 #'   0 and N liars inclusive.
 #'
-#' @return
+#' @return The updated posterior
 #' @export
 #'
 #' @examples
+#' updated <- update_prior(33, 50, 0.5)
+#' posterior_mean(updated)
+#' posterior_quantile(c(.025, .975), updated)
+#' barplot(updated)
+#' 
+#' # different prior:
+#' updated <- update_prior(33, 50, 0.5, prior = dbinom(0:50, 50, 0.25))
+#' posterior_mean(updated)
+#' posterior_quantile(c(.025, .975), updated)
 update_prior <- function(heads, N, P, prior = uniform_prior(N)) {
   pstr <- prob_L_given_report(0:N, heads = heads, N = N, P = P,
         prior = prior)
@@ -86,13 +108,32 @@ check_posterior <- function(pstr) {
   stopifnot(isTRUE(all.equal(sum(pstr), 1)), all(pstr >= 0))
 }
 
+#' Returns the mean of a discrete distribution
+#'
[…]

### 2018-10-31 bayesian-heads.R
add confidence interval check

@@ -144,3 +144,30 @@ posterior_quantile <- function (q, pstr) {
   return(L_quantiles) 
 }
 
+#' Checks coverage of confidence intervals by simulations
+#'
+#' @param L True number of liars
+#' @param N Sample size
+#' @param P Probability of bad outcome
+#' @param CI Confidence interval between 0 and 1
+#' @param nreps Number of simulations to run
+#' @param prior_fn A one-argument function which returns a N+1 length vector of probabilities
+#'
+#' @return
+#' @export
+#'
+#' @examples
+#' check_ci_coverage(15, 30, P = 0.5)
+#' check_ci_coverage(15, 30, P = 0.5, CI = 0.99)
+check_ci_coverage <- function (L, N, P, CI = 0.95, nreps = 1000, prior_fn = uniform_prior) {
+  tail <- (1 - CI)/2
+  
+  within_ci <- replicate(nreps, {
+    heads <- L + rbinom(1, N - L, prob = 1 - P)
+    pstr <- update_prior(heads, N, P, prior = prior_fn(N))
+    bounds <- posterior_quantile(c(tail, 1 - tail), pstr)
+    bounds[1] <= L && L <= bounds[2] 
+  })
+  
+  return(mean(within_ci))
+}

### 2018-10-31 bayesian-heads.R
tweak

@@ -161,6 +161,7 @@ posterior_quantile <- function (q, pstr) {
 #' check_ci_coverage(15, 30, P = 0.5, CI = 0.99)
 check_ci_coverage <- function (L, N, P, CI = 0.95, nreps = 1000, prior_fn = uniform_prior) {
   tail <- (1 - CI)/2
+  stopifnot(L <= N, P <= 1, P >= 0, CI <= 1, CI >= 0, is.function(prior_fn))
   
   within_ci <- replicate(nreps, {
     heads <- L + rbinom(1, N - L, prob = 1 - P)

### 2018-10-31 GSV-comment-brief.Rmd
Update readme and Rmd

@@
     pandoc_args: ['--self-contained']
+    keep_intermediates: true
   tufte::tufte_handout:
@@
     latex_engine: xelatex
-  tufte::tufte_book:
+  bookdown::tufte_book2:
     citation_package: natbib
     latex_engine: xelatex
-  tufte::tufte_html: 
-    pandoc_args: ['--self-contained']
+    md_extensions: +raw_attribute
 bibliography: bibliography.bib
 link-citations: yes
+abstract: |
+  Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability distribution   of the number of liars in "coin flip" style experiments. However, their method gives 
+  erroneous confidence intervals. I explain why and describe two better
+  ways to calculate probability distributions.
 ---
@@
 rewrite_csv <- FALSE # set to TRUE to (re)create the simulations CSV file
-cache_results <- FALSE # FALSE to recalculate all results. TRUE for speed.
+cache_results <- TRUE # FALSE to recalculate all results. TRUE for speed.
 ```
@@
 how many liars are in the whole sample $N$, where a liar is someone who always reports heads. From
-this, one can derive confidence intervals and expected values in the usual way.
+this, one can derive confidence intervals and expected values in the usual way.^[R code to
+run these calculations is available at https://github.com/hughjonesd/GSV-comment.]
 

### 2018-10-31 GSV-comment-brief.Rmd
update Rmd

@@
 link-citations: yes
-abstract: |
-  Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability distribution   of the number of liars in "coin flip" style experiments. However, their method gives 
-  erroneous confidence intervals. I explain why and describe two better
-  ways to calculate probability distributions.
+
 ---
+
+>  Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability distribution 
+>  of the number of liars in "coin flip" style experiments. However, their method gives 
+>  erroneous confidence intervals. I explain why and describe two better
+>  ways to calculate probability distributions.
 
@@
   confidence intervals and tests.
-3. If your N is too small for point 2 to apply, it may be too small, since results will 
-  depend on methods used and on one's priors.
+3. If your N is too small for point 2 to apply, it may be too small, full stop.
 4. If increasing your N is not possible for whatever reason, consider using Bayesian methods to find

### 2018-11-01 GSV-comment-brief.Rmd
tweak comment

@@
 ---
-title: "Lies and the lying liars who tell them: comment on Garbarino, Slonim and Villeval (2018)"
+title: "Lies, versus the lying liars who tell them: comment on Garbarino, Slonim and Villeval (2018)"
 author: "David Hugh-Jones"
@@
 >  Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability distribution 
->  of the number of liars in "coin flip" style experiments. However, their method gives 
+>  of the number of liars in "coin flip" style experiments. I run simulations showing that their method almost always gives 
 >  erroneous confidence intervals. I explain why and describe two better

### 2018-11-01 GSV-comment-brief.Rmd
Update comment to optionally use proportion of lies as ground truth

@@
 link-citations: yes
-
+editor_options: 
+  chunk_output_type: console
 ---
@@
 cache_results <- TRUE # FALSE to recalculate all results. TRUE for speed.
+estimate_lies_not_liars <- FALSE # if FALSE, use Liars/N as ground truth
+                                # if TRUE, use (R-heads)/(N-heads)
 ```
@@
 simulate_cointoss <- function (row) {
-  row["Liars"] + sum(rbinom(row["N"] - row["Liars"], 1, 1 - row["P"]))
+  h_liars <- rbinom(1, row["Liars"], 1 - row["P"])
+  h_honest <- rbinom(1, row["N"] - row["Liars"], 1 - row["P"])
+  R <- row["Liars"] + h_honest
+  heads <- h_honest + h_liars
+  c(R, heads)
 }
@@
 
+results_R <- results[1, , ]
+results_heads <- results[2, , ]
+colnames(results_R) <- paste0("R", 1:nreps)
+colnames(results_heads) <- paste0("heads", 1:nreps)
+
 sim_data <- true_data %>% 
-      cbind(as_tibble(results)) %>% 
-      tidyr::gather("sim", "R", starts_with("V")) %>% 
-      mutate(
-        sim = as.numeric(sub("^V", "", sim)),
-      ) %>% 
+      cbind(as_tibble(results_R)) %>% 
+      cbind(as_tibble(results_heads)) %>% 
+      gather("stat", "result", starts_with("R"), starts_with("heads")) %>%
+      extract(stat, c("stat", "sim"), regex="(.*?)(\\d+)", convert = TRUE) %>%
+      spread(stat, result) %>%  
       arrange(N, Liars, P)
@@
       tidyr::gather(measure, value, contains(".")) %>% 
-      tidyr::extract(measure, into = c("statistic", "method"), regex = "(.*)\\.(.*)") %>% 
+      tidyr::extract(measure, into = c("statistic", "method"), regex = "(LB|EV|UB)\\.(.*)") %>% 
       tidyr::spread(statistic, value)
 
+# alternative "ground truth" is proportion of lies: (R - heads)/(N - heads)
+if (estimate_lies_not_liars) {
   sim_est %<>% mutate(
-        true_prop = Liars/N,
+          true_prop = (R - heads)/(N - heads)
+        )
+} else {
+  sim_est %<>% mutate(
+          true_prop = Liars/N
+        )
+}
+
+sim_est %<>% mutate(
         within_ci = true_prop >= LB & true_prop <= UB,
@@
       group_by(method, CI) %>% 
-      summarize(mean_in_ci = mean(within_ci))
+      summarize(mean_in_ci = mean(within_ci, na.rm = TRUE))
 
@@
       ) %>% 
-      summarize(mean_in_ci = mean(within_ci), prop = n()/nrow(.)) %>% 
+      summarize(mean_in_ci = mean(within_ci, na.rm = TRUE), prop = n()/nrow(.)) %>% 
       mutate(CI = paste0("CI ", CI, "%")) %>% 
@@
       group_by(`R/N:`, CI) %>% 
-      summarize(mean_in_ci = mean(within_ci), `Pct cases` = pct_cases[1]) %>% 
+      summarize(
+        mean_in_ci  = mean(within_ci, na.rm = TRUE), 
+        `Pct cases` = pct_cases[1]
+      ) %>% 
       mutate(CI = paste0("CI ", CI, "%")) %>% 
@@
       group_by(method, CI, N) %>% 
-      summarize(mean_in_ci = mean(within_ci)) %>% 
+      summarize(mean_in_ci = mean(within_ci, na.rm = TRUE)) %>% 
       ungroup() %>% 
@@
       group_by(method, N) %>% 
-      summarize(mean_sq_error = mean(error_sq)) %>% 
+      summarize(mean_sq_error = mean(error_sq, na.rm = TRUE)) %>% 
       spread(N, mean_sq_error, sep = ": ") %>% 
@@
 
+This approach has a nice interpretation, somewhat analogous
+to the use of the null hypothesis in frequentist methods. We start from the 
+belief that the proportion of liars is the same across all groups. The posterior
+then shows how much the evidence changes this belief.
+
 ```{r country-comparisons}
@@
       group_by(CI) %>% 
-      summarize(mean_in_ci = mean(within_ci)) %>% 
+      summarize(mean_in_ci = mean(within_ci, na.rm = TRUE)) %>% 
       ungroup() %>% 
@@
       group_by(CI, N, P) %>% 
-      summarize(mean_in_ci = mean(within_ci)) %>% 
+      summarize(mean_in_ci = mean(within_ci, na.rm = TRUE)) %>% 
       ungroup() %>% 
@@
       group_by(CI, N, Liars, P) %>% 
-      summarize(mean_in_ci = mean(within_ci)) %>% 
+      summarize(mean_in_ci = mean(within_ci, na.rm = TRUE)) %>% 
       ungroup() %>% 
@@
       group_by(method, true_prop) %>% 
-      summarize(mean_sq_error = mean(error_sq)) %>% 
+      summarize(mean_sq_error = mean(error_sq, na.rm = TRUE)) %>% 
       ungroup() %>% 
@@
 
-ggplot(errors_true_prop, aes(`True L/N`, mean_sq_error, colour = Method)) + 
-      geom_line() + 
-      geom_point() +
+g <- ggplot(errors_true_prop, aes(`True L/N`, mean_sq_error, colour = Method)) + 
       ylab("Mean square error") + 
       scale_x_continuous(breaks = 0:5/5)
+
+# proportion of liars is set to 0:10/10, but of lies is random,
+# so we have to use a smoothing line
+if (estimate_lies_not_liars) g + geom_smooth(method="loess") else 
+      g + geom_line() + geom_point()
+
 ```
@@
       group_by(rn = findInterval(R/N, 0:10/10, rightmost.closed = TRUE), N, P, method) %>% 
-      summarize(mean_sq_error = mean(error_sq)) %>% 
+      summarize(mean_sq_error = mean(error_sq, na.rm = TRUE)) %>% 
       mutate(
@@
 
-ggplot(errors_disagg, aes(`R/N`, mean_sq_error, colour = Method)) + 
-      geom_line() + 
-      geom_point() +
+g <- ggplot(errors_disagg, aes(`R/N`, mean_sq_error, colour = Method)) + 
       ylab("Mean square error") + facet_wrap(~N + P, scales = "free_y")
+
+if (estimate_lies_not_liars) g + geom_smooth(method="loess") else 
+      g + geom_line() + geom_point()
 ```

### 2018-11-01 GSV-comment-brief.Rmd
Alter intro

--- 2018-10-31 GSV-comment-brief.Rmd
@@
 >  Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability distribution 
->  of the number of liars in "coin flip" style experiments. However, their method gives 
+>  of the number of liars in "coin flip" style experiments. However, their method appears 
 >  erroneous confidence intervals. I explain why and describe two better
@@
 
-@Garbarino2018 -- GSV from here on -- introduce a method to estimate the prevalence of lying in coin flip style experiments,
-where participants are paid for reporting a high outcome of a random variable, such as heads on a coin flip, 
-and where the true coin outcome is not observed. The input of the method is the number of "heads" 
-reports, $R$, from a sample of size $N$, along with the probability $P$ of the *low* outcome on
-the random variable. They claim that their method can estimate the full distribution of
+Some people are honest, while others will lie whenever it benefits them. We would like to know the
+prevalence of lying, since a society where many people lie is likely to experience
+economic and social problems. Since we cannot simply ask people if they are liars, one way to
+estimate the proportion of liars in a group is to ask them to report the result of a coin flip or
+other random device, offering them a payment if they report heads. Liars don't always lie: they 
+only lie when it benefits them. So they always report heads irrespective of the true coin flip.
+^[@Garbarino2018 maintain this assumption and so shall I.] If there are many more heads than
+we would expect by chance, we can assume many people are lying. But how many?
+
+A naïve estimate would be that if e.g. 80 people of 100 report heads, then on average 50 really saw
+heads and 60% (30/50) of the remainder are lying. More generally, from $R$ reports of a good outcome
+in a sample of size $N$, where the _bad_ outcome happens with probability $P$, we can estimate that
+a proportion $\frac{R/N - (1-P)}{P}$ are lying [@abeler2016preferences]. The problem with this approach is that the number of heads is not
+fixed. If we see 1 out of 3 people reporting heads, this method estimates there are less than zero
+liars. But it is still possible that everyone saw heads and 1 person lied.
+
+@Garbarino2018 -- GSV from here on -- introduce an alternative method. They claim that their method 
+corrects for this problem and can estimate the full distribution of
 lying outcomes, and they recommend using it for confidence intervals, hypothesis testing and power 
@@
 the true value. A 95% confidence interval which only contains the true value 50% of the time
-is unusual.
+is unusual. What is going on?
 
@@
 cache_results <- TRUE # FALSE to recalculate all results. TRUE for speed.
-```
-
-```{r parameters}
+sample_from_pop <- TRUE # if TRUE, the number of liars in the sample is randomly drawn 
+                        # from a population with `Liars` liars. 
+                        # If FALSE it is fixed at `Liars * N`.
 

### 2018-11-01 GSV-comment-brief.Rmd

--- 2018-11-01 GSV-comment-brief.Rmd
@@
 >  Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability distribution 
->  of the number of liars in "coin flip" style experiments. I run simulations showing that their method almost always gives 
->  erroneous confidence intervals. I explain why and describe two better
+>  of the number of liars in "coin flip" style experiments. However, their method appears 
+>  to give erroneous confidence intervals. I explain why and describe two better
 >  ways to calculate probability distributions.
 
-@Garbarino2018 -- GSV from here on -- introduce a method to estimate the prevalence of lying in coin flip style experiments,
-where participants are paid for reporting a high outcome of a random variable, such as heads on a coin flip, 
-and where the true coin outcome is not observed. The input of the method is the number of "heads" 
-reports, $R$, from a sample of size $N$, along with the probability $P$ of the *low* outcome on
-the random variable. They claim that their method can estimate the full distribution of
+Some people are honest, while others will lie whenever it benefits them. We would like to know the
+prevalence of lying, since a society where many people lie is likely to experience
+economic and social problems. Since we cannot simply ask people if they are liars, one way to
+estimate the proportion of liars in a group is to ask them to report the result of a coin flip or
+other random device, offering them a payment if they report heads. Liars don't always lie: they 
+only lie when it benefits them. So they always report heads irrespective of the true coin flip.
+^[@Garbarino2018 maintain this assumption and so shall I.] If there are many more heads than
+we would expect by chance, we can assume many people are lying. But how many?
+
+A naïve estimate would be that if e.g. 80 people of 100 report heads, then on average 50 really saw
+heads and 60% (30/50) of the remainder are lying. More generally, from $R$ reports of a good outcome
+in a sample of size $N$, where the _bad_ outcome happens with probability $P$, we can estimate that
+a proportion $\frac{R/N - (1-P)}{P}$ are lying [@abeler2016preferences]. The problem with this approach is that the number of heads is not
+fixed. If we see 1 out of 3 people reporting heads, this method estimates there are less than zero
+liars. But it is still possible that everyone saw heads and 1 person lied.
+
+@Garbarino2018 -- GSV from here on -- introduce an alternative method. They claim that their method 
+corrects for this problem and can estimate the full distribution of
 lying outcomes, and they recommend using it for confidence intervals, hypothesis testing and power 
@@
 cache_results <- TRUE # FALSE to recalculate all results. TRUE for speed.
+sample_from_pop <- TRUE # if TRUE, the number of liars in the sample is randomly drawn 
+                        # from a population with `Liars` liars. 
+                        # If FALSE it is fixed at `Liars * N`.
 estimate_lies_not_liars <- FALSE # if FALSE, use Liars/N as ground truth
                                 # if TRUE, use (R-heads)/(N-heads)
-```
-
-```{r parameters}
-
-params <-   list(
-  N     = c(10, 50, 100, 500),
-  Liars = seq(0, 1, 0.1),
-  P     = c(.2, .5, .8)
-)
-
-ci_levels <- c(90L, 95L, 99L)
 ```

### 2018-11-01 GSV-comment-brief.Rmd
Many updates

@@
 ---
-title: "Lies, versus the lying liars who tell them: comment on Garbarino, Slonim and Villeval (2018)"
+title: "Lies and the lying liars who tell them: comment on Garbarino, Slonim and Villeval (2018)"
 author: "David Hugh-Jones"
@@
 output:
-  bookdown::tufte_html2: 
-    pandoc_args: ['--self-contained']
-    keep_intermediates: true
-  tufte::tufte_handout:
-    citation_package: natbib
-    latex_engine: xelatex
   bookdown::tufte_book2:
@@
     md_extensions: +raw_attribute
+  tufte::tufte_handout:
+    citation_package: natbib
+    latex_engine: xelatex
+  bookdown::tufte_html2: 
+    pandoc_args: ['--self-contained']
+    keep_intermediates: true
 bibliography: bibliography.bib
 link-citations: yes
-editor_options: 
-  chunk_output_type: console
 ---
@@
 >  of the number of liars in "coin flip" style experiments. However, their method appears 
->  to give erroneous confidence intervals. I explain why and describe two better
+>  to give erroneous confidence intervals. I explain why, and describe two better
 >  ways to calculate probability distributions.
-
-Some people are honest, while others will lie whenever it benefits them. We would like to know the
-prevalence of lying, since a society where many people lie is likely to experience
-economic and social problems. Since we cannot simply ask people if they are liars, one way to
-estimate the proportion of liars in a group is to ask them to report the result of a coin flip or
-other random device, offering them a payment if they report heads. Liars don't always lie: they 
-only lie when it benefits them. So they always report heads irrespective of the true coin flip.
-^[@Garbarino2018 maintain this assumption and so shall I.] If there are many more heads than
-we would expect by chance, we can assume many people are lying. But how many?
-
-A naïve estimate would be that if e.g. 80 people of 100 report heads, then on average 50 really saw
-heads and 60% (30/50) of the remainder are lying. More generally, from $R$ reports of a good outcome
-in a sample of size $N$, where the _bad_ outcome happens with probability $P$, we can estimate that
-a proportion $\frac{R/N - (1-P)}{P}$ are lying [@abeler2016preferences]. The problem with this approach is that the number of heads is not
-fixed. If we see 1 out of 3 people reporting heads, this method estimates there are less than zero
-liars. But it is still possible that everyone saw heads and 1 person lied.
-
-@Garbarino2018 -- GSV from here on -- introduce an alternative method. They claim that their method 
-corrects for this problem and can estimate the full distribution of
-lying outcomes, and they recommend using it for confidence intervals, hypothesis testing and power 
-calculations.
-
-Table 3 of GSV reports Monte Carlo simulations, which show that the probability of a Type II error
-can be up to 50 per cent. GSV define a Type II error as the 95% confidence interval not containing
-the true value. A 95% confidence interval which only contains the true value 50% of the time
-is unusual. What is going on?
 
@@
 nreps <- 1000L
-rewrite_csv <- FALSE # set to TRUE to (re)create the simulations CSV file
-cache_results <- TRUE # FALSE to recalculate all results. TRUE for speed.
-sample_from_pop <- TRUE # if TRUE, the number of liars in the sample is randomly drawn 
+
+# set to FALSE to recalculate all results; TRUE for speed:
+cache_results <- FALSE
+
+# set to TRUE to (re)create the simulations CSV file:
+rewrite_csv <- FALSE
+
+# if TRUE, the number of liars in each simulation is randomly drawn
 # from a population with `Liars` liars.
-                        # If FALSE it is fixed at `Liars * N`.
-estimate_lies_not_liars <- FALSE # if FALSE, use Liars/N as ground truth
-                                # if TRUE, use (R-heads)/(N-heads)
+# If FALSE, the number of liars is fixed at `Liars * N`.
+# If you change this, you may need to recreate the simulations CSV file
+sample_from_pop <- FALSE
+
+# if FALSE, use L/N as ground truth;
+# if TRUE, use (R-heads)/(N-heads):
+estimate_lies_not_liars <- FALSE
+
+if (sample_from_pop && estimate_lies_not_liars) {
+  stop("Can't estimate proportion of actual lies in population!")
+}
+
+params <-   list(
+  N     = c(10, 50, 100, 500),
+  Liars = seq(0, 1, 0.1),
+  P     = c(.2, .5, .8)
+)
+
+ci_levels <- c(90L, 95L, 99L)
+
+method_used_statement <- paste0("This paper can be recreated from the .Rmd file using different ",
+      "methods to calculate confidence interval coverage and squared errors. 'Ground ",
+      "truth' can be the population proportion of liars, the sample proportion of liars or ",
+      "the sample proportion of actual lies. Ground truth for the document you are reading was: ",
+        if (sample_from_pop) "the population proportion of liars." else 
+        if (estimate_lies_not_liars) "the sample proportion of actual lies." else 
+        "the sample proportion of liars."
+      )
+
+if (! sample_from_pop && ! estimate_lies_not_liars) method_used_statement <- ""
+
 ```
+
+**`r method_used_statement`**
+
+Some people are honest, while others will lie whenever it benefits them. We would like to understand
+the prevalence of lying, because dishonesty may be economically and socially harmful. Since we
+cannot simply ask people if they are liars, one way to estimate the proportion of liars in a group
+is to ask them to report the result of a coin flip or other random device, offering them a payment
+if they report heads. Liars don't always lie: they only lie when it benefits them. So they always
+report heads irrespective of the true coin flip. ^[GSV maintain this assumption and so shall I.] If
+there are many more heads than we would expect by chance, we can assume many people are lying. But
+how many?
+
+A naïve estimate would be that if e.g. 80 people of 100 report heads, then on average 50 really saw
+heads and 60% (30/50) of the remainder are lying. More generally, from $R$ reports of a good outcome
+in a sample of size $N$, where the _bad_ outcome happens with probability $P$, we can estimate that
+a proportion $\frac{R/N - (1-P)}{P}$ are lying [@abeler2016preferences]. The problem with this approach is that the number of heads is not
+fixed. If we see 1 out of 3 people reporting heads, this method estimates there are less than zero
+liars. But it is still possible that everyone saw heads and 1 person lied.
+
+@Garbarino2018 -- GSV from here on -- point out this problem and introduce an alternative method.
+They claim that their method corrects for this problem and can estimate the full distribution of
+lying outcomes, and they recommend using it for confidence intervals, hypothesis testing and power
+calculations.
+
+Table 3 of GSV reports Monte Carlo simulations, which show that the probability of a Type II error
+can be up to 50 per cent. GSV define a Type II error as the 95% confidence interval not containing
+the true value. A 95% confidence interval which only contains the true value 50% of the time
+is unusual. What is going on?
 
@@
 
-true_data <- tidyr::crossing(
+sim_data <- tidyr::crossing(
   N     = params$N,
@@
 )
-true_data$Liars <- round(true_data$Liars * true_data$N, 0)
+sim_data$Liars_pop_pct <- sim_data$Liars
+
+sim_data <- sim_data[rep(1:nrow(sim_data), each = nreps), ]
+sim_data$sim <- rep_len(1:nreps, nrow(sim_data))
+
+if (sample_from_pop) {
+  sim_data %<>% 
+        group_by(N, Liars, P) %>% 
+        mutate(
+          Liars_sample = rbinom(n(), N, Liars)
+        ) %>% 
+        ungroup() %>% 
+        mutate(
+          Liars = Liars_sample,
+          Liars_sample = NULL
+        )
+} else { 
+  sim_data$Liars <- round(sim_data$Liars * sim_data$N, 0)
+}
 
@@
   R <- row["Liars"] + h_honest
+  names(R) <- NULL
   heads <- h_honest + h_liars
-  c(R, heads)
+  c(R = R, heads = heads)
 }
 
-results <- replicate(nreps, apply(true_data, 1, simulate_cointoss))
+results <- apply(sim_data, 1, simulate_cointoss)
 
-results_R <- results[1, , ]
-results_heads <- results[2, , ]
-colnames(results_R) <- paste0("R", 1:nreps)
-colnames(results_heads) <- paste0("heads", 1:nreps)
+sim_data$R <- results["R", ]
+sim_data$heads <- results["heads",]
 
-sim_data <- true_data %>% 
-      cbind(as_tibble(results_R)) %>% 
-      cbind(as_tibble(results_heads)) %>% 
-      gather("stat", "result", starts_with("R"), starts_with("heads")) %>%
-      extract(stat, c("stat", "sim"), regex="(.*?)(\\d+)", convert = TRUE) %>%
-      spread(stat, result) %>%  
-      arrange(N, Liars, P)
+sim_data <- sim_data %>% arrange(N, Liars, P)
 
@@
 if (rewrite_csv) {
-  readr::write_csv(sim_output, path = "sim-output.csv")
+  path <- paste0("GSV-sims", if (sample_from_pop) "-pop-sample", ".csv")
+
+  readr::write_csv(sim_output, path = path)
 
   # the java only lets you select a document from your home directory
-  copied_to_home_dir_ok <- file.copy("sim-output.csv", normalizePath("~"), overwrite = TRUE)
+  copied_to_home_dir_ok <- file.copy(path, normalizePath("~"), overwrite = TRUE)
   stopifnot(copied_to_home_dir_ok)
   # now run java -jar LyingCalculator.jar from the LyingCalculator directory
+  # make sure the old output file (xxxOutput.csv) is deleted first, or it will be appended to!
 }
+
+sim_est <- sim_data
 ```
@@
 
-sim_est <- left_join(sim_data, gsv_estimates, by = c("N", "R", "P", "CI"))
+sim_est <- left_join(sim_est, gsv_estimates, by = c("N", "R", "P", "CI"))
 
@@
 }
+```
 
+```{r check-gsv-posterior, eval = FALSE}
+
+# if we assume that liars are not uniformly distributed, the posterior of number of heads
+# is not like the prior
+N <- 10
+CI <- 0.9
+tmp <- replicate(10000, {
+  # L <- sample(1:N, 1) # for this, always accurate?
+  L <- rbinom(1, N, 0.1) # not many liars
+  HL <- rbinom(1, L, 0.5)
+  HNL <- rbinom(1, N-L, 0.5)
+  R <- L + HNL
+  H <- HL + HNL
+  c(L, R, H, N, CI, prop_liars_ci_gsv(CI, R, N, 0.5))
+})
+
+tmp <- as.data.frame(t(tmp))
+names(tmp) <- c('L', 'R', 'H', 'N', 'CI', 'cilo', 'cihi')
+tmp$lies_told <- with(tmp, (R-H)/(N-H))
+tmp$lies_in_ci <- tmp$cilo <= tmp$lies_told & tmp$lies_told <= tmp$cihi
+
+# the prior:
+ggplot(tmp, aes(H)) + geom_bar(aes(y = calc(prop))) + 
+  geom_line(data = tmp[tmp$R > quantile(tmp$R, 0.8), ], aes(H, calc(prop)))
+# the posterior is not the prior:
+hist(tmp$H, col = "grey", breaks = 0:N, freq = FALSE, ylim = c(0, 1))
+hist(tmp$H[tmp$R==10], breaks = 0:N, add= T, freq = FALSE, col = rgb(1,0,0,.5))
+
+# the posterior:
+lines(density(with(tmp, H[R > quantile(R, 0.9)])))
+
+# how accurate are we for different numbers of R.
+# NB you can also judge accuracy by different numbers of H, but I'm not sure that's fair as H is
+# an unknown parameter - maybe it is like saying "confidence interval coverage is way off when
+# the errors are big!"
+
+GSV_coverage <- tmp %>% group_by(R) %>% 
+  summarize(n_sims = n(), coverage = mean(lies_in_ci))
+
+tmp %<>% left_join(GSV_coverage, by = "R")
+
+scale_fac <- max(tmp$n_sims)
+ggplot(GSV_coverage, aes(R)) + 
+    geom_hline(yintercept = CI, linetype = 2) +
+    geom_line(aes(y = coverage), colour = "red") +
+    geom_line(aes(y = n_sims/scale_fac), colour = "grey") +
+    scale_y_continuous(sec.axis = sec_axis(~.*scale_fac, name = "N sims"))
+
+plot(GSV_coverage$R, GSV_coverage$coverage, type = "l")
+# number of cases:
+points(GSV_coverage$R, GSV_coverage$n_sims/max(GSV_coverage$n_sims), type = "h", col = "grey")
+
+table(low_coverage = tmp$coverage < 0.8, tmp$R > 60) %>% prop.table(2)
 ```
@@
 sim_est %<>%
-      tidyr::gather(measure, value, contains(".")) %>% 
-      tidyr::extract(measure, into = c("statistic", "method"), regex = "(LB|EV|UB)\\.(.*)") %>% 
+      tidyr::gather(measure, value, matches("^(LB|EV|UB)\\.")) %>% 
+      tidyr::extract(measure, into = c("statistic", "method"), regex = "^(LB|EV|UB)\\.(.*)") %>% 
       tidyr::spread(statistic, value)
 
-# alternative "ground truth" is proportion of lies: (R - heads)/(N - heads)
+# alternative "ground truths":
 if (estimate_lies_not_liars) {
@@
           true_prop = (R - heads)/(N - heads)
+        )
+} else if (sample_from_pop) {
+  sim_est %<>% mutate(
+          true_prop = Liars_pop_pct
         )
@@
 
-I ran simulations to check the overall performance of the GSV confidence intervals. 
+I ran simulations to check the overall performance of the GSV confidence intervals. Simulations
+parameters are shown in Table \@ref(tab:params-table). For each parameter combination, I ran 1000
+simulations. "Liars" always reported heads. Non-liars reported tails with probability $P$ and
+heads otherwise.
+
+```{r params-table}
+
+huxtable(
+        Parameter = c(
+          "Sample size (N)", 
+          "Proportion of liars (L/N)", 
+          "Probability of bad random outcome (P)"
+        ),
+        Values    = c(
+          paste(params$N, collapse = ", "),
+          paste(params$Liars, collapse = ", "),
+          paste(params$P, collapse = ", ")
+        ),
+        add_colnames = TRUE
+      ) %>% 
+      set_caption("(#tab:params-table) Parameter values") %>% 
+      theme_article()
+```
+
 For each simulation and confidence interval, I computed whether the confidence interval 
-contained the true value. Table \@ref(tab:coverage-overall) shows the results.
+contained the true value of $L/N$. Table \@ref(tab:coverage-overall) shows the results.
 
@@
 
-By definition, 95% of 95% confidence intervals ought to contain the true value, on average. GSV
+By definition, 95% of 95% confidence intervals ought to contain the true value, on average. This
+is called "achieving nominal coverage". GSV
 intervals are far from this. The confidence intervals are too narrow. Further analysis shows that
@@
 "heads" out of 10 for a fair coin flip ($R = N = 10, P = 0.5$). The resulting point estimate is that
-100% of subjects lied. The upper and lower confidence intervals are also 100%. Really? Can we rule out
-that 8 subjects lied, and the two honest subjects both saw heads?
+100% of subjects lied. The upper and lower 99% confidence intervals are also 100%. Naïvely, this might
+seem wrong. Can we rule out that 8 subjects lied, and the two honest subjects both saw heads?
 
-The GSV method works like this. First, given $R$ reports of heads, the probability that a total 
-of $T$ heads was observed is calculated as:
+In fact, the GSV method works like this. First, given $R$ reports of heads, the probability that a total 
+of $T$ "true" heads were observed is calculated as:
 
@@
 
-There are two problems with this approach.
+Putting these together, for $R = N = 10$, the estimated distribution of liars is calculated as follows:
+
+* With probability $\frac{1}{1024}$, there were really $T = 10$ heads.
+Nobody lied in the sample.^[But  the proportion of people who lied *out of those who saw tails* is undefined, because noone saw tails.
+The
+GSV software seems to resolve this by fixing the proportion of lies to 100%.]
+
+* Otherwise, 1 or more people saw tails, and they all lied. The proportion of liars is 100%.
+
+Hence, the lower and upper confidence intervals are all 100%.
+
+There are two problems with this approach. One is statistical, one is conceptual.
 
@@
 The probability distribution above does not take account of this. In particular, for $R=N$, 
-the equation above reduces to the binomial distribution.
+the equation above reduces to the binomial distribution. This is not correct.
 
-Second, suppose $R = 10$ heads out of 10 are reported, and suppose 9 heads were really observed, $T
-= 9$. The proportion of people who actually lied in the sample is indeed 100%. But it is 100% of 1
-person -- the only person who saw tails. As an estimate of the proportion of liars in the sample --
-i.e. the proportion who would have lied, had they seen tails -- that is very noisy.^[The
-true number of liars in the sample is unobserved, and needs to be estimated, even if we are not trying
-to make inferences to a larger population.]  The GSV method treats it as certain. In other words, GSV estimates the proportion of lies, rather than the proportion of lying 
-liars who tell them. But the latter is the statistic we care about.
+Second, more importantly, the GSV approach estimates the distribution of the proportion of 
+*lies actually told*, among the subsample of people who saw tails:
 
-Putting these together, for $R = N = 10$, the estimated distribution of liars is calculated as follows:
+\[
+\textit{Lies} = \frac{R-T}{N-T} 
+\]
 
-* With probability $\frac{1}{2^{10}}$, there were really $T = 10$ heads. Nobody lied in the sample,
-but the proportion of people who lied *out of those who could*, $\frac{R-T}{N-T}$, is undefined because
-nobody got the chance to lie.^[The GSV software seems to resolve this by fixing the proportion of 
-lies to 100%.]
+But usually, we are not interested in the proportion of
+lies actually told. We care about how many people in the sample *are liars*, who would lie if they
+saw tails:
 
-* Otherwise, 1 or more people saw tails, and they all lied. The proportion of liars is 100%.
+\[
+\textit{Liars} = \frac{L}{N}.
+\]
 
-Hence, the lower and upper confidence intervals are all 100%.
+Suppose $R = 10$ heads out of 10 are reported, and suppose 9 heads were really observed, $T = 9$.
+$\textit{Lies}$ is indeed 100%.  But it is 100% of 1 person
+-- the only person who saw tails. That one person's behaviour is an unbiased estimate of the
+proportion of liars in the sample, $\textit{Liars}$. But it is a very noisy estimate.
+
+The first problem means that when $R$ is very high or low,
+the percentage of confidence intervals containing $\textit{Lies}$
+may fall off sharply.^[Depending on the distribution of the number of liars $L$.]
+
+The second problem means that the percentage of confidence intervals containing $\textit{Liars}$
+is almost always much less than the nominal coverage.
 
@@
 
-The same problem happens in less extreme form whenever $R$ is high relative to $N$. Table 
-\@ref(tab:coverage-rn) shows this by splitting the simulations by $R/N$. When $R/N$ is
-less than 0.5, coverage levels are OK. When it is greater than 0.5, they are not. Note that
-for fair coin flips, $R/N$ is typically greater than 0.5, in the simulations and in reality.^[
-If we disaggregate by $N$, $P$, and $R/N$, 95% confidence intervals achieve their nominal 
-coverage level in only `r round(prop_ok*100, 1)`% of cases.]
+The problem is especially bad when there are many reports of heads. In this case there were probably
+many true heads, so $T$ is high and the true sample size $N-T$ is low. Table \@ref(tab:coverage-rn)
+shows this. It splits the simulations by the proportion of reported heads, $R/N$. Coverage levels
+fall off sharply as $R/N$ increases. Note that for fair coin flips, $R/N$ is typically greater than
+0.5, in the simulations and in reality.
 
@@
       group_by(
-        `R/N:` = factor(Hmisc::cut2(R/N, cuts = c(0, 1/2, 1)), labels = c("< 0.5", "&ge; 0.5"))      
+        `R/N:` = factor(Hmisc::cut2(R/N, cuts = c(0, 1/4, 1/2, 3/4, 1)))      
       ) %>% 
@@
 
-One can then calculate the proportions of liars as $L/N$. Note that we are now directly estimating
-how many liars are in the whole sample $N$, where a liar is someone who always reports heads. From
+One can then estimate the proportion of $\textit{Liars}$ as $L/N$. From
 this, one can derive confidence intervals and expected values in the usual way.^[R code to
-run these calculations is available at https://github.com/hughjonesd/GSV-comment.]
+run these calculations, along with all the code for this article, is available at https://github.com/hughjonesd/GSV-comment .]
 
@@
 
-Results are shown in Table \@ref(tab:coverage-allmethods). Both
-frequentist and  Bayesian methods mostly achieve the nominal confidence level, with
-more than 90/95/99% of intervals containing the true value. The exception is the frequentist
-99% confidence interval, which is too narrow.
+Results are shown in Table \@ref(tab:coverage-allmethods). Both frequentist and  Bayesian methods
+mostly achieve the nominal confidence level, with more than 90/95/99% of intervals containing the
+true value of $Liars$. The exception is the frequentist 99% confidence interval, which is too
+narrow.
 
@@
 
-We can also compare the accuracy of point estimates of the proportion of liars. Table
+We can also compare the accuracy of point estimates of $\textit{Liars}$. Table
 \@ref(tab:point-estimates) shows the mean squared error for methods by different $N$. For low $N$,
@@
 })
+
 names(distribs) <- nats$resnat
@@
 regression to the mean". In other words, if we start from the prior that everyone is the same,
-we will end up believing that the British are less honest, and the Chinese people are more honest,
-than the experimental data *per se* suggest.
+we will end up believing that the British people in the sample are less honest, and the Chinese 
+people more honest, than the experimental data *per se* suggest.
 
@@
   stopifnot(ctry1 %in% nats$resnat, ctry2 %in% nats$resnat)
-
-  prob_first_less <- 0
   N_1 <- nats$N[nats$resnat == ctry1]
   N_2 <- nats$N[nats$resnat == ctry2]
-  for (L_1 in seq(0, length.out = length(distribs[[ctry1]]))) {
-    for (L_2 in seq(0, length.out = length(distribs[[ctry2]]))) {
-      l_1 <- L_1/N_1
-      l_2 <- L_2/N_2
-      if (l_1 < l_2) {
-        prob_first_less <- prob_first_less + 
-            (distribs[[ctry1]][L_1 + 1] * distribs[[ctry2]][L_2 + 1])
-      }
-    }
-  }
+  heads_1 <- nats$heads[nats$resnat == ctry1]
+  heads_2 <- nats$heads[nats$resnat == ctry2]  
+  diff_dist <- compare_groups(heads1 = heads_1, N1 = N_1, heads2 = heads_2, N2 = N_2, P = 0.5)
 
+  prob_first_less <-sum(diff_dist$prob[diff_dist$diff < 0]) 
   return(prob_first_less)
@@
 
+# The population
+
+So far we have been trying to estimate the proportion of $\textit{Liars}$ in the sample. In fact,
+we usually care about the proportion in liars in populations from which the sample is drawn. This
+adds another layer of randomness. When $N$ is large, the sample distribution should approximate
+the population distribution and either frequentist or Bayesian approaches should work. Further
+simulations, not shown, suggest that Bayesian confidence intervals are less robust in bounding
+$Liars$ in the population from which the sample $L$ is randomly drawn.
+
 # Recommendations
@@
 
-1. Do not use the GSV confidence intervals.
+1. Do not use the GSV confidence intervals, unless you are specifically interested in *Lies* rather
+  than *Liars*. Even in that case be aware that the confidence intervals have low coverage for extreme
+  values of $R$.
 2. If your N is reasonably large, say at least 100, you can safely use standard frequentist 
-  confidence intervals and tests.
-3. If your N is too small for point 2 to apply, it may be too small, full stop.
-4. If increasing your N is not possible for whatever reason, consider using Bayesian methods to find
-  confidence intervals and point estimates. To estimate differences between subgroups, consider
+  confidence intervals and tests. If you are interested in the population from which the sample is drawn,
+  you should do so, as they are most robust.
+3. If your N is small and you are interested in the sample proportion of $\textit{Liars}$, consider
+  Bayesian estimates. To estimate differences between subgroups, consider
   empirical Bayes with a prior derived from the pooled sample.
+
+Lastly, here is a simple way to avoid these shenanigans. Ask a group of $N$ experimental subjects, 
+not to flip a coin, but to draw a black or white ball, without replacement, from an urn containing 
+$N$ balls, of which $T$ are white. Pay them if they report a white ball. You will then know that the 
+proportion of lies told is $(R-T)/(N-T)$, and this will also be the proportion of liars, in a sample
+of $N-T$ subjects. So you can estimate the proportion of $\textit{Lies}$, and of the lying 
+$\textit{Liars}$ who tell them.
 
@@
 
-## Methods
-
-Simulations parameters are shown in Table \@ref(tab:params-table).
-
-```{r params-table}
-
-huxtable(
-        Parameter = c(
-          "Sample size (N)", 
-          "Proportion of liars (R/N)", 
-          "Probability of bad outcome (P)"
-        ),
-        Values    = c(
-          paste(params$N, collapse = ", "),
-          paste(params$Liars, collapse = ", "),
-          paste(params$P, collapse = ", ")
-        ),
-        add_colnames = TRUE
-      ) %>% 
-      set_caption("(#tab:params-table) Parameter values") %>% 
-      theme_article()
-```
-
-For each parameter combination, I ran 1000 simulations. All liars always reported heads. Non-liars
-reported tails with probability $P$ and heads otherwise.
-
-## More results
+R code to reproduce this comment is available at https://github.com/hughjonesd/GSV-comment . You
+can also rerun the simulations to test confidence interval coverage of $Lies$, of $Liars$, or
+of $Liars$ in a population from which samples are drawn. Lastly, I provide code to find Bayesian
+posterior distributions of $Liars$.
 
@@
 
-ggplot(coverage_grp_gsv, aes(Liars/N, mean_in_ci, colour = P)) +
-      geom_point() + geom_line() + 
+g <- ggplot(coverage_grp_gsv, aes(Liars/N, mean_in_ci, colour = P)) +
       geom_hline(aes(yintercept = ci/100), linetype = 2) +
@@
       xlab("True proportion of liars L/N") + ylab("Proportion within C.I.")
+
+if (sample_from_pop) g + geom_smooth(method = "loess") else g + geom_point() + geom_line()
 

### 2018-11-01 bayesian-heads.R

@@ -133,7 +133,7 @@ naive_prob_L <- function (heads, N, P) {
 #' @return 
 #' A data frame with two columns, "diff" and "prob". "diff"
 #' gives a possible difference between the proportion of liars
-#' in group 1 and group 2 (positive values mean group 1 has more).
+#' in group 1 and group 2 (positive values mean that group 1 has more).
 #' "prob" gives the posterior probability of that outcome.
 #' 
 #' @examples

### 2018-11-01 GSV-comment-brief.Rmd
Make LaTeX (ugh) work

@@
 ---
-title: "Lies and the lying liars who tell them: comment on Garbarino, Slonim and Villeval (2018)"
+title: "Lies and the lying liars who tell them"
+subtitle: "Comment on Garbarino, Slonim and Villeval (2018)"
 author: "David Hugh-Jones"
 date: "`r Sys.Date()`"
+header-includes:
+  - \usepackage{setspace}
+  - \usepackage{placeins}
+  - \onehalfspacing
 output:
-  bookdown::tufte_book2:
-    citation_package: natbib
+  pdf_document:
+    keep_tex: true
+    md_extensions: +raw_attribute
+    latex_engine: xelatex
+  tufte::tufte_handout:
+    latex_engine: xelatex
+  bookdown::tufte_handout2:
     latex_engine: xelatex
     md_extensions: +raw_attribute
-  tufte::tufte_handout:
-    citation_package: natbib
-    latex_engine: xelatex
   bookdown::tufte_html2: 
@@
 knitr::opts_chunk$set(echo = FALSE)
-options(huxtable.knitr_output_format = "html")
+options(huxtable.knitr_output_format = "latex")
 source("bayesian-heads.R")
@@
 
-huxtable::set_default_properties(position = "left")
+huxtable::set_default_properties(position = "left", top_padding = 7, bottom_padding = 12)
 set.seed(19751027)
@@
 I ran simulations to check the overall performance of the GSV confidence intervals. Simulations
-parameters are shown in Table \@ref(tab:params-table). For each parameter combination, I ran 1000
+parameters are shown in Table \ref{tab:params-table}. For each parameter combination, I ran 1000
 simulations. "Liars" always reported heads. Non-liars reported tails with probability $P$ and
@@
       ) %>% 
-      set_caption("(#tab:params-table) Parameter values") %>% 
-      theme_article()
+      set_caption("Parameter values") %>% 
+      set_label("tab:params-table") %>% 
+      theme_article(header_col = FALSE)
 ```
@@
 For each simulation and confidence interval, I computed whether the confidence interval 
-contained the true value of $L/N$. Table \@ref(tab:coverage-overall) shows the results.
+contained the true value of $L/N$. Table \ref{tab:coverage-overall} shows the results.
 
@@
         CI = paste0("CI ", CI, "%"),
-        method = recode(method, gsv = "GSV", simple = "Frequentist", ubayes = "Bayesian")
+        Method = recode(method, gsv = "GSV", simple = "Frequentist", ubayes = "Bayesian"),
+        method = NULL
       ) %>% 
       spread(CI, mean_in_ci) %>% 
-      arrange(factor(method, levels = c("GSV", "Frequentist", "Bayesian")))
+      arrange(factor(Method, levels = c("GSV", "Frequentist", "Bayesian")))
 
@@
 ht_overall <- as_huxtable(cov_overall, add_colnames = TRUE) %>% 
-      set_caption("(#tab:coverage-overall) Proportion of true results within confidence interval.") %>% 
+      set_caption("Proportion of true results within confidence interval.") %>% 
       set_label("tab:coverage-overall") %>% 
       set_number_format(-1, -1, list(pct_format)) %>% 
-      theme_article()
+      theme_article(header_col = FALSE)
 
@@
 The problem is especially bad when there are many reports of heads. In this case there were probably
-many true heads, so $T$ is high and the true sample size $N-T$ is low. Table \@ref(tab:coverage-rn)
+many true heads, so $T$ is high and the true sample size $N-T$ is low. Table \ref{tab:coverage-rn}
 shows this. It splits the simulations by the proportion of reported heads, $R/N$. Coverage levels
@@
         mean_in_ci  = mean(within_ci, na.rm = TRUE), 
-        `Pct cases` = pct_cases[1]
+        `Percentage of cases` = pct_cases[1]
       ) %>% 
@@
 as_huxtable(coverage_rn, add_colnames = TRUE) %>% 
-      set_caption("(#tab:coverage-rn) GSV confidence interval coverage by low and high R/N") %>% 
+      set_caption("GSV confidence interval coverage by low and high R/N") %>% 
       set_label("tab:coverage-rn") %>% 
@@
       set_number_format(-1, -1, list(pct_format)) %>% 
-      theme_article()
+      theme_article(header_col = FALSE)
 ```
@@
 
-Results are shown in Table \@ref(tab:coverage-allmethods). Both frequentist and  Bayesian methods
+Results are shown in Table \ref{tab:coverage-allmethods}. Both frequentist and  Bayesian methods
 mostly achieve the nominal confidence level, with more than 90/95/99% of intervals containing the
@@
 ht_overall %>% 
-      set_caption("(#tab:coverage-allmethods) Coverage levels for GSV and alternative methods")
+      set_caption("Coverage levels for GSV and alternative methods") %>% 
+      set_label("tab:coverage-allmethods")
 ```
@@
 Frequentist confidence intervals could be less accurate when N is low, since that leads to more
-sampling variation in the number of true heads. Table \@ref(tab:coverage-N) checks this by looking
+sampling variation in the number of true heads. Table \ref{tab:coverage-N} checks this by looking
 separately at simulations with $N=10$ and $N=50$. Frequentist 99% confidence intervals indeed appear
@@
       set_rowspan(c(2, 4, 6), "Method", 2) %>% 
+      set_valign(c(2, 4, 6), "Method", "top") %>% 
       set_number_format(-1, contains("CI"), list(pct_format)) %>% 
-      set_caption("(#tab:coverage-N) Confidence interval coverage by sample size") %>% 
-      set_label("table:coverage-N") %>% 
-      theme_article()
+      set_caption("Confidence interval coverage by sample size") %>% 
+      set_label("tab:coverage-N") %>% 
+      theme_article(header_col = FALSE) %>% 
+      set_bottom_border(6, 1, 0.4) # rowspan problems
 ```
@@
 We can also compare the accuracy of point estimates of $\textit{Liars}$. Table
-\@ref(tab:point-estimates) shows the mean squared error for methods by different $N$. For low $N$,
+\ref{tab:point-estimates} shows the mean squared error for methods by different $N$. For low $N$,
 the best method is Bayesian and the worst is Frequentist, with GSV in between. When $N$ gets large all
@@
       as_huxtable(add_colnames = TRUE) %>% 
-      set_caption("(#tab:point-estimates) Mean squared errors by method and N") %>% 
-      theme_article()
+      set_caption("Mean squared errors by method and N") %>% 
+      set_label("tab:point-estimates") %>% 
+      theme_article(header_col = FALSE)
 ```
@@
 
-```{r hj2016-pic, fig.cap = "Posterior means and confidence intervals for proportion dishonest in 15 countries. Crosses are naive estimates."}
+```{r hj2016-pic, fig.cap = "Posterior means and confidence intervals for proportion dishonest in 15 countries. Crosses are naïve estimates.", fig.align="center"}
 
@@
 
-Results are shown in Figure \@ref(fig:hj2016-pic), with means and 95% confidence intervals. There
+Results are shown in Figure \ref{fig:hj2016-pic}, with means and 95% confidence intervals. There
 is substantial shrinkage from the "naive" per-country estimates (using $2R/N - 1$). One of the strengths of empirical Bayes,  as @casella1985introduction points out, is that it "anticipates
@@
 
-Table \@ref(tab:country-comparisons) shows Bayesian comparisons for selected countries. Even though
+Table \ref{tab:country-comparisons} shows Bayesian comparisons for selected countries. Even though
 estimates have "shrunk" towards the pooled mean from the naive estimates, differences remain
@@
 cc_hux <- as_huxtable(ctry_comp, add_colnames = TRUE, add_rownames = TRUE) %>% 
-      set_caption("(#tab:country-comparisons) Bayesian country comparisons. 
+      set_caption("Bayesian country comparisons. 
             Cells give the probability that row country has fewer liars than column country.") %>% 
@@
 
+\FloatBarrier
+
 # Appendix
@@
 Nevertheless, if I use GSV's method as stated, rather than their program, confidence intervals
-remain too small, as shown in Table \@ref(tab:coverage-recalc).
+remain too small, as shown in Table \ref{tab:coverage-recalc}.
 
@@
 as_huxtable(coverage_recalc, add_colnames = TRUE) %>% 
-      set_caption("(#tab:coverage-recalc) Proportion of true results within confidence interval, recalculated GSV method") %>% 
+      set_caption("Proportion of true results within confidence interval, recalculated GSV method") %>% 
       set_label("tab:coverage-recalc") %>% 
@@
 
-Figure \@ref(fig:coverage-pic) shows the proportions of true values within the confidence interval for the GSV method,
-split by $N$, $P$ and confidence level. Dashed lines show the nominal confidence level.
-
-Figure \@ref(fig:coverage-grp-pic) splits this still further, by the true proportion of liars within each
-simulation. This makes the pattern clear: coverage gets worse as the proportion of liars increases (until 100% where it jumps back up as results become deterministic).
-
-```{r coverage-pic, fig.cap = "GSV confidence interval coverage by confidence level, N and P"}
+Figure \ref{fig:coverage-pic} shows the proportions of true values within the confidence interval
+for the GSV method, split by $N$, $P$ and confidence level. Dashed lines show the nominal confidence
+level.
+
+Figure \ref{fig:coverage-grp-pic} splits this still further, by the true proportion of liars within
+each simulation. This makes the pattern clear: coverage gets worse as the proportion of liars
+increases (until 100% where it jumps back up as results become deterministic).
+
+```{r coverage-pic, fig.cap = "GSV confidence interval coverage by confidence level, N and P", fig.align="centre"}
 
@@
 
-```{r coverage-grp-pic, fig.cap = "GSV confidence interval coverage by confidence level, N, P and true proportion of liars"}
+```{r coverage-grp-pic, fig.cap = "GSV confidence interval coverage by confidence level, N, P and true proportion of liars", fig.align="centre"}
 
@@
 
-Figure \@ref(fig:errors-by-true-prop) shows mean squared error by estimation method and 
-true proportion of liars in the sample (True $L/N$), for $N$ &le; 50. The Bayesian method is best 
+Figure \ref{fig:errors-by-true-prop} shows mean squared error by estimation method and 
+true proportion of liars in the sample (True $L/N$), for $N$ of 10 and 50. The Bayesian method is best 
 for all values of $L/N$ up to 80%.
 
-```{r errors-by-true-prop, fig.cap = "Errors by method and true proportion of liars, N &le; 50"}
+```{r errors-by-true-prop, fig.cap = "Errors by method and true proportion of liars, N = 10 and 50", fig.align="centre"}
 errors_true_prop <- sim_est %>%       
@@
 
-```{r errors-disagg, include = FALSE}
+```{r errors-disagg, include = FALSE, fig.align="centre", fig.cap="Point estimate errors by R/N, N and P"}
 
@@
 ```
+
+\FloatBarrier
+
+# References

### 2018-11-01 GSV-comment-brief.Rmd
Something reasonable for TeX.

@@
   - \onehalfspacing
+  - \usepackage{fontspec}
 output:
   pdf_document:
-    keep_tex: true
     md_extensions: +raw_attribute
@@
     latex_engine: xelatex
+    md_extensions: +raw_attribute
   bookdown::tufte_handout2:
@@
 link-citations: yes
+fontsize: 12pt
+mainfont: Times New Roman
 ---
@@
 >  Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability distribution 
->  of the number of liars in "coin flip" style experiments. However, their method appears 
->  to give erroneous confidence intervals. I explain why, and describe two better
+>  of the number of liars in "coin flip" style experiments. However, their method  
+>  gives misleading confidence intervals. I explain why, and describe two better
 >  ways to calculate probability distributions.
@@
 
-huxtable::set_default_properties(position = "left", top_padding = 7, bottom_padding = 12)
+huxtable::set_default_properties(position = "left", top_padding = 12, bottom_padding = 6)
 set.seed(19751027)
@@
 ```
+
+TODO XXX: point out the claims they make. Add your sims of when the posterior is wrong
+and intervals fail even for (R-T)/(N-T).
 
@@
 A naïve estimate would be that if e.g. 80 people of 100 report heads, then on average 50 really saw
-heads and 60% (30/50) of the remainder are lying. More generally, from $R$ reports of a good outcome
-in a sample of size $N$, where the _bad_ outcome happens with probability $P$, we can estimate that
+heads and 60% (30/50) of the remainder are lying. More generally, from *R* reports of a good outcome
+in a sample of size *N*, where the _bad_ outcome happens with probability *P*, we can estimate that
 a proportion $\frac{R/N - (1-P)}{P}$ are lying [@abeler2016preferences]. The problem with this approach is that the number of heads is not
@@
 parameters are shown in Table \ref{tab:params-table}. For each parameter combination, I ran 1000
-simulations. "Liars" always reported heads. Non-liars reported tails with probability $P$ and
-heads otherwise.
+simulations. "Liars" always reported heads. Non-liars reported tails with probability *P* and
+heads otherwise. For each simulation and confidence interval, I computed whether the confidence interval 
+contained the true value of *L/N*. Table \ref{tab:coverage-overall} shows the results.
 
@@
       set_label("tab:params-table") %>% 
-      theme_article(header_col = FALSE)
-```
-
-For each simulation and confidence interval, I computed whether the confidence interval 
-contained the true value of $L/N$. Table \ref{tab:coverage-overall} shows the results.
+      theme_plain()
+```
 
@@
       set_number_format(-1, -1, list(pct_format)) %>% 
-      theme_article(header_col = FALSE)
+      theme_plain()
 
@@
 ht_just_gsv[1, 1] <- ""
-ht_just_gsv
+theme_plain(ht_just_gsv)
 ```
@@
 intervals are far from this. The confidence intervals are too narrow. Further analysis shows that
-this problem holds across all simulated probabilities of the low outcome $P$, confidence
-levels, and sample sizes $N$ (up to 500).^[In the appendix.]
+this problem holds across all simulated probabilities of the low outcome *P*, confidence
+levels, and sample sizes *N* (up to 500).^[See the appendix.]
 
 Why does this happen? We can get a clue by running the GSV method when there are 10 reports of 
-"heads" out of 10 for a fair coin flip ($R = N = 10, P = 0.5$). The resulting point estimate is that
+"heads" out of 10 for a fair coin flip (*R = N = 10, P = 0.5*). The resulting point estimate is that
 100% of subjects lied. The upper and lower 99% confidence intervals are also 100%. Naïvely, this might
@@
 
-In fact, the GSV method works like this. First, given $R$ reports of heads, the probability that a total 
-of $T$ "true" heads were observed is calculated as:
+In fact, the GSV method works like this. First, given *R* reports of heads, the probability that a total 
+of *T* "true" heads were observed is calculated as:
 
@@
 
-This is the binomial distribution, truncated at $R$, because by assumption, nobody "lies downward"
+This is the binomial distribution, truncated at *R*, because by assumption, nobody "lies downward"
 and reports tails when they really saw heads.
 
-Next, from $T$ the number of liars is calculated as $R-T$; and the proportion of liars is calculated
-as $(R-T)/(N-T)$, because $N-T$ people saw the low outcome and had the chance to lie. Combining this
+Next, from *T* the number of liars is calculated as *R-T*; and the proportion of liars is calculated
+as *(R-T)/(N-T)*, because *N-T* people saw the low outcome and had the chance to lie. Combining this
 with the truncated binomial gives a cumulative distribution function of the proportion of liars.
@@
 
-Putting these together, for $R = N = 10$, the estimated distribution of liars is calculated as follows:
-
-* With probability $\frac{1}{1024}$, there were really $T = 10$ heads.
+Putting these together, for *R = N = 10*, the estimated distribution of liars is calculated as follows:
+
+* With probability $\frac{1}{1024}$, there were really *T = 10* heads.
 Nobody lied in the sample.^[But  the proportion of people who lied *out of those who saw tails* is undefined, because noone saw tails.
@@
 are probably many liars in your sample. On the other hand, probably a lot of coins really landed heads.
-The probability distribution above does not take account of this. In particular, for $R=N$, 
+The probability distribution above does not take account of this. In particular, for *R = N*, 
 the equation above reduces to the binomial distribution. This is not correct.
@@
 
-Suppose $R = 10$ heads out of 10 are reported, and suppose 9 heads were really observed, $T = 9$.
-$\textit{Lies}$ is indeed 100%.  But it is 100% of 1 person
+We care about *Liars* not *Lies*, because *Lies* is just a noisy estimate of *Liars*: it is the
+number of liars who happened to see heads. It is a function of honesty and luck. We are interested
+in the honesty.^[There may be times when social scientists care about how many people actually
+lied, but I cannot think of many.]
+
+Suppose *R = 10* heads out of 10 are reported, and suppose 9 heads were really observed, *T = 9*.
+*Lies* is indeed 100%.  But it is 100% of 1 person
 -- the only person who saw tails. That one person's behaviour is an unbiased estimate of the
-proportion of liars in the sample, $\textit{Liars}$. But it is a very noisy estimate.
-
-The first problem means that when $R$ is very high or low,
-the percentage of confidence intervals containing $\textit{Lies}$
-may fall off sharply.^[Depending on the distribution of the number of liars $L$.]
-
-The second problem means that the percentage of confidence intervals containing $\textit{Liars}$
+proportion of liars in the sample, *Liars*. But it is a very noisy estimate.
+
+The first problem means that when *R* is very high or low,
+the percentage of confidence intervals containing *Lies*
+may fall off sharply.^[Depending on the distribution of the number of liars *L*.]
+
+The second problem means that the percentage of confidence intervals containing *Liars*
 is almost always much less than the nominal coverage.
@@
 The problem is especially bad when there are many reports of heads. In this case there were probably
-many true heads, so $T$ is high and the true sample size $N-T$ is low. Table \ref{tab:coverage-rn}
-shows this. It splits the simulations by the proportion of reported heads, $R/N$. Coverage levels
-fall off sharply as $R/N$ increases. Note that for fair coin flips, $R/N$ is typically greater than
+many true heads, so *T* is high and the true sample size *N - T* is low. Table \ref{tab:coverage-rn}
+shows this. It splits the simulations by the proportion of reported heads, *R/N*. Coverage levels
+fall off sharply as *R/N* increases. Note that for fair coin flips, *R/N* is typically greater than
 0.5, in the simulations and in reality.
@@
       set_number_format(-1, -1, list(pct_format)) %>% 
-      theme_article(header_col = FALSE)
+      theme_plain()
 ```
@@
 Can we do better? There are two alternative methods one might use to calculate confidence intervals.
-The first is simply to calculate confidence bounds $\bar{R},\underline{R}$ for the proportion of
-heads reported in the population, given the number reported in the sample. One can then back out
-confidence bounds for the proportion of liars as $\frac{R - (1-P)}{P}$, as in
+The first is simply to calculate confidence bounds for the proportion of
+heads that would be reported in the population, given the number that were reported in the sample. 
+One can then back out
+confidence bounds for the proportion of liars as $\frac{R/N - (1-P)}{P}$, as in
 @abeler2016preferences.^[Confidence bounds lower than 0 can be set to 0.]  As GSV point out, this
@@
 The second method is to use Bayes' rule. Start with a prior probability distribution over
-the number of liars $L$, $\textrm{Pr}(L)$. The posterior probability is then:
+the number of liars *L*, *Pr(L)*. The posterior probability is then:
 
@@
 
-where the probability of getting $R$ reports of heads in total for given $L$ is just
-the probability that the $N - L$ honest people saw $R - L$ heads:
+where the probability of getting *R* reports of heads in total for given *L* is just
+the probability that the *N - L* honest people saw *R - L* heads:
 
@@
 
-One can then estimate the proportion of $\textit{Liars}$ as $L/N$. From
-this, one can derive confidence intervals and expected values in the usual way.^[R code to
-run these calculations, along with all the code for this article, is available at https://github.com/hughjonesd/GSV-comment .]
-
-For the estimation here, I used a uniform prior, with $Pr(L) = \frac{1}{N+1}$ for $L$ in  0
-to $N$.
-
-Results are shown in Table \ref{tab:coverage-allmethods}. Both frequentist and  Bayesian methods
-mostly achieve the nominal confidence level, with more than 90/95/99% of intervals containing the
-true value of $Liars$. The exception is the frequentist 99% confidence interval, which is too
-narrow.
+One can then estimate the proportion of *Liars* as *L/N*. From
+this, one can derive confidence intervals and expected values in the usual way.
+
+For the estimation here, I used a uniform prior, with *Pr(L) =* $\frac{1}{N+1}$ for *L* in  0
+to *N*.
+
+I used these estimation methods on my simulated data. Results are shown in Table
+\ref{tab:coverage-allmethods}. Both frequentist and  Bayesian methods mostly achieve the nominal
+confidence level, with more than 90/95/99% of intervals containing the true value of *Liars*. The
+exception is the frequentist 99% confidence interval, which is too narrow.
 
@@
 sampling variation in the number of true heads. Table \ref{tab:coverage-N} checks this by looking
-separately at simulations with $N=10$ and $N=50$. Frequentist 99% confidence intervals indeed appear
-slightly too narrow for this range. Bayesian confidence intervals are fine. Both alternatives
+separately at simulations with *N = 10* and *N = 50*. Frequentist 99% confidence intervals indeed
+appear slightly too narrow for this range. Bayesian confidence intervals are fine. Both alternatives
 perform much better than the GSV approach.
@@
       set_label("tab:coverage-N") %>% 
-      theme_article(header_col = FALSE) %>% 
-      set_bottom_border(6, 1, 0.4) # rowspan problems
+      theme_plain() %>% 
+      set_bottom_border(6, 1, 0.4)
 ```
@@
 
-We can also compare the accuracy of point estimates of $\textit{Liars}$. Table
-\ref{tab:point-estimates} shows the mean squared error for methods by different $N$. For low $N$,
-the best method is Bayesian and the worst is Frequentist, with GSV in between. When $N$ gets large all
+We can also compare the accuracy of point estimates of *Liars*. Table
+\ref{tab:point-estimates} shows the mean squared error for methods by different *N*. For low *N*,
+the best method is Bayesian and the worst is Frequentist, with GSV in between. When *N* gets large all
 methods give about the same estimates and are equally accurate.
@@
 The Bayesian method might have an advantage here, since it assumes a uniform prior and the
-simulations indeed used a uniform distribution of the proportion of liars $L/N$. In fact, further
-analysis reveals that the Bayesian method is best across all specific values of $L/N$ up to
-80%.^[When $L/N = 1$, all subjects deterministically report heads, and both Frequentist and
+simulations indeed used a uniform distribution of the proportion of liars *L/N*. In fact, further
+analysis reveals that the Bayesian method is best across all specific values of *L/N* up to
+80%.^[When *L/N = 1*, all subjects deterministically report heads, and both Frequentist and
 Bayesian point estimates are exactly correct.] So, the Bayesian method is likely to be best unless
-one is sure that the true $L/N$ is rather high.
+one is sure that the true *L/N* is rather high.
 
@@
       set_label("tab:point-estimates") %>% 
-      theme_article(header_col = FALSE)
+      theme_plain()
 ```
@@
 For example, @hugh2016honesty estimates the dishonesty rates of 15 nations using a coin flip
-experiment. The pooled estimate of the proportion of liars in the sample is given by $2R/N - 1$ = 
-`r round(pooled_prop_liars, 2)`. With $N$ = `r nrow(dfr)`, this will not be much affected by 
+experiment. The pooled estimate of the proportion of liars in the sample is given by *2R/N - 1* = 
+`r round(pooled_prop_liars, 2)`. With *N* = `r nrow(dfr)`, this will not be much affected by 
 sampling variation in the number of heads. We can use a binomial distribution with this as the prior.
 
-```{r hj2016-pic, fig.cap = "Posterior means and confidence intervals for proportion dishonest in 15 countries. Crosses are naïve estimates.", fig.align="center"}
+```{r hj2016-pic, fig.cap = "Posterior means and confidence intervals for proportion dishonest in 15 countries. Crosses are naïve estimates.", fig.align="center", fig.width=5.5, fig.height=4}
 
@@
 Results are shown in Figure \ref{fig:hj2016-pic}, with means and 95% confidence intervals. There
-is substantial shrinkage from the "naive" per-country estimates (using $2R/N - 1$). One of the strengths of empirical Bayes,  as @casella1985introduction points out, is that it "anticipates
-regression to the mean". In other words, if we start from the prior that everyone is the same,
-we will end up believing that the British people in the sample are less honest, and the Chinese 
-people more honest, than the experimental data *per se* suggest.
+is substantial shrinkage from the "naïve" per-country estimates found by calculating *2R/N - 1*
+separately for each country). One of the strengths of empirical Bayes,  as @casella1985introduction
+points out, is that it "anticipates regression to the mean". That is, as there is noise in the data,
+the most and least honest groups in the data probably had some extreme error terms. So the
+British people in the sample may be less honest, and the Chinese people more honest, than the per-group 
+data suggest.
 
@@
 
-This approach has a nice interpretation, somewhat analogous
-to the use of the null hypothesis in frequentist methods. We start from the 
-belief that the proportion of liars is the same across all groups. The posterior
-then shows how much the evidence changes this belief.
+This approach has a nice interpretation, analogous to the use of the null hypothesis in frequentist
+methods. We start from the belief that the proportion of liars is the same across all groups. The
+posterior then shows how much the evidence changes this belief.
 
@@
       set_na_string("--") %>% 
-      theme_basic()
+      set_number_format("%.3f") %>% 
+      set_align(-1, -1, ".") %>% 
+      theme_plain() %>% 
+      set_bold(everywhere, 1, TRUE)
 
@@
 
-So far we have been trying to estimate the proportion of $\textit{Liars}$ in the sample. In fact,
-we usually care about the proportion in liars in populations from which the sample is drawn. This
-adds another layer of randomness. When $N$ is large, the sample distribution should approximate
+So far we have been trying to estimate the proportion of *Liars* in the sample. In fact,
+we usually care about the proportion of liars in populations from which the sample is drawn. This
+adds another layer of randomness. When *N* is large, the sample distribution should approximate
 the population distribution and either frequentist or Bayesian approaches should work. Further
-simulations, not shown, suggest that Bayesian confidence intervals are less robust in bounding
-$Liars$ in the population from which the sample $L$ is randomly drawn.
-
-# Recommendations
-
-To sum up, these results suggest some simple recommendations when you are analysing a coin flip
+simulations, not shown, suggest that Bayesian confidence intervals are less robust than frequentist ones
+in bounding the population proportion of *Liars* when the sample is randomly drawn from the population.
+
+# Conclusion
+
+These results suggest some simple recommendations when you are analysing a coin-flip
 style experiment.
@@
 1. Do not use the GSV confidence intervals, unless you are specifically interested in *Lies* rather
-  than *Liars*. Even in that case be aware that the confidence intervals have low coverage for extreme
-  values of $R$.
+  than *Liars*. Even in that case, be aware that the confidence intervals have low coverage for extreme
+  values of *R*.
 2. If your N is reasonably large, say at least 100, you can safely use standard frequentist 
@@
   you should do so, as they are most robust.
-3. If your N is small and you are interested in the sample proportion of $\textit{Liars}$, consider
+3. If your N is small and you are interested in the sample proportion of *Liars*, consider
   Bayesian estimates. To estimate differences between subgroups, consider
@@
 
-Lastly, here is a simple way to avoid these shenanigans. Ask a group of $N$ experimental subjects, 
+Lastly, here is a simple way to avoid these shenanigans. Ask a group of *N* experimental subjects, 
 not to flip a coin, but to draw a black or white ball, without replacement, from an urn containing 
-$N$ balls, of which $T$ are white. Pay them if they report a white ball. You will then know that the 
-proportion of lies told is $(R-T)/(N-T)$, and this will also be the proportion of liars, in a sample
-of $N-T$ subjects. So you can estimate the proportion of $\textit{Lies}$, and of the lying 
-$\textit{Liars}$ who tell them.
+*N* balls, of which *T* are white. Pay them if they report a white ball. You will then know -- not
+estimate -- that the proportion of lies told is *(R-T)/(N-T)*, and this will also be the proportion
+of liars, in a sample of *N-T* subjects. So you can simultaneously estimate the proportion of
+*Lies*, and of the lying *Liars* who tell them.
 
 \FloatBarrier
+\newpage
 
@@
 
-R code to reproduce this comment is available at https://github.com/hughjonesd/GSV-comment . You
-can also rerun the simulations to test confidence interval coverage of $Lies$, of $Liars$, or
-of $Liars$ in a population from which samples are drawn. Lastly, I provide code to find Bayesian
-posterior distributions of $Liars$.
+R code to reproduce this comment is available at https://github.com/hughjonesd/GSV-comment. You
+can also rerun the simulations to test confidence interval coverage of *Lies*, of *Liars*, or
+of *Liars* in a population from which samples are drawn. Lastly, I provide code to find Bayesian
+posterior distributions of *Liars*.
 
@@
 method, but I could not reproduce their confidence intervals. For example, 
-when $R = 3, N = 6, P = 0.5$, GSV's Java program gives the upper bound of the 95% confidence 
+when *R = 3, N = 6, P = 0.5*, GSV's Java program gives the upper bound of the 95% confidence 
 interval for the proportion of liars as 49.91%. But the possible proportions of liars when there
-are $T=0,1,2,3$ true heads, are $(R-T)/(N-T) =$ 
+are *T=0,1,2,3* true heads, are *(R-T)/(N-T) =* 
 `r paste0(prop_liars(3:0, 3, 6) * 100, "%", collapse = ", ")`.
@@
       set_number_format(-1, everywhere, list(pct_format)) %>% 
-      theme_article(header_col = FALSE)
+      theme_plain()
 
@@
 Figure \ref{fig:coverage-pic} shows the proportions of true values within the confidence interval
-for the GSV method, split by $N$, $P$ and confidence level. Dashed lines show the nominal confidence
+for the GSV method, split by *N*, *P* and confidence level. Dashed lines show the nominal confidence
 level.
@@
 
-```{r coverage-pic, fig.cap = "GSV confidence interval coverage by confidence level, N and P", fig.align="centre"}
+```{r coverage-pic, fig.cap = "GSV confidence interval coverage by confidence level, N and P", fig.width=5.5, fig.height=4, fig.align="left"}
 
@@
 
-```{r coverage-grp-pic, fig.cap = "GSV confidence interval coverage by confidence level, N, P and true proportion of liars", fig.align="centre"}
+```{r coverage-grp-pic, fig.cap = "GSV confidence interval coverage by confidence level, N, P and true proportion of liars", fig.align="left", fig.width=6, fig.height=4}
 
@@
       facet_grid(N ~ CI, labeller = "label_both") +
-      xlab("True proportion of liars L/N") + ylab("Proportion within C.I.")
+      xlab("Liars") + ylab("Proportion within C.I.")
 
@@
 Figure \ref{fig:errors-by-true-prop} shows mean squared error by estimation method and 
-true proportion of liars in the sample (True $L/N$), for $N$ of 10 and 50. The Bayesian method is best 
-for all values of $L/N$ up to 80%.
-
-```{r errors-by-true-prop, fig.cap = "Errors by method and true proportion of liars, N = 10 and 50", fig.align="centre"}
+true proportion of liars in the sample (*Liars*), for *N* of 10 and 50. The Bayesian method is best 
+for all values of *Liars* up to 80%.
+
+```{r errors-by-true-prop, fig.cap = "Errors by method and true proportion of liars, N = 10 and 50", fig.align="left", fig.width=5.5, fig.height=4}
 errors_true_prop <- sim_est %>%       
@@
       ) %>% 
-      rename(`True L/N` = true_prop, Method = method)
-
-g <- ggplot(errors_true_prop, aes(`True L/N`, mean_sq_error, colour = Method)) + 
+      rename(`Liars` = true_prop, Method = method)
+
+g <- ggplot(errors_true_prop, aes(`Liars`, mean_sq_error, colour = Method)) + 
       ylab("Mean square error") + 
@@
 
-```{r errors-disagg, include = FALSE, fig.align="centre", fig.cap="Point estimate errors by R/N, N and P"}
+```{r errors-disagg, include = FALSE, fig.align="left", fig.width=5.5, fig.height=4, fig.cap="Point estimate errors by R/N, N and P"}
 
@@
 
+\newpage
+
 # References

### 2018-11-01 GSV-comment-brief.Rmd
make sure we pick up latest csv from home directory

@@
 mainfont: Times New Roman
+mathfont: Times New Roman
 ---
@@
 
+  path_root <- paste0("GSV-sims", if (sample_from_pop) "-pop-sample")
+
 if (rewrite_csv) {
-  path <- paste0("GSV-sims", if (sample_from_pop) "-pop-sample", ".csv")
-
-  readr::write_csv(sim_output, path = path)
+  readr::write_csv(sim_output, path = paste0(path_root, ".csv"))
 
@@
 
-gsv_estimates <- suppressMessages(readr::read_csv(normalizePath("~/sim-outputOutput.csv")))
+output_path <- paste0(path_root, "Output.csv")
+gsv_estimates <- suppressMessages(readr::read_csv(normalizePath(paste0("~/", output_path))))
 

### 2018-11-01 bayesian-heads-cts.R
New functions: Bayesian updating continuous distributions over lambda

@@ -1,0 +1,71 @@
+
+# Bayesian ways to calculate the probability of people in a sample reporting heads 
+# when they observe tails
+
+is_prob <- function (p) all(p >= 0 & p <= 1)
+
+#' Calculate the probability of observing `heads`
+#' good outcomes out of `N` total outcomes, conditional
+#' on subjects lying with prob `lambda` if they see heads.
+#'
+#' @param lambda Prob of lying. 
+#' @param heads Number of heads reported
+#' @param N Total number in sample
+#' @param P Probability of *bad* outcome
+#'
+#' @return A vector of probabilities
+#'
+#' @examples
+prob_report_given_lambda <- function (lambda, heads, N, P) {
+  stopifnot(is_prob(lambda), 0 <= heads, heads <= N, is_prob(P))
+
+  # on average, heads are reported 1-P + P*lambda of the time
+  dbinom(heads, N, 1 - P + lambda * P)
+}
+
+
+try_integral <- function(f, a, b, npoints = 100) {
+  integ <- stats::integrate(f, a, b, subdivisions = npoints) # numerical integration
+  if (integ$message != "OK") stop("stats::integrate failed with message: ", integ$message)
+  
+  return(integ$value)
+}
+
+#' Calculate posterior of lambdas given prior, and heads reports of good
+#' outcome
+#'
+#' @inherit prob_report_given_lambda params
+#' @param prior Prior over lambda. A function which takes a vector of values between 0 and 1, 
+#'   and returns the probability density
+#' @param npoints How many points to integrate on?
+#'
+#' @return A vector of posterior probabilities
+#'
+#' @examples
+update_prior <- function(heads, N, P, prior, npoints = 1e3) {
+  stopifnot(heads <= N, heads >= 0, is_prob(P), is.function(prior))
+
+  f <- function (lprime) prior(lprime) * prob_report_given_lambda(lprime, heads, N, P)
+  integ <- try_integral(f, 0, 1)
+  denominator <- integ
+  
+  posterior <- function(lambda) {
+    prob_report_given_lambda(lambda, heads, N, P) * prior(lambda)/denominator
+  }
+  
+  return(posterior)
+}
+
+mean_dist <- function (dist) {
+  stopifnot(is.function(dist))
+  
+  f <- function (x) x * dist(x)
+  EV <- try_integral(f, 0, 1)
+
+  return(EV)
+}
+
+interval_prob <- function (dist, l, r) {
+  stopifnot(l <= r, is.function(dist))
+  try_integral(dist, l, r)
+}

### 2018-11-02 bayesian-heads-cts.R
New difference_dist and dist_quantile functions

@@ -2,7 +2,6 @@
 # Bayesian ways to calculate the probability of people in a sample reporting heads 
 # when they observe tails
 
-is_prob <- function (p) all(p >= 0 & p <= 1)
 
 #' Calculate the probability of observing `heads`
 #' good outcomes out of `N` total outcomes, conditional
@@ -56,16 +55,113 @@ update_prior <- function(heads, N, P, prior, npoints = 1e3) {
   return(posterior)
 }
 
-mean_dist <- function (dist) {
+
+
+#' Estimate probability that two samples s1, s2 from 2 independent distributions have s1 > s2
+#'
+#' @param dist1 
+#' @param dist2 
+#'
+#' @return A probability scalar
+#' @export
+#'
+#' @examples
+compare_dists <- function (dist1, dist2) {
+  outer_f <- function (l1) {
+    dist1(l1) * dist_prob_within(dist2, 0, l1)
+  }
+  outer_f <- Vectorize(outer_f)
+  prob_1_more <- try_integral(outer_f, 0, 1)
+  
+  return(prob_1_more)
+}
+
+
+#' Given dist1 and dist2, find the pdf of dist1 - dist2
+#' 
+#' At the moment this only works when dist1 and dist2 are defined on [0, 1].
+#' 
+#' @param dist1,dist2 Probability distribution functions 
+#'
+#' @return A probability distribution function defined on [-1, 1].
+#' 
+#' @examples
+difference_dist <- function (dist1, dist2) {
+  
+  # prob l1 - l2 = d is integral from 0 to 1-d of dist1(z+d)*dist2(z)
+  # l1 - l2 = -.5; l1 = l2 + .5; integral from .5 to 1 of dist1(z + d)*dist2(z)
+  dd_fun <- function (d) {
+    stopifnot(d >= -1 && d <= 1)
+    dist_prob <- function(x) dist1(x + d) * dist2(x)
+    dist_prob <- Vectorize(dist_prob)
+    ends <- if (d > 0) c(0, 1 - d) else c(-d, 1)
+    try_integral(dist_prob, ends[1], ends[2])
+  }
+  
+  return(Vectorize(dd_fun))
+}
+
+
+#' Find mean of a probability distribution function
+#'
+#' @param dist A one-argument function
+#' @param l Minimum value
+#' @param r Maximum value
+#'
+#' @return A scalar
+#'
+#' @examples
[…]

### 2018-11-02 GSV-comment-brief.Rmd
Cleaner pipeline when you rerun the java; use new continuous Bayesian updating over lambda, and use population sampling approach

@@
 options(huxtable.knitr_output_format = "latex")
-source("bayesian-heads.R")
+source("bayesian-heads-cts.R")
 suppressPackageStartupMessages({
@@
   library(huxtable)
+  loadNamespace("MASS")
 })
@@
 
+# how many simulations to run:
 nreps <- 1000L
 
-# set to FALSE to recalculate all results; TRUE for speed:
-cache_results <- FALSE
-
-# set to TRUE to (re)create the simulations CSV file:
-rewrite_csv <- FALSE
+# set to FALSE to recalculate all confidence interval estimates; TRUE for speed:
+cache_results <- TRUE
+
+# set to TRUE to (re)create the simulations CSV file, then stop:
+rerun_java <- FALSE
 
@@
 # If you change this, you may need to recreate the simulations CSV file
-sample_from_pop <- FALSE
+sample_from_pop <- TRUE
 
@@
 TODO XXX: point out the claims they make. Add your sims of when the posterior is wrong
-and intervals fail even for (R-T)/(N-T).
+and intervals fail even for (R-T)/(N-T). Convert to sampling from a cts distrib.
 
@@
 
-Some people are honest, while others will lie whenever it benefits them. We would like to understand
+Some people are honest, while others are likely to lie whenever it benefits them. We would like to understand
 the prevalence of lying, because dishonesty may be economically and socially harmful. Since we
@@
 
-  path_root <- paste0("GSV-sims", if (sample_from_pop) "-pop-sample")
-
-if (rewrite_csv) {
-  readr::write_csv(sim_output, path = paste0(path_root, ".csv"))
-
-  # the java only lets you select a document from your home directory
-  copied_to_home_dir_ok <- file.copy(path, normalizePath("~"), overwrite = TRUE)
+file_root <- paste0("GSV-sims", if (sample_from_pop) "-pop-sample")
+sim_output_file <- paste0(file_root, "Output.csv")
+if (rerun_java) {
+  sim_input_file <- paste0(file_root, ".csv")
+  readr::write_csv(sim_output, path = sim_input_file)
+
+  # the java only lets you select a document from your home directory X-o
+  copied_to_home_dir_ok <- file.copy(sim_input_file, normalizePath("~"), overwrite = TRUE)
   stopifnot(copied_to_home_dir_ok)
-  # now run java -jar LyingCalculator.jar from the LyingCalculator directory
-  # make sure the old output file (xxxOutput.csv) is deleted first, or it will be appended to!
+  stop(sprintf("Now run java -jar LyingCalculator.jar and input '%s'", sim_input_file),
+        " from your home directory.\n",
+        "Make sure the old output file is deleted first!\n",
+        sprintf("The java will create a new file called '%s'.\n", sim_output_file), 
+        "Leave it in your home directory, set `rerun_java` to FALSE and reknit this file.")
 }
@@
 
-output_path <- paste0(path_root, "Output.csv")
-gsv_estimates <- suppressMessages(readr::read_csv(normalizePath(paste0("~/", output_path))))
+gsv_estimates <- suppressMessages(readr::read_csv(normalizePath(file.path("~", sim_output_file))))
 
@@
 
-my_prior <- uniform_prior
-# alternative:
-# my_prior <- function (N) dbinom(0:N, N, p = 0.5)
+my_prior <- dunif
 
@@
                 P = .$P/100, 
-                prior = my_prior(.$N)
+                prior = my_prior
               )
@@
         ci_qs <- c(1/2 - ci/2, 1/2 + ci/2)
-        cis <- posterior_quantile(ci_qs, pstr)
+        cis <- dist_quantile(pstr, ci_qs)
         # calculate quantities as prop dishonest
         tibble(
-          EV.ubayes = posterior_mean(pstr)/.$N,
-          LB.ubayes = cis[1]/.$N, 
-          UB.ubayes = cis[2]/.$N
+          EV.ubayes = dist_mean(pstr),
+          LB.ubayes = cis[1], 
+          UB.ubayes = cis[2]
         )
@@
   dist_L <- dist_L_gsv(heads, N, P)
-  check_posterior(dist_L)
   stopifnot(length(dist_L) == heads + 1)
@@
 
-When comparing the dishonesty rates of different groups, a possible approach is to use the
-"empirical Bayes" method [@casella1985introduction]. This means that one estimates a common prior
-from the pooled data, before updating the prior for each individual group.
+When comparing the dishonesty rates of different groups, an interesting approach is to use the
+"empirical Bayes" method [@casella1985introduction]. This piece of statistical jiu-jitsu involves
+estimating a common prior from the pooled data, before updating the prior for each individual group.
 
@@
       )
-pooled_prop_liars <- mean(dfr$heads == 1) * 2 - 1
+
+pp <- MASS::fitdistr(nats$prop_liars, "beta", start = list(
+        shape1 = 1, shape2 = 1
+      ))
+pooled_prior <- function (x) dbeta(x, pp$estimate["shape1"], pp$estimate["shape2"])
 
@@
       P = 0.5, 
-      prior = dbinom(0:N, N, p = pooled_prop_liars)
+      prior = pooled_prior
   )
@@
 
-nat_means <- sapply(distribs, posterior_mean)
-nat_cis <- sapply(distribs, posterior_quantile, q = c(0.025, 0.975))
+nat_means <- sapply(distribs, dist_mean)
+nat_cis <- sapply(distribs, dist_quantile, probs = c(0.025, 0.975))
 rownames(nat_cis) <- c("ci.low", "ci.high")
@@
 
-nats %<>% 
-      mutate(
-        mean = mean/N,
-        ci.low = ci.low/N,
-        ci.high = ci.high/N
-      ) %>% 
-      arrange(mean)
+nats %<>% arrange(mean)
 
@@
 For example, @hugh2016honesty estimates the dishonesty rates of 15 nations using a coin flip
-experiment. The pooled estimate of the proportion of liars in the sample is given by *2R/N - 1* = 
-`r round(pooled_prop_liars, 2)`. With *N* = `r nrow(dfr)`, this will not be much affected by 
-sampling variation in the number of heads. We can use a binomial distribution with this as the prior.
+experiment. We can fit a beta distribution using the 15 observations of *2R/N - 1*. This will be
+our prior.
 
@@
 
-Results are shown in Figure \ref{fig:hj2016-pic}, with means and 95% confidence intervals. There
-is substantial shrinkage from the "naïve" per-country estimates found by calculating *2R/N - 1*
-separately for each country). One of the strengths of empirical Bayes,  as @casella1985introduction
-points out, is that it "anticipates regression to the mean". That is, as there is noise in the data,
-the most and least honest groups in the data probably had some extreme error terms. So the
-British people in the sample may be less honest, and the Chinese people more honest, than the per-group 
-data suggest.
+Results are shown in Figure \ref{fig:hj2016-pic}, with means and 95% confidence intervals. There is
+some "shrinkage" towards the pooled mean from the naïve per-country estimates found by calculating
+*2R/N - 1* separately for each country). One of the strengths of empirical Bayes,  as
+@casella1985introduction points out, is that it "anticipates regression to the mean". That is, as
+there is noise in the data, the most and least honest groups in the data probably had some extreme
+error terms. So the British people in the sample may be less honest, and the Chinese people more
+honest, than the per-group data suggest.
 
@@
 \[
-\sum_{L = 0}^{N_{1}} \sum_{M=0}^{N_{2}} Pr(L_{1} = L) Pr(L_{2} = M) \;
-  \mathbb{1}({\frac{L}{N_{1}} < \frac{M}{N_{2}})}
+\int^1_0 \int_0^{\lambda_1} \phi(\lambda_1)\phi(\lambda_2) \; \mathrm{d}\lambda_2 \mathrm{d}\lambda_1
 \]
@@
 
-This approach has a nice interpretation, analogous to the use of the null hypothesis in frequentist
-methods. We start from the belief that the proportion of liars is the same across all groups. The
-posterior then shows how much the evidence changes this belief.
-
-```{r country-comparisons}
-
-prob_country_less <- function (ctry1, ctry2) {
-  stopifnot(ctry1 %in% nats$resnat, ctry2 %in% nats$resnat)
-  N_1 <- nats$N[nats$resnat == ctry1]
-  N_2 <- nats$N[nats$resnat == ctry2]
-  heads_1 <- nats$heads[nats$resnat == ctry1]
-  heads_2 <- nats$heads[nats$resnat == ctry2]  
-  diff_dist <- compare_groups(heads1 = heads_1, N1 = N_1, heads2 = heads_2, N2 = N_2, P = 0.5)
-
-  prob_first_less <-sum(diff_dist$prob[diff_dist$diff < 0]) 
-  return(prob_first_less)
-}
-
-ctry_comp <- outer(nats$resnat, nats$resnat, Vectorize(prob_country_less))
+```{r country-comparisons, eval = FALSE}
+
+prob_country_more <- function (ctry1, ctry2) {
+  compare_dists(distribs[[ctry1]], distribs[[ctry2]])
+}
+
+ctry_comp <- outer(nats$resnat, nats$resnat, Vectorize(prob_country_more))
 diag(ctry_comp) <- NA
@@
       set_caption("Bayesian country comparisons. 
-            Cells give the probability that row country has fewer liars than column country.") %>% 
+            Cells give the probability that row country has higher \\lambda than column country.") %>% 
       set_label("tab:country-comparisons") %>% 
@@
 cc_hux
-```
-
-# The population
-
-So far we have been trying to estimate the proportion of *Liars* in the sample. In fact,
-we usually care about the proportion of liars in populations from which the sample is drawn. This
-adds another layer of randomness. When *N* is large, the sample distribution should approximate
-the population distribution and either frequentist or Bayesian approaches should work. Further
-simulations, not shown, suggest that Bayesian confidence intervals are less robust than frequentist ones
-in bounding the population proportion of *Liars* when the sample is randomly drawn from the population.
+
+```
 

### 2018-11-03 GSV-comment-brief.Rmd
Use posterior highest density region; split out GSV methods into separate file; remove different estimation targets; rewrite...

@@
 ---
-title: "Lies and the lying liars who tell them"
+title: "True lies"
 subtitle: "Comment on Garbarino, Slonim and Villeval (2018)"
@@
 >  Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability distribution 
->  of the number of liars in "coin flip" style experiments. However, their method  
->  gives misleading confidence intervals. I explain why, and describe two better
->  ways to calculate probability distributions.
+>  of the number of lies told in "coin flip" style experiments. I show that their estimates and
+>  confidence intervals are flawed. I explain why, and describe two better
+>  ways to estimate the probability distribution of the proportion of liars.
 
@@
 options(huxtable.knitr_output_format = "latex")
+
 source("bayesian-heads-cts.R")
+source("GSV-heads.R")
+
 suppressPackageStartupMessages({
   library(Hmisc)
-  library(magrittr)
+  library(MASS)
+
   library(dplyr)
   library(purrr)
+  library(broom)
+  library(readr)
+  library(magrittr)
   library(tidyr)
-  library(readr)
   library(ggplot2)
-  library(broom)
+
   library(huxtable)
-  loadNamespace("MASS")
+  library(hdrcde)
 })
@@
 huxtable::set_default_properties(position = "left", top_padding = 12, bottom_padding = 6)
+ggplot2::theme_set(theme_light())
+
 set.seed(19751027)
@@
 
-# if TRUE, the number of liars in each simulation is randomly drawn
-# from a population with `Liars` liars.
-# If FALSE, the number of liars is fixed at `Liars * N`.
-# If you change this, you may need to recreate the simulations CSV file
-sample_from_pop <- TRUE
-
-# if FALSE, use L/N as ground truth;
-# if TRUE, use (R-heads)/(N-heads):
-estimate_lies_not_liars <- FALSE
-
-if (sample_from_pop && estimate_lies_not_liars) {
-  stop("Can't estimate proportion of actual lies in population!")
-}
-
 params <-   list(
   N      = c(10, 50, 100, 500),
-  Liars = seq(0, 1, 0.1),
+  lambda = seq(0, 1, 0.1),
   P      = c(.2, .5, .8)
@@
 
-method_used_statement <- paste0("This paper can be recreated from the .Rmd file using different ",
-      "methods to calculate confidence interval coverage and squared errors. 'Ground ",
-      "truth' can be the population proportion of liars, the sample proportion of liars or ",
-      "the sample proportion of actual lies. Ground truth for the document you are reading was: ",
-        if (sample_from_pop) "the population proportion of liars." else 
-        if (estimate_lies_not_liars) "the sample proportion of actual lies." else 
-        "the sample proportion of liars."
-      )
-
-if (! sample_from_pop && ! estimate_lies_not_liars) method_used_statement <- ""
-
-```
-
-TODO XXX: point out the claims they make. Add your sims of when the posterior is wrong
-and intervals fail even for (R-T)/(N-T). Convert to sampling from a cts distrib.
-
-**`r method_used_statement`**
+```
+
+TODO XXX: point out the claims they make.
 
@@
 in a sample of size *N*, where the _bad_ outcome happens with probability *P*, we can estimate that
-a proportion $\frac{R/N - (1-P)}{P}$ are lying [@abeler2016preferences]. The problem with this approach is that the number of heads is not
+the following proportion are lying [@abeler2016preferences]:
+
+\begin{equation}
+\label{eqn:naive-estimator}
+\frac{R/N - (1-P)}{P}
+\end{equation}
+The problem with this approach is that the number of heads is not
 fixed. If we see 1 out of 3 people reporting heads, this method estimates there are less than zero
@@
   N      = params$N,
-  Liars = params$Liars,
+  lambda = params$lambda,
   P      = params$P
 )
-sim_data$Liars_pop_pct <- sim_data$Liars
 
@@
 
-if (sample_from_pop) {
-  sim_data %<>% 
-        group_by(N, Liars, P) %>% 
-        mutate(
-          Liars_sample = rbinom(n(), N, Liars)
-        ) %>% 
-        ungroup() %>% 
-        mutate(
-          Liars = Liars_sample,
-          Liars_sample = NULL
-        )
-} else { 
-  sim_data$Liars <- round(sim_data$Liars * sim_data$N, 0)
-}
-
-simulate_cointoss <- function (row) {
-  h_liars <- rbinom(1, row["Liars"], 1 - row["P"])
-  h_honest <- rbinom(1, row["N"] - row["Liars"], 1 - row["P"])
-  R <- row["Liars"] + h_honest
-  names(R) <- NULL
-  heads <- h_honest + h_liars
-  c(R = R, heads = heads)
-}
-
-results <- apply(sim_data, 1, simulate_cointoss)
-
-sim_data$R <- results["R", ]
-sim_data$heads <- results["heads",]
-
-sim_data <- sim_data %>% arrange(N, Liars, P)
+sim_data %<>% mutate(
+        heads = rbinom(nrow(.), N, 1 - P),
+        lies = rbinom(nrow(.), N - heads, lambda),
+        R    = heads + lies
+      )
+
+sim_data %<>% arrange(N, lambda, P)
 
 nci_levels <- length(ci_levels)
-sim_data <- sim_data[rep(seq_len(nrow(sim_data)), each = nci_levels), ]
+sim_data <- sim_data[rep(1:nrow(sim_data), each = nci_levels), ]
 sim_data$CI <- rep(ci_levels, nrow(sim_data)/nci_levels)
-
-sim_data$P <- sim_data$P * 100 # input has to be in %
 
@@
 # only printing out distinct lines
-sim_output <- sim_data %>% 
+sim_input <- sim_data %>% 
       select(N, R, P, CI) %>% 
@@
 
-file_root <- paste0("GSV-sims", if (sample_from_pop) "-pop-sample")
+file_root <- "GSV-sims"
 sim_output_file <- paste0(file_root, "Output.csv")
@@
   sim_input_file <- paste0(file_root, ".csv")
-  readr::write_csv(sim_output, path = sim_input_file)
+  # input has to be in percentages:
+  readr::write_csv(sim_input %>% mutate(P = P * 100), path = sim_input_file)
 
@@
 sim_data %<>% mutate(
-  expected_R = Liars + (1 - P/100) * (N - Liars)
+  expected_R = N * ((1 - P) + lambda * P)
 )
@@
 
-sim_est <- left_join(sim_est, gsv_estimates, by = c("N", "R", "P", "CI"))
+sim_est %<>% 
+      mutate(p_pct = round(P * 100, 0)) %>% 
+      left_join(gsv_estimates, by = c("N", "R", "p_pct" = "P", "CI")) %>% 
+      mutate(p_pct = NULL)
 
@@
 
-bayes_est <- sim_output %>% 
+bayes_est <- sim_input %>% 
       rowwise() %>% 
@@
                 N = .$N, 
-                P = .$P/100, 
+                P = .$P, 
                 prior = my_prior
               )
-        ci <- .$CI / 100
-        ci_qs <- c(1/2 - ci/2, 1/2 + ci/2)
-        cis <- dist_quantile(pstr, ci_qs)
+        cis <- suppressWarnings(dist_hdr(pstr, .$CI/100))
         # calculate quantities as prop dishonest
@@
       })
-bayes_est <- cbind(sim_output, bayes_est)
+bayes_est <- cbind(sim_input, bayes_est)
 sim_est <- left_join(sim_est, bayes_est, by = c("N", "P", "R", "CI"))
@@
 
-simple_est <- sim_output %>%
-      mutate(
-        EV.simple = heads_to_liars(R/N, P/100)
-      )
-
-heads_confints <- apply(sim_output, 1, function (row) {
+simple_est <- sim_input %>%
+      mutate(
+        EV.simple = heads_to_liars(R/N, P)
+      )
+
+heads_confints <- apply(sim_input, 1, function (row) {
   ci <- binom.test(row["R"], row["N"], conf.level = row["CI"]/100)$conf.int
-  res <- heads_to_liars(ci, row["P"]/100)
+  res <- heads_to_liars(ci, row["P"])
   names(res) <- c("LB.simple", "UB.simple")
@@
 
-```{r recalculate-gsv-functions}
-
-dist_L_gsv <- function(heads, N, P) {
-  # L liars means that T = heads - L
-  # T is distributed binomially conditional on being no more than `heads`
-  L = 0:heads
-  result <- rep(NA_real_, length(L))
-  result <- dbinom(heads - L, N, 1 - P) / sum(dbinom(L, N, 1 - P))
-
-  result
-}
-
-prop_liars <- function(L, heads, N) {
-  stopifnot(all(L <= heads), heads >= 0, heads <= N)
-  # for any number of liars L, reported heads, and N:
-  # true heads T = heads - L
-  # number observing low outcome = N - T
-  # proportion lying is L/(N-T)
-  T <- heads - L
-  prop_lied <- L/(N - T)
-  prop_lied[N == T] <- 1 # if everyone saw true heads, then   
-                         # we can't estimate how many might have
-                         # GSV code solves this by assuming 1
-
-  prop_lied
-}
-
-prop_liars_ci_gsv <- function (ci, heads, N, P) {
-  stopifnot(0 <= ci, ci <= 1, heads <= N, 0 <= heads, 0 <= P, P <= 1)
-
-  dist_L <- dist_L_gsv(heads, N, P)
-  stopifnot(length(dist_L) == heads + 1)
-
-  pl <- prop_liars(0:heads, heads, N)
-  stopifnot(length(pl) == heads + 1)
-
-  pl <- pl[dist_L > 0] # get rid of 0-probability events
-  dist_L <- dist_L[dist_L > 0]
-  dist_L <- dist_L[order(pl)]
-  pl <- sort(pl)
-
-  cdf <- cumsum(dist_L)
-
-  # we know pl is always positive, so represent that:
-  cdf <- c(0, cdf)
-  pl  <- c(0, pl)
-
-  tail <- (1 - ci)/2
-  # lower bound: no more than tail% of probability has less than this
-  lb_idx <- max(which(cdf <= tail)) # must exist since cdf starts at 0.
-  lb <- pl[lb_idx]
-
-  # upper bound: no more than 1-tail% of probability has more
-  ub_idx <- min(which(cdf >= 1 - tail))
-  ub <- pl[ub_idx]
-
-  return(c(lb, ub))
-}
-
-prop_liars_ev_gsv <- function(heads, N, P) {
-  dist_L <- dist_L_gsv(heads, N, P)
-  prop_lied <- prop_liars(0:heads, heads, N)
-  sum(dist_L * prop_lied)
-}
-```
-
-```{r check-gsv-posterior, eval = FALSE}
-
-# if we assume that liars are not uniformly distributed, the posterior of number of heads
-# is not like the prior
-N <- 10
-CI <- 0.9
-tmp <- replicate(10000, {
-  # L <- sample(1:N, 1) # for this, always accurate?
-  L <- rbinom(1, N, 0.1) # not many liars
-  HL <- rbinom(1, L, 0.5)
-  HNL <- rbinom(1, N-L, 0.5)
-  R <- L + HNL
-  H <- HL + HNL
-  c(L, R, H, N, CI, prop_liars_ci_gsv(CI, R, N, 0.5))
-})
-
-tmp <- as.data.frame(t(tmp))
-names(tmp) <- c('L', 'R', 'H', 'N', 'CI', 'cilo', 'cihi')
-tmp$lies_told <- with(tmp, (R-H)/(N-H))
-tmp$lies_in_ci <- tmp$cilo <= tmp$lies_told & tmp$lies_told <= tmp$cihi
-
-# the prior:
-ggplot(tmp, aes(H)) + geom_bar(aes(y = calc(prop))) + 
-  geom_line(data = tmp[tmp$R > quantile(tmp$R, 0.8), ], aes(H, calc(prop)))
-# the posterior is not the prior:
-hist(tmp$H, col = "grey", breaks = 0:N, freq = FALSE, ylim = c(0, 1))
-hist(tmp$H[tmp$R==10], breaks = 0:N, add= T, freq = FALSE, col = rgb(1,0,0,.5))
-
-# the posterior:
-lines(density(with(tmp, H[R > quantile(R, 0.9)])))
-
-# how accurate are we for different numbers of R.
-# NB you can also judge accuracy by different numbers of H, but I'm not sure that's fair as H is
-# an unknown parameter - maybe it is like saying "confidence interval coverage is way off when
-# the errors are big!"
-
-GSV_coverage <- tmp %>% group_by(R) %>% 
-  summarize(n_sims = n(), coverage = mean(lies_in_ci))
-
-tmp %<>% left_join(GSV_coverage, by = "R")
-
-scale_fac <- max(tmp$n_sims)
-ggplot(GSV_coverage, aes(R)) + 
-    geom_hline(yintercept = CI, linetype = 2) +
-    geom_line(aes(y = coverage), colour = "red") +
-    geom_line(aes(y = n_sims/scale_fac), colour = "grey") +
-    scale_y_continuous(sec.axis = sec_axis(~.*scale_fac, name = "N sims"))
-
-plot(GSV_coverage$R, GSV_coverage$coverage, type = "l")
-# number of cases:
-points(GSV_coverage$R, GSV_coverage$n_sims/max(GSV_coverage$n_sims), type = "h", col = "grey")
-
-table(low_coverage = tmp$coverage < 0.8, tmp$R > 60) %>% prop.table(2)
-```
-
 ```{r recalc-estimates, cache = cache_results}
 
-sim_tmp <- sim_output[, c("R", "N", "P", "CI")]
+sim_tmp <- sim_input[, c("R", "N", "P", "CI")]
 recalc <- apply(sim_tmp, 1, function (x) {
   x <- c(
-    prop_liars_ev_gsv(x["R"], x["N"], x["P"]/100),
-    prop_liars_ci_gsv(x["CI"]/100, x["R"], x["N"], x["P"]/100)
+    prop_liars_ev_gsv(x["R"], x["N"], x["P"]),
+    prop_liars_ci_gsv(x["CI"]/100, x["R"], x["N"], x["P"])
   )
@@
 
-# alternative "ground truths":
-if (estimate_lies_not_liars) {
 sim_est %<>% mutate(
-          true_prop = (R - heads)/(N - heads)
-        )
-} else if (sample_from_pop) {
-  sim_est %<>% mutate(
-          true_prop = Liars_pop_pct
-        )
-} else {
-  sim_est %<>% mutate(
-          true_prop = Liars/N
-        )
-}
-
-sim_est %<>% mutate(
-        within_ci = true_prop >= LB & true_prop <= UB,
-        error     = EV - true_prop,
+        within_ci = lambda >= LB & lambda <= UB,
+        error     = EV - lambda,
         error_sq  = error^2
@@
 parameters are shown in Table \ref{tab:params-table}. For each parameter combination, I ran 1000
-simulations. "Liars" always reported heads. Non-liars reported tails with probability *P* and
-heads otherwise. For each simulation and confidence interval, I computed whether the confidence interval 
-contained the true value of *L/N*. Table \ref{tab:coverage-overall} shows the results.
+simulations. $\lambda$ is the probability that an individual in the sample lies and report heads
+when they observe tails:
+
+\begin{equation}
+\label{eqn:lambda}
+\lambda = \textrm{Prob}(i \textrm{ reports heads}|i\textrm{ saw tails}).
+\end{equation}
+
+For each simulation and confidence interval, I computed whether the confidence interval contained
+the true value of $\lambda$. Table \ref{tab:coverage-just-gsv} shows the results.
 
@@
           "Sample size (N)", 
-          "Proportion of liars (L/N)", 
+          "Probability of lying ($\\lambda$)", 
           "Probability of bad random outcome (P)"
@@
           paste(params$N, collapse = ", "),
-          paste(params$Liars, collapse = ", "),
+          paste(params$lambda, collapse = ", "),
           paste(params$P, collapse = ", ")
@@
       set_caption("Parameter values") %>% 
+      set_escape_contents(everywhere, 1, FALSE) %>% 
       set_label("tab:params-table") %>% 
@@
 ht_just_gsv <- ht_overall[1:2,]
+label(ht_just_gsv) <- "tab:coverage-just-gsv"
 ht_just_gsv[1, 1] <- ""
@@
 
-By definition, 95% of 95% confidence intervals ought to contain the true value, on average. This
-is called "achieving nominal coverage". GSV
-intervals are far from this. The confidence intervals are too narrow. Further analysis shows that
-this problem holds across all simulated probabilities of the low outcome *P*, confidence
-levels, and sample sizes *N* (up to 500).^[See the appendix.]
+By definition, 95% of 95% confidence intervals ought to contain the true value, on average. This is
+called "achieving nominal coverage". GSV intervals are far from this. The confidence intervals are
+too narrow. This problem holds across all simulated probabilities of the low outcome, confidence
+levels, and sample sizes.^[See the appendix.]
 
@@
 
-\[
-Z_{T,R,N,p} = \frac{
-  \textrm{binom}(T,N,p)
+\begin{equation}
+\label{eqn:truncated-binom}
+\textrm{Prob}(T \textrm{ heads}| R; N, P) = \frac{
+  \textrm{binom}(T,N, 1 - P)
 }{
-  \sum^R_{k=0}\textrm{binom}(k,N,p)
+  \sum^R_{k=0}\textrm{binom}(k,N, 1 - P)
 }
-\]
-
-This is the binomial distribution, truncated at *R*, because by assumption, nobody "lies downward"
+\end{equation}
+
+This is the binomial distribution, truncated at *R* because by assumption, nobody "lies downward"
 and reports tails when they really saw heads.
 
-Next, from *T* the number of liars is calculated as *R-T*; and the proportion of liars is calculated
-as *(R-T)/(N-T)*, because *N-T* people saw the low outcome and had the chance to lie. Combining this
+Next, from *T* the number of lies told is calculated as $R - T$; and the proportion of lies told
+is:
+
+\begin{equation}
+\textit{Lies} = \frac{R-T}{N-T} 
+\end{equation}
+
+because $N - T$ people saw the low outcome and had the chance to lie. Combining this
 with the truncated binomial gives a cumulative distribution function of the proportion of liars.
-This can then be used to estimate means and confidence intervals.
-
-Putting these together, for *R = N = 10*, the estimated distribution of liars is calculated as follows:
-
-* With probability $\frac{1}{1024}$, there were really *T = 10* heads.
-Nobody lied in the sample.^[But  the proportion of people who lied *out of those who saw tails* is undefined, because noone saw tails.
-The
-GSV software seems to resolve this by fixing the proportion of lies to 100%.]
+This is then used to estimate means and confidence intervals.
+
+Putting these together, for $R = N = 10$, the estimated distribution of liars is calculated as follows:
+
+* With probability $\frac{1}{1024}$, there were really 10 heads. Nobody lied in the
+sample.^[But the proportion of people who lied *out of those who saw tails* is undefined, because
+noone saw tails. The GSV software seems to resolve this by fixing the proportion of lies to 100%.]
 
@@
 
-First, if 10 out of 10 heads are reported, you should learn two things. On the one hand, there
-are probably many liars in your sample. On the other hand, probably a lot of coins really landed heads.
-The probability distribution above does not take account of this. In particular, for *R = N*, 
-the equation above reduces to the binomial distribution. This is not correct.
-
-Second, more importantly, the GSV approach estimates the distribution of the proportion of 
-*lies actually told*, among the subsample of people who saw tails:
-
-\[
-\textit{Lies} = \frac{R-T}{N-T} 
-\]
-
-But usually, we are not interested in the proportion of
-lies actually told. We care about how many people in the sample *are liars*, who would lie if they
-saw tails:
-
-\[
-\textit{Liars} = \frac{L}{N}.
-\]
-
-We care about *Liars* not *Lies*, because *Lies* is just a noisy estimate of *Liars*: it is the
-number of liars who happened to see heads. It is a function of honesty and luck. We are interested
-in the honesty.^[There may be times when social scientists care about how many people actually
-lied, but I cannot think of many.]
-
-Suppose *R = 10* heads out of 10 are reported, and suppose 9 heads were really observed, *T = 9*.
-*Lies* is indeed 100%.  But it is 100% of 1 person
--- the only person who saw tails. That one person's behaviour is an unbiased estimate of the
-proportion of liars in the sample, *Liars*. But it is a very noisy estimate.
-
-The first problem means that when *R* is very high or low,
-the percentage of confidence intervals containing *Lies*
-may fall off sharply.^[Depending on the distribution of the number of liars *L*.]
-
-The second problem means that the percentage of confidence intervals containing *Liars*
-is almost always much less than the nominal coverage.
+```{r}
+
+heads_10 <- sim_est %>% 
+      filter(N == 10, R == 10, P == 0.5) %>% 
+      select(lambda, heads) 
+h10 <- heads_10$heads
+l10 <- heads_10$lambda
+
+inv_prob_h <- round(1/mean(h10 == 10), 0)
+inv_prob_h_l20 <- round(1/mean(h10[l10 == 0.2] == 10), 0)
+
+```
+
+First, if 10 out of 10 heads are reported, you should learn two things. On the one hand, there are
+probably many liars in your sample. On the other hand, probably a lot of coins really landed heads.
+The probability distribution in (\ref{eqn:truncated-binom}) does not take account of this. In
+particular, for *R = N*, it reduces to the binomial distribution. This is not correct. For example,
+in my simulations with $P = 0.5$, the probability that there were 10 heads when $R = N = 10$ was
+about 1 in `r inv_prob_h`, not 1 in 1024. When $\\lambda = 0.2$, it is about 1 in 
+`r inv_prob_h_l20`. The same is true at the other end of the scale: when *R* is low, we indeed learn
+that $T \le R$ but also that the overall distribution is not shaped like the prior.
+
+Second, more importantly, the GSV approach estimates *Lies*, the distribution of the proportion of 
+*lies actually told*, among the subsample of people who saw tails. But we are not usually interested
+in the proportion of lies actually told. We care about the probability that people in the
+sample would lie if they saw tails --  $\lambda$ in equation (\ref{eqn:lambda}). This $\lambda$ can
+be interpreted in different ways. It could be that on seeing a tail, each person in the sample lies
+with probability $\lambda$. Or it could be that the sample is drawn from a population of whom
+$\lambda$ are (always) liars, and $1 - \lambda$ are truth-tellers.
+
+The fact that some people saw heads, and had no reason to lie, is just a nuisance for estimation.
+Similarly, we are not interested, per se, in whether more lies were actually told in one group than
+another. Suppose that 9 out of 10 people saw heads. Only one person had a reason to lie, so by
+definition, *Lies* will be either 0 or 1. This will almost certainly be different from the value of
+*Lies* in another group where there were fewer heads. But that tells us very little, either about the 
+samples as a whole, or about the population they come from.
+
+*Lies* can be treated as an estimate of $\lambda$. It is unbiased, because the
+probability that people would lie if they saw tails is independent of the coin flip they actually
+see. But it can be a very noisy estimate. 
+Again, suppose 10 heads out of 10 are reported, and 9 heads were really observed. *Lies* is 100%. 
+But it is 100% of just one person.
+
+The first of these two problems means that the GSV distribution of *Lies* is wrong. In the appendix
+I show that their estimator can have substantial bias. In fact, it performs worse than the naïve
+estimator from (\ref{eqn:naive-estimator}), $\frac{R-(1-P)}{P}$.
+Also, the GSV confidence intervals do not always achieve nominal coverage of *Lies*.
+When the number of heads reported is either high or low, the percentage of confidence intervals containing *Lies* may fall below the nominal value.
+
+The second problem means that the GSV confidence intervals are not correct for $\lambda$. We can
+tell that the second problem matters, because GSV coverage of $\lambda$ is much worse than coverage 
+of *Lies*. Also, since the GSV estimator of *Lies* is biased, it is a biased estimator of
+$\lambda$.
 
@@
 as_huxtable(coverage_rn, add_colnames = TRUE) %>% 
-      set_caption("GSV confidence interval coverage by low and high R/N") %>% 
+      set_caption("GSV confidence interval coverage by proportion of heads reported") %>% 
       set_label("tab:coverage-rn") %>% 
@@
       set_number_format(-1, -1, list(pct_format)) %>% 
-      theme_plain()
+      theme_plain() %>% 
+      set_right_border(-1, 2, 0.4)
 ```
@@
 
-Can we do better? There are two alternative methods one might use to calculate confidence intervals.
-The first is simply to calculate confidence bounds for the proportion of
-heads that would be reported in the population, given the number that were reported in the sample. 
-One can then back out
-confidence bounds for the proportion of liars as $\frac{R/N - (1-P)}{P}$, as in
-@abeler2016preferences.^[Confidence bounds lower than 0 can be set to 0.]  As GSV point out, this
-assumes that the sample proportion of high outcomes was equal to its expected proportion. We'll see 
-whether this matters.
+Can we do better? Start with the probability of getting *R* reports of heads in total, given
+$\lambda$. Since individuals report heads either if they see heads with probability $1-P$, or if
+they see tails but lie, with probability $\lambda P$, this is just:
+
+\begin{equation}
+\textrm{Pr}(R|\lambda; N,P) = \textrm{binom}(R, N, (1 - P) + \lambda P)
+\end{equation}
+
+That immediately suggests the first method, which is to estimate the parameter of this distribution,
+$(1 - P) + \lambda P$, from the proportion of heads reported in the sample, then back out $\lambda$.
+This is the conventional method of e.g. @abeler2016preferences. It is justified if the sample is
+large, because this will lessen sampling variation in the proportion of actual heads observed.
+Similarly, if the sample is large enough, we can generate hypothesis tests for a value of $\lambda$
+-- e.g., zero -- by using the tails of the binomial distribution. And we can back out confidence
+bounds for $\lambda$ from confidence bounds for the population proportion of heads reported in the
+same way. As GSV point out, in small samples, this method runs the risk that the sample proportion
+of high outcomes will be different from its expected value.^[In particular, this method can estimate
+confidence bounds for $\lambda$ lower than 0. If so, we can set them to 0.]   We'll see whether this
+matters.
 
@@
 
-The second method is to use Bayes' rule. Start with a prior probability distribution over
-the number of liars *L*, *Pr(L)*. The posterior probability is then:
-
-\[
-\textrm{Pr}(L | R; N,P) = \frac{
-  \textrm{Pr}(R|L; N,P) \textrm{Pr}(L)
+The second method is to use Bayes' rule. Start with a prior probability density function over
+the probability of liars, $\phi(\lambda)$. The posterior probability is then:
+
+\begin{equation}
+\phi(\lambda | R; N,P) = \frac{
+  \textrm{Pr}(R|\lambda; N,P) \phi(\lambda)
 }{
-  \sum_{L'=0}^N \textrm{Pr}(R|L'; N,P) \textrm{Pr}(L')
+  \int_0^1 \textrm{Pr}(R|\lambda'; N,P) \phi(\lambda) \; \textrm{d}\lambda
 }
-\]
-
-where the probability of getting *R* reports of heads in total for given *L* is just
-the probability that the *N - L* honest people saw *R - L* heads:
-
-\[
-\textrm{Pr}(R|L; N,P) = \textrm{binom}(R - L, N - L,1 - P)
-\]
-
-One can then estimate the proportion of *Liars* as *L/N*. From
-this, one can derive confidence intervals and expected values in the usual way.
-
-For the estimation here, I used a uniform prior, with *Pr(L) =* $\frac{1}{N+1}$ for *L* in  0
-to *N*.
-
-I used these estimation methods on my simulated data. Results are shown in Table
+\end{equation}
+
+From this, one can derive confidence intervals and expected values in the usual way.^[R code
+to do this is available at https://github.com/hughjonesd/GSV-comment. ] Technically,
+they are Bayesian "credible" intervals. I use Highest Posterior Density intervals [@hyndman1996computing], rather than the central confidence interval. This allows the intervals
+to include endpoints of the distribution, which is important when e.g. testing for $\lambda = 0$.
+
+The Bayesian method requires a prior. Here, I used a uniform prior, $\phi(\lambda) = 1$ on $[0, 1]$.
+
+I ran these estimation methods on my simulated data. Results are shown in Table
 \ref{tab:coverage-allmethods}. Both frequentist and  Bayesian methods mostly achieve the nominal
@@
       theme_plain() %>% 
+      set_background_color(everywhere, 1, NA) %>% 
+      set_top_border(c(4, 6), everywhere, 0.4) %>% 
       set_bottom_border(6, 1, 0.4)
@@
       geom_linerange(aes(ymin = ci.low,ymax = ci.high)) +
-      geom_point(aes(y = prop_liars), shape = 4, size = 3) +
+      geom_point(aes(y = prop_liars), shape = 4, size = 3, colour = "red") +
       xlab("Nation") + ylab("Prop. liars") +
       viridis::scale_fill_viridis(option = "E", guide = FALSE) + 
-      theme_light() +
       coord_flip()
@@
 significant, partly because the pooled prior has made posterior confidence intervals narrower.
-
-```{r country-comparisons, eval = FALSE}
+Similarly, we can calculate the full distribution of the differences between countries.
+
+```{r country-comparisons}
 
@@
       set_caption("Bayesian country comparisons. 
-            Cells give the probability that row country has higher \\lambda than column country.") %>% 
+            Cells give the probability that the row country has higher proportion of liars.") %>% 
       set_label("tab:country-comparisons") %>% 
@@
 
+```{r GB-vs-RU-pic, fig.cap = "Probability distribution of difference in proportion of liars, GB vs RU", fig.width=4, fig.height=3, fig.align="left", eval = FALSE}
+
+diff_GB_RU <- difference_dist(distribs$GB, distribs$RU)
+curve(diff_GB_RU, xlim = c(-1, 1), ylab = "Density", xlab = expression(lambda[GB] - lambda[RU]))
+```
+
 # Conclusion
 
-These results suggest some simple recommendations when you are analysing a coin-flip
+These results suggest some recommendations when you are analysing a coin-flip
 style experiment.
@@
 1. Do not use the GSV confidence intervals, unless you are specifically interested in *Lies* rather
-  than *Liars*. Even in that case, be aware that the confidence intervals have low coverage for extreme
-  values of *R*.
-2. If your N is reasonably large, say at least 100, you can safely use standard frequentist 
-  confidence intervals and tests. If you are interested in the population from which the sample is drawn,
-  you should do so, as they are most robust.
-3. If your N is small and you are interested in the sample proportion of *Liars*, consider
-  Bayesian estimates. To estimate differences between subgroups, consider
-  empirical Bayes with a prior derived from the pooled sample.
-
-Lastly, here is a simple way to avoid these shenanigans. Ask a group of *N* experimental subjects, 
-not to flip a coin, but to draw a black or white ball, without replacement, from an urn containing 
-*N* balls, of which *T* are white. Pay them if they report a white ball. You will then know -- not
-estimate -- that the proportion of lies told is *(R-T)/(N-T)*, and this will also be the proportion
-of liars, in a sample of *N-T* subjects. So you can simultaneously estimate the proportion of
-*Lies*, and of the lying *Liars* who tell them.
+  than $\lambda$. Even in that case, be aware that the confidence intervals have low coverage for 
+  extreme values of *R*.
+
+2. Do not use the GSV estimates. They are biased as estimators of both *Lies* and $\lambda$.
+
+3. If your N is reasonably large, say at least 100, you can safely use standard frequentist 
+  confidence intervals and tests.
+
+4. If your N is small, consider Bayesian estimates and confidence intervals. To estimate differences 
+  between subgroups, consider empirical Bayes with a prior derived from the pooled sample.
+
+Lastly, I suggest a simple way to avoid these statistical shenanigans. Ask a group of *N*
+experimental subjects, not to flip a coin, but to draw a black or white ball, without replacement,
+from an urn containing *N* balls, of which *T* are white. Pay them if they report a white ball. You
+will then know -- not estimate -- that the proportion of lies told is $(R - T)/(N - T)$, and this
+will also be the proportion of liars, in a sample of exactly $N - T$ subjects. So you can
+simultaneously estimate the proportion of lies, and of the lying liars who tell them.
 
@@
 
-R code to reproduce this comment is available at https://github.com/hughjonesd/GSV-comment. You
-can also rerun the simulations to test confidence interval coverage of *Lies*, of *Liars*, or
-of *Liars* in a population from which samples are drawn. Lastly, I provide code to find Bayesian
-posterior distributions of *Liars*.
+```{r methods-scale}
+
+scale_colour_methods <- scale_color_brewer(type = "qual", palette = 2)
+```
+
+R code to reproduce this comment is available at https://github.com/hughjonesd/GSV-comment, along with
+code to find Bayesian posterior distributions of $\lambda$.
 
@@
 method, but I could not reproduce their confidence intervals. For example, 
-when *R = 3, N = 6, P = 0.5*, GSV's Java program gives the upper bound of the 95% confidence 
-interval for the proportion of liars as 49.91%. But the possible proportions of liars when there
-are *T=0,1,2,3* true heads, are *(R-T)/(N-T) =* 
+when $R = 3, N = 6, P = 0.5$, GSV's Java program gives the upper bound of the 95% confidence 
+interval for the proportion of liars as 49.91%. But the possible proportions of lies when there
+are $T = 0, 1, 2, 3$ true heads, are $(R-T)/(N-T) =$
 `r paste0(prop_liars(3:0, 3, 6) * 100, "%", collapse = ", ")`.
@@
 
-Figure \ref{fig:coverage-pic} shows the proportions of true values within the confidence interval
-for the GSV method, split by *N*, *P* and confidence level. Dashed lines show the nominal confidence
-level.
-
-Figure \ref{fig:coverage-grp-pic} splits this still further, by the true proportion of liars within
-each simulation. This makes the pattern clear: coverage gets worse as the proportion of liars
-increases (until 100% where it jumps back up as results become deterministic).
-
-```{r coverage-pic, fig.cap = "GSV confidence interval coverage by confidence level, N and P", fig.width=5.5, fig.height=4, fig.align="left"}
-
-coverage_treat_gsv <- sim_est %>% 
-      filter(method == "gsv") %>% 
-      group_by(CI, N, P) %>% 
+Figure \ref{fig:coverage-grp-pic} shows the proportions of true values within the confidence interval
+for the GSV method, split by *N*, *P*, confidence level and $\lambda$. Dashed lines show the nominal
+confidence level. This makes the pattern clear: coverage gets worse as $\lambda$ increases. (At
+100%, coverage jumps back up since results become deterministic). Also, coverage does not get
+better as *N* increases.
+
+```{r coverage-grp-pic, fig.cap = "GSV confidence interval coverage by confidence level, N, P and $\\lambda$", fig.align="left", fig.width=6, fig.height=4}
+
+pic_method <- "gsv"
+# pic_method <- "ubayes"
+
+coverage_grp_gsv <- sim_est %>% 
+      filter(method == pic_method) %>% 
+      group_by(CI, N, lambda, P) %>% 
       summarize(mean_in_ci = mean(within_ci, na.rm = TRUE)) %>% 
@@
       mutate(
-        P = factor(paste0(P, "%")),
+        P = factor(P),
         ci = CI,
@@
 
-ggplot(coverage_treat_gsv, aes(P, mean_in_ci, colour = P)) +
-      geom_point(size = 2) +  
+ggplot(coverage_grp_gsv, aes(lambda, mean_in_ci, colour = P)) +
+      geom_point() + geom_line() +
       geom_hline(aes(yintercept = ci/100), linetype = 2) +
       facet_grid(N ~ CI, labeller = "label_both") +
-      xlab("Probability of low outcome (P)") + ylab("Proportion within C.I.")
-```
-
-```{r coverage-grp-pic, fig.cap = "GSV confidence interval coverage by confidence level, N, P and true proportion of liars", fig.align="left", fig.width=6, fig.height=4}
-
-coverage_grp_gsv <- sim_est %>% 
-      filter(method == "gsv") %>% 
-      group_by(CI, N, Liars, P) %>% 
-      summarize(mean_in_ci = mean(within_ci, na.rm = TRUE)) %>% 
+      xlab(expression(lambda)) + ylab("Coverage")
+
+```
+
+Figure \ref{fig:bias-by-lambda-pic} shows the average bias of expected values by different methods.
+At N = 500, all methods perform reasonably well. For lower values, there is a clear pattern: 
+Bayesian methods are least biased, GSV method is most biased, and the frequentist method is
+in between.
+
+```{r bias-by-lambda-pic, fig.cap = "Bias by method and $\\lambda$", fig.align="left", fig.width=5.5, fig.height=4}
+
+bias_lambda <- sim_est %>%       
+      filter(CI == 90) %>% 
+      group_by(method, N, P) %>% 
+      summarize(Bias = mean(error, na.rm = TRUE)) %>% 
       ungroup() %>% 
       mutate(
-        P = factor(paste0(P, "%")),
-        ci = CI,
-        CI = paste0(CI, "%")
-      )
-
-g <- ggplot(coverage_grp_gsv, aes(Liars/N, mean_in_ci, colour = P)) +
-      geom_hline(aes(yintercept = ci/100), linetype = 2) +
-      facet_grid(N ~ CI, labeller = "label_both") +
-      xlab("Liars") + ylab("Proportion within C.I.")
-
-if (sample_from_pop) g + geom_smooth(method = "loess") else g + geom_point() + geom_line()
-
-```
-
-Figure \ref{fig:errors-by-true-prop} shows mean squared error by estimation method and 
-true proportion of liars in the sample (*Liars*), for *N* of 10 and 50. The Bayesian method is best 
-for all values of *Liars* up to 80%.
-
-```{r errors-by-true-prop, fig.cap = "Errors by method and true proportion of liars, N = 10 and 50", fig.align="left", fig.width=5.5, fig.height=4}
-errors_true_prop <- sim_est %>%       
+        method = recode(method, gsv = "GSV", simple = "Frequentist", ubayes = "Bayesian")
+      ) %>% 
+      rename(Method = method)
+
+ggplot(bias_lambda, aes(Method, Bias, colour = Method)) + 
+      geom_point() + scale_x_discrete(breaks = NULL) +
+      facet_grid(N ~ P, labeller = "label_both", scales = "free") +
+      xlab("") +
+      scale_colour_methods
+
+```
+
+Figure \ref{fig:errors-by-true-prop} shows mean squared error by estimation method and $\lambda$,
+for *N* of 10 and 50. The Bayesian method is best for all values of *Liars* up to 80%.
+
+```{r errors-by-true-prop, fig.cap = "Errors by method and $\\lambda$, N = 10 and 50", fig.align="left", fig.width=5.5, fig.height=4}
+
+errors_lambda <- sim_est %>%       
       filter(CI == 90, N <= 50) %>% 
-      group_by(method, true_prop) %>% 
+      group_by(method, lambda) %>% 
       summarize(mean_sq_error = mean(error_sq, na.rm = TRUE)) %>% 
@@
       ) %>% 
-      rename(`Liars` = true_prop, Method = method)
-
-g <- ggplot(errors_true_prop, aes(`Liars`, mean_sq_error, colour = Method)) + 
-      ylab("Mean square error") + 
-      scale_x_continuous(breaks = 0:5/5)
-
-# proportion of liars is set to 0:10/10, but of lies is random,
-# so we have to use a smoothing line
-if (estimate_lies_not_liars) g + geom_smooth(method="loess") else 
-      g + geom_line() + geom_point()
+      rename(Method = method)
+
+ggplot(errors_lambda, aes(lambda, mean_sq_error, colour = Method)) + 
+      scale_x_continuous(breaks = 0:5/5) + 
+      geom_line() + geom_point() +
+      scale_colour_methods + 
+      xlab(expression(lambda)) + ylab("Mean square error")
 
@@
 g <- ggplot(errors_disagg, aes(`R/N`, mean_sq_error, colour = Method)) + 
-      ylab("Mean square error") + facet_wrap(~N + P, scales = "free_y")
-
-if (estimate_lies_not_liars) g + geom_smooth(method="loess") else 
-      g + geom_line() + geom_point()
+      geom_line() + geom_point() +
+      facet_wrap(~N + P, scales = "free_y") + 
+      scale_colour_methods +
+      ylab("Mean square error")
+
+```
+
+```{r gsv-lies-coverage, cache = cache_results}
+
+# if we assume that liars are not uniformly distributed, the posterior of number of heads
+# is not like the prior
+nreps_l <- 2000L
+
+check_coverage_lies <- function(N, CL, lambda, P) {
+
+  L <- rbinom(nreps_l, N, lambda) # how many people will lie if they see tails?
+  HL <- rbinom(nreps_l, L, 1 - P)
+  HNL <- rbinom(nreps_l, N - L, 1 - P)
+  R <- L + HNL
+  TH <- HL + HNL
+  sim_inputs <- data.frame(L, R, TH, N, CL, P, lambda, row.names = NULL)
+
+  sim_in_uq <- distinct(sim_inputs[, c("CL", "R", "N", "P")])
+  sim_results <- apply(sim_in_uq, 1, function (r) {
+    with(as.list(r), 
+      c(prop_liars_ev_gsv(R, N, P), prop_liars_ci_gsv(CL, R, N, P))
+    )
+  })
+  sims_in_uq <- cbind(sim_in_uq, t(sim_results))
+
+  sims <- left_join(sim_inputs, sims_in_uq, by = names(sim_in_uq))
+  names(sims) <- c('L', 'R', 'TH', 'N', 'CL', 'P', 'lambda', 'ev', 'cilo', 'cihi')
+
+  return(sims)
+}
+
+# reuse our parameters
+lies_params <- tidyr::crossing(
+        N      = params$N,
+        lambda = params$lambda,
+        P      = params$P,
+        CL     = ci_levels/100
+      )
+
+lies_sims <- apply(lies_params, 1, function (x) check_coverage_lies(
+      x["N"], x["CL"], x["lambda"], x["P"]))
+lies_sims <- bind_rows(lies_sims)
+lies_sims <- right_join(lies_params, lies_sims, by = names(lies_params))
+
+lies_sims %<>% 
+      mutate(
+        cl          = CL,
+        CL          = paste("CI: ", CL * 100, "%"),
+        ci_width    = cihi - cilo,
+        lies_told   = (R - TH)/(N - TH),
+        lies_in_ci  = cilo <= lies_told & lies_told <= cihi,
+        error       = ev - lies_told,
+        naive_ev    = pmax(0, (R/N - (1 - P))/P),
+        naive_error = naive_ev - lies_told,
+        P = factor(P)
+      ) %>% 
+      group_by(P, N, lambda) %>% 
+      mutate(
+        # within-group quantiles
+        RN = ntile(R/N, 10)
+      ) %>% 
+      ungroup()
+
+# confints ought to look like real dist, over R, N and P.
+qs <- c(0.005, 0.025, 0.05, 0.95, 0.975, 0.995)
+lies_sims %<>% group_by(R, N, P) %>%
+      do(lies_quantiles = quantile(.$lies_told, qs, na.rm = TRUE)) %>% 
+      unnest(lies_quantiles) %>% 
+      mutate(quantile = paste0("q", rep_len(qs, nrow(.)))) %>% 
+      spread(quantile, lies_quantiles) %>% 
+      inner_join(lies_sims, by = c("R", "N", "P")) %>% 
+      mutate(
+        true_cihi = case_when(
+          cl == 0.99 ~ q0.995,
+          cl == 0.95 ~ q0.975,
+          cl == 0.90 ~ q0.95
+        ),
+        true_cilo = case_when(
+          cl == 0.99 ~ q0.005,
+          cl == 0.95 ~ q0.025,
+          cl == 0.90 ~ q0.05
+        )
+      ) %>% 
+      select(-starts_with("q0"))
+
+```
+
+## GSV as an estimate of *Lies*
+
+GSV argue that their method provides a good estimate of *Lies*, as opposed to $\lambda$. Here
+I check whether that is true.
+
+I ran `r nreps_l` simulations for each of the parameter combinations. I calculated *Lies* as
+*(R - T)/(N - T)*, and ignored simulations where *N = T*. I estimated confidence intervals and
+expected value using the GSV method. For a comparison I also estimated the expected value of 
+*Lies* using the "naïve" estimator $\max(0, \frac{R - (1 - P))}{P})$.
+
+Figure \ref{fig:gsv-lies-bias-pic} shows average bias by sample size, *P* and true *Lies*. For low
+sample sizes, both methods perform about the same. For higher sample sizes and low values of *Lies*, however, the GSV method is clearly dominated by the naïve method, and shows a lot of upward bias
+-- more than 5 percentage points even when *N = 100*. This is especially problematic for testing 
+whether anyone lied in the sample.
+
+```{r gsv-lies-bias-pic, fig.cap = "Bias of GSV method for 'Lies'.", fig.align="center", fig.width=5.5, fig.height=4, warning=FALSE}
+
+lies_sims$lt_cut <- cut(lies_sims$lies_told, 0:10/10, labels = FALSE)
+
+my_alph <- 0.8
+g <- ggplot(lies_sims, aes(lt_cut, error, color = "GSV", linetype = "GSV")) + 
+      stat_summary(fun.y = mean, geom = "point", alpha = my_alph) + 
+      stat_summary(group = 1, fun.y = mean, geom = "line", alpha = my_alph) + 
+      stat_summary(aes(y = naive_error, color = "Naive"), fun.y = mean, geom = "point", 
+            alpha = my_alph) + 
+      stat_summary(aes(y = naive_error, linetype = "Naive", color = "Naive"), group=1, fun.y = mean, 
+            geom = "line", alpha = my_alph) + 
+      facet_grid(N ~ P, labeller = "label_both", scales = "free_y")
+g +
+      geom_hline(yintercept = 0) +
+      scale_x_continuous(breaks = seq(0, 10, 2), labels = seq(0, 1, 0.2)) +
+      scale_linetype_discrete(name = "Method", guide = guide_legend(title = "Method")) +
+      scale_color_manual(name = "Method", values = c("darkred", "blue")) +
+      xlab("Lies") + ylab("Bias") 
+```
+
+Figure \ref{fig:gsv-lies-coverage-pic} shows the proportion of confidence intervals that contain the true
+value of *Lies*. Coverage is shown by confidence level, *N*, *P* and the decile (within these groups) of
+proportion of heads reported (*R/N*). Overall results are quite solid, but when the proportion of
+heads reported is low or high, coverage drops below the nominal intervals. Interestingly, this problem
+gets worse as $N$ increases.
+
+```{r gsv-lies-coverage-pic, fig.cap = "Coverage of GSV method for 'Lies'.", fig.align="center", fig.width=5.5, fig.height=4}
+
+# you can do this to find where confints are wrong. If the red line is above the diagonal,
+# cilo is too high; if the blue line is below it, cihi is too low.
+# ggplot(lies_sims) + 
+#       geom_smooth(aes(true_cihi, cihi), color = "blue") + 
+#       geom_smooth(aes(true_cilo, cilo), color = "red") + 
+#       geom_abline(slope = 1, intercept = 0) + 
+#       facet_grid(N ~ CL) + theme_minimal() + xlab("True bound") + 
+#       labs(title = "Red line: low ci; blue line: high ci")
+
+# lsims_summary <- lies_sims %>% 
+#       group_by(lambda, P, N, CI, ci) %>% 
+#       summarize(
+#         Coverage = mean(lies_in_ci, na.rm = TRUE)
+#       )
+
+# ggplot(lsims_summary, aes(lambda, Coverage, colour = P)) + 
+#       geom_point() + geom_line() + 
+#       geom_hline(aes(yintercept = ci), linetype = 2) +
+#       facet_grid(N ~ CI) + xlab(expression(lambda))
+
+lsims_by_R <- lies_sims %>% 
+      group_by(P, N, CL, RN, cl) %>%   # having cl keeps it in the data
+      summarize(
+        Coverage = mean(lies_in_ci, na.rm = TRUE)
+      )
+
+ggplot(lsims_by_R, aes(RN, Coverage, colour = P)) + 
+      geom_point() + geom_line() + 
+      geom_hline(aes(yintercept = cl), linetype = 2) +
+      facet_grid(CL ~ N, scales = "free", labeller = "label_both") +
+      xlab("R/N (decile)") + 
+      scale_x_continuous(breaks = 0:5 * 2)
+
 ```

### 2018-11-03 GSV-heads.R

@@ -1,0 +1,67 @@
+
+# functions to compute distributions of lies told in coin flip experiments, according to GSV (2018).
+# WARNING: IMHO these methods are flawed, use at your own risk!
+
+
+dist_L_gsv <- function(heads, N, P) {
+  # L liars means that T = heads - L
+  # T is distributed binomially conditional on being no more than `heads`
+  L = 0:heads
+  result <- rep(NA_real_, length(L))
+  result <- dbinom(heads - L, N, 1 - P) / sum(dbinom(L, N, 1 - P))
+  
+  result
+}
+
+prop_liars <- function(L, heads, N) {
+  stopifnot(all(L <= heads), heads >= 0, heads <= N)
+  # for any number of liars L, reported heads, and N:
+  # true heads T = heads - L
+  # number observing low outcome = N - T
+  # proportion lying is L/(N-T)
+  T <- heads - L
+  prop_lied <- L/(N - T)
+  prop_lied[N == T] <- 1 # if everyone saw true heads, then   
+  # we can't estimate how many might have
+  # GSV code solves this by assuming 1
+  
+  prop_lied
+}
+
+prop_liars_ci_gsv <- function (ci, heads, N, P) {
+  stopifnot(0 <= ci, ci <= 1, heads <= N, 0 <= heads, 0 <= P, P <= 1)
+  
+  dist_L <- dist_L_gsv(heads, N, P)
+  stopifnot(length(dist_L) == heads + 1)
+  
+  pl <- prop_liars(0:heads, heads, N)
+  stopifnot(length(pl) == heads + 1)
+  
+  pl <- pl[dist_L > 0] # get rid of 0-probability events
+  dist_L <- dist_L[dist_L > 0]
+  dist_L <- dist_L[order(pl)]
+  pl <- sort(pl)
+  
+  cdf <- cumsum(dist_L)
+  
+  # we know pl is always positive, so represent that:
+  cdf <- c(0, cdf)
+  pl  <- c(0, pl)
+  
+  tail <- (1 - ci)/2
+  # lower bound: no more than tail% of probability has less than this
+  lb_idx <- max(which(cdf <= tail)) # must exist since cdf starts at 0.
+  lb <- pl[lb_idx]
+  
+  # upper bound: no more than 1-tail% of probability has more
+  ub_idx <- min(which(cdf >= 1 - tail))
+  ub <- pl[ub_idx]
+  
[…]

### 2018-11-03 bayesian-heads-cts.R

@@ -2,6 +2,7 @@
 # Bayesian ways to calculate the probability of people in a sample reporting heads 
 # when they observe tails
 
+library(hdrcde)
 
 #' Calculate the probability of observing `heads`
 #' good outcomes out of `N` total outcomes, conditional
@@ -145,6 +146,48 @@ dist_quantile <- function(dist, probs) {
   })
   
   return(qs)
+}
+
+
+#' Compute highest density region for a given confidence level
+#'
+#' This is a wrapper for `hdrcde::hdr`. The highest density region is the
+#' interval that covers `conf_level` of the data and has the highest
+#' average density. See:
+#' 
+#' Rob J Hyndman (1996) “Computing and graphing highest density regions”. American Statistician, 
+#' 50, 120-126.
+#' 
+#' 
+#' @param dist A one-argument function
+#' @param conf_level A scalar between 0 and 1
+#' @param hdr_workaround Another confidence level to workaround a bug in hdrcde::hdr. You
+#'   shouldn't need to set this unless you have an unusual distribution and `dist_hdr` gives
+#'    a warning; if so, try setting it to a smaller or larger value.
+#'
+#' @return A length 2 vector of 
+#'
+#' @examples
+dist_hdr <- function (dist, conf_level, hdr_workaround = 0.01) {
+  stopifnot(is_prob(conf_level), is.function(dist)) 
+  
+  density_est <- list(x = 0:1000/1000, y = dist(0:1000/1000))
+  
+  # we include prob 0.1 to make sure that result has two columns
+  result <- hdrcde::hdr(den = density_est, prob = c(100 * conf_level, 100 * hdr_workaround))
+  result <- result$hdr[1, ]
+  if (length(result) != 2) {
+    warning("hdrcde::hdr returned only one endpoint. Guessing which it is.")
+    if (isTRUE(all.equal(dist(0), 0))) result <- c(result, 1) else
+          if (isTRUE(all.equal(dist(1), 0))) result <- c(0, result) else
+          if (all(diff(density_est$y) >= 0)) result <- c(result, 1) else
+          if (all(diff(density_est$y) <= 0)) result <- c(0, result)
+    if (length(result) == 1) stop(
+            "Couldn't figure out which endpoint hdrcde::hdr returned. Try adjusting `hdr_workaround`")
+  }
+  result[is.na(result)] <- c(0, 1)[is.na(result)] 
+  
+  result
 }
 
 is_prob <- function (p) all(p >= 0 & p <= 1)

### 2018-11-03 GSV-comment-brief.Rmd
Use checkpoint; other textual tweaks

@@
 ---
-title: "True lies"
+title: "Lies and the lying liars who tell them"
 subtitle: "Comment on Garbarino, Slonim and Villeval (2018)"
@@
 
->  Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability distribution 
->  of the number of lies told in "coin flip" style experiments. I show that their estimates and
->  confidence intervals are flawed. I explain why, and describe two better
->  ways to estimate the probability distribution of the proportion of liars.
+> Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability
+> distribution of the proportion of lies told in "coin flip" style experiments. I show that their
+> estimates and confidence intervals are flawed. I demonstrate two better ways to estimate the 
+> probability distribution of what we are really interested in: the proportion of liars.
 
 ```{r setup, include = FALSE}
+
+library(checkpoint)
+checkpoint("2018-11-03")
 
@@
 # set to FALSE to recalculate all confidence interval estimates; TRUE for speed:
-cache_results <- TRUE
+cache_results <- FALSE
 
@@
 probably many liars in your sample. On the other hand, probably a lot of coins really landed heads.
-The probability distribution in (\ref{eqn:truncated-binom}) does not take account of this. In
-particular, for *R = N*, it reduces to the binomial distribution. This is not correct. For example,
-in my simulations with $P = 0.5$, the probability that there were 10 heads when $R = N = 10$ was
-about 1 in `r inv_prob_h`, not 1 in 1024. When $\\lambda = 0.2$, it is about 1 in 
+The probability distribution in equation (\ref{eqn:truncated-binom}) does not take account of this.
+In particular, for *R = N*, it reduces to the binomial distribution. This is not correct. For
+example, in my simulations with $P = 0.5$, the overall probability that there were 10 heads when $R
+= N = 10$ was about 1 in `r inv_prob_h`, not 1 in 1024. When $\lambda = 0.2$, it is about 1 in 
 `r inv_prob_h_l20`. The same is true at the other end of the scale: when *R* is low, we indeed learn
@@
 I show that their estimator can have substantial bias. In fact, it performs worse than the naïve
-estimator from (\ref{eqn:naive-estimator}), $\frac{R-(1-P)}{P}$.
-Also, the GSV confidence intervals do not always achieve nominal coverage of *Lies*.
-When the number of heads reported is either high or low, the percentage of confidence intervals containing *Lies* may fall below the nominal value.
+estimator from equation (\ref{eqn:naive-estimator}), $\frac{R-(1-P)}{P}$. Also, the GSV confidence
+intervals do not always achieve nominal coverage of *Lies*. When the number of heads reported is
+either high or low, the percentage of confidence intervals containing *Lies* may fall below the
+nominal value.
 
 The second problem means that the GSV confidence intervals are not correct for $\lambda$. We can
-tell that the second problem matters, because GSV coverage of $\lambda$ is much worse than coverage 
-of *Lies*. Also, since the GSV estimator of *Lies* is biased, it is a biased estimator of
-$\lambda$.
+tell that the second problem matters, because the confidence interval coverage of $\lambda$ is much
+worse than coverage of *Lies*. The GSV estimator is also a biased estimator of $\lambda$.
 
 ```{r disagg-coverage}
+
 disagg <- sim_est %>% 
@@
 The problem is especially bad when there are many reports of heads. In this case there were probably
-many true heads, so *T* is high and the true sample size *N - T* is low. Table \ref{tab:coverage-rn}
+many true heads, so *T* is high and the true sample size $N - T$ is low. Table \ref{tab:coverage-rn}
 shows this. It splits the simulations by the proportion of reported heads, *R/N*. Coverage levels
@@
       set_top_border(c(4, 6), everywhere, 0.4) %>% 
-      set_bottom_border(6, 1, 0.4)
+      set_bottom_border(6, 1, 0.4) %>% 
+      set_right_border(everywhere, 1, 0.4)
 ```
@@
       filter(CI == 90) %>% 
-      group_by(method, N) %>% 
+      mutate(
+        Method = recode(method, gsv = "GSV", simple = "Frequentist", ubayes = "Bayesian"),
+        method = NULL
+      ) %>% 
+      group_by(Method, N) %>% 
       summarize(mean_sq_error = mean(error_sq, na.rm = TRUE)) %>% 
@@
       ungroup() %>% 
-      mutate(
-        method = recode(method, gsv = "GSV", simple = "Frequentist", ubayes = "Bayesian")
-      ) %>% 
       as_huxtable(add_colnames = TRUE) %>% 
-      set_caption("Mean squared errors by method and N") %>% 
+      set_caption("Mean squared errors by method and $N$") %>% 
       set_label("tab:point-estimates") %>% 
@@
 nat_means <- sapply(distribs, dist_mean)
-nat_cis <- sapply(distribs, dist_quantile, probs = c(0.025, 0.975))
+nat_cis <- sapply(distribs, dist_hdr, conf_level = 0.95)
 rownames(nat_cis) <- c("ci.low", "ci.high")
@@
       xlab("Nation") + ylab("Prop. liars") +
-      viridis::scale_fill_viridis(option = "E", guide = FALSE) + 
+      scale_fill_viridis_c(option = "A", guide = "none") + 
+      theme_light()+
       coord_flip()

### 2018-11-03 GSV-comment-brief.Rmd
back to the politer title

@@
 ---
-title: "Lies and the lying liars who tell them"
+title: "True Lies:"
 subtitle: "Comment on Garbarino, Slonim and Villeval (2018)"

### 2018-11-05 GSV-comment-brief.Rmd
check differences between their results and my calculations; make GSV-heads correspond to what they say, not what they do; add bias table; add power calculations; update readme; stop using workaround for hdrcde::hdr (thanks @robjhyndman); look at benndorf et al. 2017

@@
 ---
-title: "True Lies:"
+title: "True Lies"
 subtitle: "Comment on Garbarino, Slonim and Villeval (2018)"
@@
 
+# how many simulations to run:
+nreps <- 1000L
+
+# set to FALSE to recalculate all confidence interval estimates; TRUE for speed:
+cache_results <- FALSE
+
+# set to TRUE to (re)create the simulations CSV file, then stop:
+rerun_java <- FALSE
+
+params <-   list(
+  N      = c(10, 50, 100, 500),
+  lambda = seq(0, 1, 0.1),
+  P      = c(.2, .5, .8)
+)
+
+ci_levels <- c(90L, 95L, 99L)
+
 library(checkpoint)
-checkpoint("2018-11-03")
+checkpoint("2018-11-03", scanForPackages = cache_results)
 
@@
 set.seed(19751027)
-
-# how many simulations to run:
-nreps <- 1000L
-
-# set to FALSE to recalculate all confidence interval estimates; TRUE for speed:
-cache_results <- FALSE
-
-# set to TRUE to (re)create the simulations CSV file, then stop:
-rerun_java <- FALSE
-
-params <-   list(
-  N      = c(10, 50, 100, 500),
-  lambda = seq(0, 1, 0.1),
-  P      = c(.2, .5, .8)
-)
-
-ci_levels <- c(90L, 95L, 99L)
 
@@
 
+# check we aren't too far from their calculations. 
+with(sim_est, stopifnot(
+        max(abs(EV.recalc - EV.gsv)) < 0.0001,
+        mean(abs(LB.recalc - LB.gsv)) < 0.05,
+        mean(abs(UB.recalc - UB.gsv)) < 0.05
+      ))
 ```
@@
 "heads" out of 10 for a fair coin flip (*R = N = 10, P = 0.5*). The resulting point estimate is that
-100% of subjects lied. The upper and lower 99% confidence intervals are also 100%. Naïvely, this might
-seem wrong. Can we rule out that 8 subjects lied, and the two honest subjects both saw heads?
-
-In fact, the GSV method works like this. First, given *R* reports of heads, the probability that a total 
-of *T* "true" heads were observed is calculated as:
+100% of subjects lied. The upper and lower 99% confidence intervals are also 100%. Naïvely, this
+might seem wrong. Can we rule out that 8 subjects lied, and the two honest subjects both saw heads?
+
+In fact, the GSV method works like this. First, given *R* reports of heads, the probability that a
+total of *T* "true" heads were observed is calculated as:
 
@@
 
-```{r}
+```{r heads-10-10-calcs}
 
@@
 example, in my simulations with $P = 0.5$, the overall probability that there were 10 heads when $R
-= N = 10$ was about 1 in `r inv_prob_h`, not 1 in 1024. When $\lambda = 0.2$, it is about 1 in 
+= N = 10$ was about 1 in `r inv_prob_h`, not 1 in 1024. When $\lambda = 0.2$, it was about 1 in 
 `r inv_prob_h_l20`. The same is true at the other end of the scale: when *R* is low, we indeed learn
@@
 with probability $\lambda$. Or it could be that the sample is drawn from a population of whom
-$\lambda$ are (always) liars, and $1 - \lambda$ are truth-tellers.
+$\lambda$ are (always) liars, and $1 - \lambda$ are truth-tellers. *Lies*, on the other hand,
+has no interpretation in the population, because the rest of the population has no chance to tell a lie
+in the experiment. Indeed, when GSV run Monte Carlo simulations, they themselves check their
+confidence intervals against $\lambda$ (which they call $Q$).
 
@@
 
-*Lies* can be treated as an estimate of $\lambda$. It is unbiased, because the
-probability that people would lie if they saw tails is independent of the coin flip they actually
-see. But it can be a very noisy estimate. 
+*Lies* can be treated as an estimate of $\lambda$. It is unbiased: it is an estimate of 
+$\lambda$ in the random sample of $N - T$ people who saw tails. But it can be a very noisy estimate. 
 Again, suppose 10 heads out of 10 are reported, and 9 heads were really observed. *Lies* is 100%. 
@@
 tell that the second problem matters, because the confidence interval coverage of $\lambda$ is much
-worse than coverage of *Lies*. The GSV estimator is also a biased estimator of $\lambda$.
+worse than coverage of *Lies*. The GSV estimator is also a biased estimator of $\lambda$, as we will
+see.
 
@@
 shows this. It splits the simulations by the proportion of reported heads, *R/N*. Coverage levels
-fall off sharply as *R/N* increases. Note that for fair coin flips, *R/N* is typically greater than
+fall off sharply as *R/N* increases. For fair coin flips, *R/N* is typically greater than
 0.5, in the simulations and in reality.
@@
 
-From this, one can derive confidence intervals and expected values in the usual way.^[R code
-to do this is available at https://github.com/hughjonesd/GSV-comment. ] Technically,
-they are Bayesian "credible" intervals. I use Highest Posterior Density intervals [@hyndman1996computing], rather than the central confidence interval. This allows the intervals
-to include endpoints of the distribution, which is important when e.g. testing for $\lambda = 0$.
+From this, one can derive confidence intervals and expected values in the usual way.^[R code to do
+this is available at https://github.com/hughjonesd/GSV-comment. ] Technically, they are Bayesian
+"credible" intervals. I use Highest Posterior Density intervals [@hyndman1996computing], rather than
+the central confidence interval. This allows the intervals to include endpoints of the distribution,
+which is important when e.g. testing for $\lambda = 0$.
 
@@
 
+```{r benndorf-recalc}
+bennd <- update_prior(57, 98, 5/6, dunif)
+bennd_bounds <- dist_hdr(bennd, 0.95)
+bennd_bounds <- pct_format(bennd_bounds)
+bennd_trad <- binom.test(57, 98)$conf.int
+bennd_trad <- pct_format(bennd_trad)
+```
+
+@benndorf2017experienced use the GSV method to calculate confidence intervals for the proportion of
+liars in a lying task with a die roll ($P = 5/6$). From 57 reports of the best outcome, out of 98
+subjects, they calculate a lying rate of 49.68%, with a 95% CI of (45.3%, 53.95%). Using the
+Bayesian method with a uniform prior, the confidence interval becomes (`r bennd_bounds[1]`, 
+`r bennd_bounds[2]`), about twice as big. Obviously, this matters for e.g. sample size calculations.
+
 # Point estimation
 
-We can also compare the accuracy of point estimates of *Liars*. Table
-\ref{tab:point-estimates} shows the mean squared error for methods by different *N*. For low *N*,
+We can also compare the accuracy of point estimates of *Liars*. Table \ref{tab:bias} shows bias
+(the estimated value minus the true value of $\lambda$) for different methods by different *N*.
+The Bayesian method is always the least biased until $N = 500$, and the GSV method is the most biased.
+
+Table \ref{tab:mse} shows the mean squared error for methods by different *N*. For low *N*,
 the best method is Bayesian and the worst is Frequentist, with GSV in between. When *N* gets large all
@@
 
-sim_est %>% 
+bias_mse <- sim_est %>% 
       filter(CI == 90) %>% 
@@
       group_by(Method, N) %>% 
-      summarize(mean_sq_error = mean(error_sq, na.rm = TRUE)) %>% 
+      summarize(
+        mean_sq_error = mean(error_sq, na.rm = TRUE),
+        bias          = mean(error, na.rm = TRUE)
+      )
+
+bias_mse %>% 
+      select(-mean_sq_error) %>% 
+      spread(N, bias, sep = ": ") %>% 
+      ungroup() %>% 
+      as_huxtable(add_colnames = TRUE) %>% 
+      set_caption("Mean bias by method and $N$") %>% 
+      set_label("tab:bias") %>% 
+      theme_plain()
+
+bias_mse %>% 
+      select(-bias) %>% 
       spread(N, mean_sq_error, sep = ": ") %>% 
@@
       set_caption("Mean squared errors by method and $N$") %>% 
-      set_label("tab:point-estimates") %>% 
+      set_label("tab:mse") %>% 
       theme_plain()
-```
+
+```
+
+# Power tests
+
+```{r power-tests}
+power_l_25 <- power_calc(N = 100, P = 0.5, lambda = 0.25)
+power_l_10 <- power_calc(N = 100, P = 0.5, lambda = 0.10)
+```
+
+GSV argue that existing sample sizes may be too small to reject "no lying" ($\lambda = 0). 
+We can check this with the Bayesian method by simulations. With a uniform prior and an $N$ of 100, 
+the Bayesian method has `r pct_format(power_l_25)` power to detect $\lambda$ of 25% and 
+`r pct_format(power_l_10)` power to detect $\lambda$ of 10%. So, on this we agree.
 

### 2018-11-05 GSV-heads.R

@@ -49,12 +49,15 @@ prop_liars_ci_gsv <- function (ci, heads, N, P) {
   pl  <- c(0, pl)
   
   tail <- (1 - ci)/2
-  # lower bound: no more than tail% of probability has less than this
-  lb_idx <- max(which(cdf <= tail)) # must exist since cdf starts at 0.
+  # lower bound: no more than tail% of probability has less than this.
+  # this ought to be max(which(tail <= cdf)) but the paper says this instead - which
+  # will lead to excessively narrow confidence intervals when N is low
+  lb_idx <- min(which(cdf > tail)) # must exist since cdf starts at 0.
   lb <- pl[lb_idx]
   
-  # upper bound: no more than 1-tail% of probability has more
-  ub_idx <- min(which(cdf >= 1 - tail))
+  # upper bound: no more than 1-tail% of probability has more. This is what the paper says
+  # but it is far from what they do:
+  ub_idx <- max(which(cdf < 1 - tail))
   ub <- pl[ub_idx]
   
   return(c(lb, ub))

### 2018-11-05 bayesian-heads-cts.R

@@ -161,20 +161,17 @@ dist_quantile <- function(dist, probs) {
 #' 
 #' @param dist A one-argument function
 #' @param conf_level A scalar between 0 and 1
-#' @param hdr_workaround Another confidence level to workaround a bug in hdrcde::hdr. You
-#'   shouldn't need to set this unless you have an unusual distribution and `dist_hdr` gives
-#'    a warning; if so, try setting it to a smaller or larger value.
 #'
-#' @return A length 2 vector of 
+#' @return A length 2 vector of region endpoints
 #'
 #' @examples
-dist_hdr <- function (dist, conf_level, hdr_workaround = 0.01) {
+dist_hdr <- function (dist, conf_level) {
   stopifnot(is_prob(conf_level), is.function(dist)) 
   
-  density_est <- list(x = 0:1000/1000, y = dist(0:1000/1000))
+  density_est <- list(x = -1:101/100, y = c(0, dist(0:100/100), 0))
   
   # we include prob 0.1 to make sure that result has two columns
-  result <- hdrcde::hdr(den = density_est, prob = c(100 * conf_level, 100 * hdr_workaround))
+  result <- hdrcde::hdr(den = density_est, prob = 100 * conf_level)
   result <- result$hdr[1, ]
   if (length(result) != 2) {
     warning("hdrcde::hdr returned only one endpoint. Guessing which it is.")
@@ -207,4 +204,26 @@ if (FALSE) {
     cis[1] <= lambda && lambda <= cis[2]
   })
   table(cov_check)
+}
+
+
+#' Calculate power to detect non-zero lying
+#'
+#' @inherit prob_report_given_lambda params
+#' @param alpha Significance level to use for the null hypothesis 
+#' @param nsims Number of simulations to run
+#'
+#' @return
+#' @export
+#'
+#' @examples
+power_calc <- function (N, P, lambda, alpha = 0.05, prior = dunif, nsims = 200) {
+  res <- replicate(nsims, {
+    R <- rbinom(1, N, (1-P) + P * lambda)
+    pstr <- update_prior(R, N, P, prior)
+    bounds <- dist_hdr(pstr, 1 - alpha)
+    bounds[1] > 0 
+  })
+  
+  mean(res)
 }

### 2018-11-05 GSV-comment-brief.Rmd
Final tweaks

@@
 
-TODO XXX: point out the claims they make.
-
 Some people are honest, while others are likely to lie whenever it benefits them. We would like to understand
@@
 
-Lastly, I suggest a simple way to avoid these statistical shenanigans. Ask a group of *N*
+Lastly, here is a simple experimental design to avoid these statistical shenanigans. Ask a group of *N*
 experimental subjects, not to flip a coin, but to draw a black or white ball, without replacement,
@@
 will then know -- not estimate -- that the proportion of lies told is $(R - T)/(N - T)$, and this
-will also be the proportion of liars, in a sample of exactly $N - T$ subjects. So you can
-simultaneously estimate the proportion of lies, and of the lying liars who tell them.
+will also be the proportion of liars, in a sample of exactly $N - T$ subjects. You can compare
+different samples, or test for no lying, using a straightforward chi-squared test.
+So, you can simultaneously estimate the proportion of lies, and of the lying liars who tell them.
 

### 2018-11-05 GSV-comment-brief.Rmd
Add reanalysis of Banerjee et al 2018; let dist_quantile and dist_hdr work with distribution functions not on [0, 1].

@@
 # set to FALSE to recalculate all confidence interval estimates; TRUE for speed:
-cache_results <- FALSE
+cache_results <- TRUE
 
@@
 I show that their estimator can have substantial bias. In fact, it performs worse than the naïve
-estimator from equation (\ref{eqn:naive-estimator}), $\frac{R-(1-P)}{P}$. Also, the GSV confidence
-intervals do not always achieve nominal coverage of *Lies*. When the number of heads reported is
-either high or low, the percentage of confidence intervals containing *Lies* may fall below the
-nominal value.
+estimator from equation (\ref{eqn:naive-estimator}), $\frac{R-(1-P)}{P}$. Since the true value of
+*Lies* is an unbiased estimator of $\lambda$, the GSV estimator is also a biased estimator of
+$\lambda$, as we will see. Also, the GSV confidence intervals do not always achieve nominal coverage
+of *Lies*. When the number of heads reported is either high or low, the percentage of confidence
+intervals containing *Lies* may fall below the nominal value.
 
@@
 tell that the second problem matters, because the confidence interval coverage of $\lambda$ is much
-worse than coverage of *Lies*. The GSV estimator is also a biased estimator of $\lambda$, as we will
-see.
+worse than coverage of *Lies*.
 
@@
 as_huxtable(coverage_rn, add_colnames = TRUE) %>% 
-      set_caption("GSV confidence interval coverage by proportion of heads reported") %>% 
+      set_caption("GSV confidence interval coverage by proportion of heads reported ($R/N$)") %>% 
       set_label("tab:coverage-rn") %>% 
@@
 ```
+
+```{r banerjee-recalc, cache = cache_results}
+
+paste_combn <- function (x, y, flip = FALSE) {
+ res <- outer(x, y, FUN = paste0)
+ if (! flip) res <- t(res)
+ c(res)
+}
+
+sigstar <- function (x) {
+  symnum(x, corr = FALSE, 
+          cutpoints = c(0, .001, .01, .05, 1),
+          symbols = c("***", "**", "*", "")
+        )
+}
+
+treats <- paste_combn(c("T1", "T2", "T2-winners", "T2-losers"), c("-GC-", "-SC-"))
+treats <- paste_combn(treats, c("Same", "Other"))
+treats <- c("T0-GC-Same", "T0-SC-Same", treats)
+treats <- paste_combn(treats, c("-Aligned", "-Unaligned"), flip = TRUE)
+
+banerjee <- data.frame(
+  Treatment = treats,
+  N       = c(84, 84, rep(c(43, 41, 41, 43, 12,  17, 33, 22), each = 2),
+              90, 78, rep(c(42, 42, 40, 44, 12, 15, 32, 28), each = 2)),
+  pct_gt3 = c(77.38, 77.38, 83.72, 65.12, 80.49, 73.17, 75.61, 53.66, 88.37, 81.40, 58.33, 50.00, 
+              70.59, 52.94, 87.88, 45.45, 68.18, 72.73,
+              68.89, 66.67, 57.14, 73.81, 57.14, 66.67, 60.0, 77.5, 56.82, 59.09, 33.33, 41.67,
+              40.00, 73.33, 53.12, 93.75, 60.71, 75.00
+            )
+)
+
+banerjee %<>% mutate(
+        N_gt3 = round(pct_gt3/100*N, 0)
+      ) %>% 
+      extract(Treatment, c("Treatment", "Target", "Payoffs"), regex = "(.*)-([:alnum:]+)-([:alnum:]+)")
+
+banerjee_gsv_cis <- apply(banerjee %>% select(N_gt3, N), 1, function(x) {
+  prop_liars_ci_gsv(0.95, x["N_gt3"], x["N"], 0.5)
+})
+
+rownames(banerjee_gsv_cis) <- c("gsv_lo", "gsv_hi")
+banerjee %<>% cbind(t(round(banerjee_gsv_cis, 2) * 100))
+
+pp <- MASS::fitdistr(banerjee$N_gt3/banerjee$N, "beta", start = list(
+        shape1 = 1, shape2 = 1
+      ))
+pooled_prior <- function (x) dbeta(x, pp$estimate["shape1"], pp$estimate["shape2"])
+
+banerjee_bayes_cis  <- apply(banerjee %>% select(N_gt3, N), 1, function(x) {
+  pstr <- update_prior(x["N_gt3"], x["N"], 0.5, prior = dunif)
+  dist_hdr(pstr, 0.95)
+})
+
+rownames(banerjee_bayes_cis) <- c("bayes_lo", "bayes_hi")
+banerjee %<>% cbind(t(round(banerjee_bayes_cis, 2) * 100))
+
+bj_wide <- banerjee %>% 
+      reshape2::melt(id.vars = c("Treatment", "Target", "Payoffs")) %>% 
+      reshape2::dcast(Treatment + Payoffs ~ ...)
+
+same_other_p <- apply(bj_wide %>% select(matches("(Other|Same)_N")), 1, function (x) {
+  if (is.na(x["Other_N_gt3"])) return(rep(NA, 2))
+  pstr_other <- update_prior(x["Other_N_gt3"], x["Other_N"], 0.5, prior = dunif)
+  pstr_same <- update_prior(x["Same_N_gt3"], x["Same_N"], 0.5, prior = dunif)
+  diff_dist <- difference_dist(pstr_other, pstr_same)
+  dist_hdr(diff_dist, 0.95, bounds = c(-1, 1))
+})
+
+rownames(same_other_p) <- c("diff_lo", "diff_hi")
+same_other_p <- t(same_other_p)
+bj_wide %<>% cbind(same_other_p)
+bj_wide %<>% select(Treatment, Payoffs, diff_lo, diff_hi)
+
+banerjee %<>% left_join(bj_wide, by = c("Treatment", "Payoffs"))
+banerjee %<>% mutate(
+        GSV_CIs      = sprintf("%s -- %s", gsv_lo, gsv_hi),
+        Bayesian_CIs = sprintf("%s -- %s", bayes_lo, bayes_hi),
+        diff_ci      = ifelse(is.na(diff_lo), "", 
+                               sprintf("%.0f -- %.0f", diff_lo * 100, diff_hi * 100)),
+        diff_ci      = ifelse(diff_lo > 0 | diff_hi < 0, paste(diff_ci, "*"), diff_ci )
+      )
+```
+
+```{r banerjee-recalc-table}
+
+group_cols <- c("Treatment", "Payoffs", "Diff. 95% CI", "N")
+banerjee %>% 
+      select(
+        Treatment,
+        Payoffs,
+        Target,
+        "Pct > 3"        = pct_gt3, 
+        N, 
+        "GSV 95% CI"   = `GSV_CIs`, 
+        "Bayes 95% CI" = `Bayesian_CIs`,
+        "Diff. 95% CI" = `diff_ci`
+      ) %>%
+      as_huxtable(add_colnames = TRUE) %>% 
+      set_rowspan(evens, group_cols, 2) %>% 
+      set_rowspan(grepl("T0", banerjee$Treatment), group_cols, 1) %>% 
+      set_all_border_colors("grey70") %>% 
+      theme_plain() %>% 
+      set_top_border(evens, everywhere, 0.4) %>%
+      set_bottom_border(evens, group_cols, 0.4) %>%
+      set_bottom_border(grepl("T0", banerjee$Treatment), group_cols, 0) %>%
+      set_valign(everywhere, group_cols, "middle") %>% 
+      set_background_color(NA) %>% 
+      set_top_padding(8) %>% 
+      set_bottom_padding(4) %>% 
+      set_font_size(10) %>% 
+      set_caption("Confidence intervals from Banerjee et al. 2018, original and recalculated") %>% 
+      set_label("tab:banerjee-recalc")
+
+```
+
+@banerjee2018spillover use the GSV method to estimate confidence intervals for proportion of liars
+in a die roll task. They estimate the proportion of liars who report a die roll above 3 
+($P = 0.5$), for several treatments. Table \ref{tab:banerjee-recalc} shows GSV confidence intervals,
+along with recalculated Bayesian confidence intervals, and confidence intervals for the difference
+between lying to the "Same" and "Other" caste. I use a uniform prior rather than a pooled prior
+here. This may be more reasonable when we are testing for differences in experimental treatments,
+as we do not start from a strong belief that the treatments have no effect.
+
+The Bayesian confidence intervals are much larger
+than GSV confidence intervals. Only a couple of significant results survive. (Note that
+significance tests in the original paper were done with standard frequentist techniques, not the
+GSV method.) More importantly, it is clear that the N is rather low to make useful inferences
+about the differences between groups. For example, for the T2-winners-GC group in the "aligned
+payoffs" treatment, differences in lying could be as much as 30% in either direction. Notice
+also that sometimes confidence intervals for the number of liars start above 0, even though less
+than half reported the high outcome. This is because, starting from a pooled prior, the evidence
+from the low N is not enough to shift the prior much. Low die rolls are more likely than a population
+of truth tellers.
 

### 2018-11-05 bayesian-heads-cts.R

@@ -121,6 +121,13 @@ dist_mean <- function (dist, l = 0, r = 1) {
   return(EV)
 }
 
+#' Find probability of a probability distribution function within given bounds 
+#'
+#' @inherit dist_mean params
+#'
+#' @return
+#'
+#' @examples
 dist_prob_within <- function (dist, l, r) {
   stopifnot(l <= r, is.function(dist))
   try_integral(dist, l, r)
@@ -131,17 +138,18 @@ dist_prob_within <- function (dist, l, r) {
 #'
 #' @param dist A one argument function
 #' @param probs A vector of probabilities
+#' @param bounds A length 2 vector of the bounds of the distribution's support
 #'
 #' @return A vector of quantiles
 #'
 #' @examples
-dist_quantile <- function(dist, probs) {
+dist_quantile <- function(dist, probs, bounds = c(0, 1)) {
   stopifnot(is_prob(probs), is.function(dist))
   
   qs <- sapply(probs, function (prob) {
-    f <- function (x) (dist_prob_within(dist, 0, x) - prob)^2
+    f <- function (x) (dist_prob_within(dist, bounds[1], x) - prob)^2
     # want x s.t. interval_prob(dist, 0, x) == prob
-    res <- optimize(f, c(0, 1))
+    res <- optimize(f, bounds)
     res$minimum
   })
   
@@ -161,14 +169,19 @@ dist_quantile <- function(dist, probs) {
 #' 
 #' @param dist A one-argument function
 #' @param conf_level A scalar between 0 and 1
+#' @param bounds A length 2 vector of the bounds of the distribution's support
 #'
 #' @return A length 2 vector of region endpoints
 #'
 #' @examples
-dist_hdr <- function (dist, conf_level) {
+dist_hdr <- function (dist, conf_level, bounds = c(0, 1)) {
   stopifnot(is_prob(conf_level), is.function(dist)) 
   
-  density_est <- list(x = -1:101/100, y = c(0, dist(0:100/100), 0))
+  eval_at <- seq(bounds[1], bounds[2], 0.01)
+  eval_at_y <- dist(eval_at)
+  eval_at <- c(bounds[1] - 0.01, eval_at, bounds[2] + 0.01)
+  eval_at_y <- c(0, eval_at_y, 0)
+  density_est <- list(x = eval_at, y = eval_at_y)
   
[…]

### 2018-11-05 GSV-comment-brief.Rmd
Submitted version

@@
 
-GSV argue that existing sample sizes may be too small to reject "no lying" ($\lambda = 0). 
+GSV argue that existing sample sizes may be too small to reject "no lying" ($\lambda = 0$). 
 We can check this with the Bayesian method by simulations. With a uniform prior and an $N$ of 100, 
@@
 
-pp <- MASS::fitdistr(nats$prop_liars, "beta", start = list(
+pp <- suppressWarnings(MASS::fitdistr(nats$prop_liars, "beta", start = list(
         shape1 = 1, shape2 = 1
-      ))
+      )))
 pooled_prior <- function (x) dbeta(x, pp$estimate["shape1"], pp$estimate["shape2"])
@@
 
-pp <- MASS::fitdistr(banerjee$N_gt3/banerjee$N, "beta", start = list(
-        shape1 = 1, shape2 = 1
-      ))
-pooled_prior <- function (x) dbeta(x, pp$estimate["shape1"], pp$estimate["shape2"])
+# didn't converge to give finite density at 0!
+# pp <- suppressWarnings(MASS::fitdistr(pmax(0.03, 2 * banerjee$N_gt3/banerjee$N - 1), "beta", start = list(
+#         shape1 = 1, shape2 = 1
+#       )))
+# pooled_prior <- function (x) dbeta(x, pp$estimate["shape1"], pp$estimate["shape2"])
 
@@
 along with recalculated Bayesian confidence intervals, and confidence intervals for the difference
-between lying to the "Same" and "Other" caste. I use a uniform prior rather than a pooled prior
-here. This may be more reasonable when we are testing for differences in experimental treatments,
-as we do not start from a strong belief that the treatments have no effect.
+between lying to the "Same" and "Other" caste. Here, I used a non-informative prior rather than
+a pooled prior, letting the algorithm maintain an "open mind" about treatment effects.
 
@@
 about the differences between groups. For example, for the T2-winners-GC group in the "aligned
-payoffs" treatment, differences in lying could be as much as 30% in either direction. Notice
-also that sometimes confidence intervals for the number of liars start above 0, even though less
-than half reported the high outcome. This is because, starting from a pooled prior, the evidence
-from the low N is not enough to shift the prior much. Low die rolls are more likely than a population
-of truth tellers.
+payoffs" treatment, differences in lying could be as much as 40% in either direction.
 
@@
 
-1. Do not use the GSV confidence intervals, unless you are specifically interested in *Lies* rather
-  than $\lambda$. Even in that case, be aware that the confidence intervals have low coverage for 
-  extreme values of *R*.
-
-2. Do not use the GSV estimates. They are biased as estimators of both *Lies* and $\lambda$.
-
-3. If your N is reasonably large, say at least 100, you can safely use standard frequentist 
+1. Do not use the GSV method. Confidence intervals are always too narrow, risking false inferences.
+
+2. If your N is reasonably large, say at least 100, you can safely use standard frequentist 
   confidence intervals and tests.
 
-4. If your N is small, consider Bayesian estimates and confidence intervals. To estimate differences 
+3. If your N is small, consider Bayesian estimates and confidence intervals. To estimate differences 
   between subgroups, consider empirical Bayes with a prior derived from the pooled sample.
@@
 proportion of heads reported (*R/N*). Overall results are quite solid, but when the proportion of
-heads reported is low or high, coverage drops below the nominal intervals. Interestingly, this problem
-gets worse as $N$ increases.
+heads reported is low or high, coverage drops below the nominal intervals. This is probably because,
+at these extremes, the difference between the true posterior and equation \ref{eqn:truncated-binom} 
+becomes large. Interestingly, this problem gets worse as $N$ increases.
 

### 2018-11-08 GSV-comment-brief.Rmd
Add the word Abstract to the abstract, because apparently it wasn't obvious enough for Springer.

@@
 
-> Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability
+> **Abstract**: Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability
 > distribution of the proportion of lies told in "coin flip" style experiments. I show that their

### 2019-02-27 response-to-reviewers.Rmd
Add response to reviewers

---
title: "Untitled"
author: "David Hugh-Jones"
date: "27/02/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

> The most obvious comment that both reviewers made is one of etiquette: you are unnecessarily harsh
> to GSV! I would like you to reframe the discussion of GSV following the suggestions of R2. (And yes,
> the “don’t use the GSV method” in the conclusion should be replaced with something more informative
> and less pedantic.)

[TODO]

> I also like R2’s suggestion about either providing power calculations (see the example table this
> reviewer provided) and/or an online calculator that you will discuss in your paper. Finally, please
> ensure that you address R1’s comments on clarity.

[Already in software]

* Reviewer 1

> I think that the statistical argument could be explained more clearly... I would encourage the 
> author to expand this part of the paper to explain things more clearly.

[Use bits of R1's example]

I also think that it would be important to explain more clearly how the statistical and conceptual arguments relate to the lack of nominal coverage of the estimator and its biasedness. This is not very clear at the moment - I am referring in particular to the last four paragraphs of page 4. In particular, I struggle to see how the two arguments can help explain the poor nominal coverage of the GSV method. In those paragraphs, it would also be useful to make a clearer distinction between the GSV method as an estimator of the proportion of lies actually told in the sample ("Lies") - and the problems that arise there; and the method as an estimate of the proportion of liars in the sample ("lambda"). At the moment the paper goes back and forth between the problems that arise in either case, which is confusing.

This is also true in the following sections ("Alternative methods" and "Point estimates"). As far as I understand, the exercise here consists in comparing across methods the coverage and point estimates of lambda (this is confusingly referred to as "Liars" in this part of the paper). It would be useful to point this out more clearly.

I also thought that the part on "empirical Bayes" is not very well explained. Indeed, I wondered whether the inclusion of this section may detract from the overall value of the paper, since it becomes slightly less focused. The same goes for table 9 and corresponding text in the paper - it seems that this goes somewhat beyond the scope of the paper - which in my opinion works best as a comment focused on the GSV method, rather than its applications in subsequent papers.

Regarding the conclusions, I liked the prescriptive approach of the paper. However, I think that the first precept, "Do not use the GSV method", is perhaps too strong. I think that the simulations presented in the paper convinced me that GSV is not a good method to estimate the proportion of liars ("lambda"), espcially in comparison with the alternative methods - but I am less convinced that the method is a terrible estimator of the proportion of lies actually told in the sample ("Lies"). The simulations in the Appendix do not seem to show a very large bias or dramatic drops in coverage in this case. So, in my view, the first precept could perhaps be rephrased as "Do not use the GSV method if you are interested in estimating the proportion of liars in your sample".

I also liked the thought experiment presented in the concluding section. However, one important point to make here is that, in such an experiment, each subject would face a different truthful distribution (and the experiment would not be able to control or observe which subject faced which distribution). We know from existing research that the underlying distribution matters for the willingness to lie. So this is a caveat to keep in mind when estimating the proportion of lies via this method.

Finally, I have some additional minor comments:
- p. 1, footnote 1: the acronym GSV is used before it has been explained
- p. 4: line 33, equation 1 should contain R/N, not R.
- p. 4, table 3: what does "Percentage of cases" mean?
- Figure 3 in the Appendix, the horizontal axis is missing

* Reviewer 2

Power Calculations: I believe one area that would be extremely useful for future research would be to provide some power calculations based on your proposed method (either frequentist or Bayesian).

[Give example in main paper]

Online Calculator: Another way the paper could be extremely valuable for future researchers would be, like GSV, to provide an online lying calculator so that researchers can easily use your improved method. I worry otherwise that while readers might find your paper interesting, if it is not trivial to apply (which I suspect will be the case for many), then they might not use your method. I will leave it up to you, but either a stand- alone piece of software, or possibly even a STATA routine if that is possible (which I would think would be preferable). In any case, I believe this would be an enormous improvement to the value of your paper (and citations).

[Maybe turn stuff into R package? Or just put some examples into the main paper.]

Suggested experiment in the concluding section: While I like the objective of the suggested experiment, I do not think the design works as I think it changes the nature/implication of lying...
in the second experiment, if a subject gets the white ball but lies and reports black, then there is only one outcome for the experiment: both subjects will report black, and it will be with certainty that the experimenter will know one of the subjects will have lied. This seems like it a potentially important difference that could affect the willingness of subjects to lie. Having more subjects in the room does not change the basic point that in your proposed setup that any subject that lies will make it clear to the experimenter that someone is lying, whereas in the current approach one subject lying does not guarantee the experimenter will detect lying. I see no way to avoid this without some form of deception.

[It's a fair point. Even if the number of white balls is unknown, subjects know the experimenter
knows. But, in a large session, this is perhaps not a big issue.
Acknowledge this point in a footnote. But, still worth making the suggestion.]

Tone down the negative attention to GSV, and get directly to your solution. Your method is the critical contribution, and make it central. Comparisons of the CIs in the simulations make this immediately clear. As I mentioned above, I believe that GSV made an important contribution by pointing out the lack of a good statistical inference method for estimating the distribution of lying in the literature, and your contribution is an obvious advance that gets the CIs to be essentially what we would expect. Hopefully, researchers in this literature will adopt an appropriate statistical inference. The likely two most important practical contributions from GSV is quite notably extended here: many studies likely have been under-powered to find significant differences, and closely related, many null results could thus likely be due to low power. Addressing my first two recommendations above (power and a calculator) will help the literature not fall prey to these mistakes.

[TODO. Maybe have less on GSV.]

### 2019-03-01 GSV-comment-brief.Rmd
Edits in response to reviewers

@@
 > estimates and confidence intervals are flawed. I demonstrate two better ways to estimate the 
-> probability distribution of what we are really interested in: the proportion of liars.
+> probability distribution of what we really care about -- the proportion of liars -- and
+> I provide R software to do this.
 
@@
 # invalidate cache when the tufte version changes
-knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tufte'))
+knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tufte'), highlight = FALSE)
 options(htmltools.dir.version = FALSE)
@@
 if they report heads. Liars don't always lie: they only lie when it benefits them. So they always
-report heads irrespective of the true coin flip. ^[GSV maintain this assumption and so shall I.] If
+report heads irrespective of the true coin flip. ^[@Garbarino2018 maintain this assumption and so shall I.] If
 there are many more heads than we would expect by chance, we can assume many people are lying. But
@@
 calculations.
-
-Table 3 of GSV reports Monte Carlo simulations, which show that the probability of a Type II error
-can be up to 50 per cent. GSV define a Type II error as the 95% confidence interval not containing
-the true value. A 95% confidence interval which only contains the true value 50% of the time
-is unusual. What is going on?
 
@@
 I ran simulations to check the overall performance of the GSV confidence intervals. Simulations
-parameters are shown in Table \ref{tab:params-table}. For each parameter combination, I ran 1000
-simulations. $\lambda$ is the probability that an individual in the sample lies and report heads
+parameters are shown in Table \ref{tab:params-table}. $\lambda$ is the probability that an individual in the sample lies and report heads
 when they observe tails:
@@
 \label{eqn:lambda}
-\lambda = \textrm{Prob}(i \textrm{ reports heads}|i\textrm{ saw tails}).
+\lambda = \frac{1}{N} \sum_{i=1}^N \textrm{Prob}(i \textrm{ reports heads}|i\textrm{ saw tails}).
 \end{equation}
 
-For each simulation and confidence interval, I computed whether the confidence interval contained
-the true value of $\lambda$. Table \ref{tab:coverage-just-gsv} shows the results.
+For each parameter combination, I ran 1000 simulations, drawing random coin flips and reports given
+$P$, $\lambda$ and $N$.
+
+For each simulation and confidence level, I computed whether the GSV confidence interval contained
+the true value of $\lambda$. The first row of Table \ref{tab:coverage-allmethods} shows the results.
 
@@
 
-```{r coverage-overall}
+```{r coverage-allmethods}
 
@@
 
-ht_just_gsv <- ht_overall[1:2,]
-label(ht_just_gsv) <- "tab:coverage-just-gsv"
-ht_just_gsv[1, 1] <- ""
-theme_plain(ht_just_gsv)
+ht_overall %>% 
+      set_caption("Coverage levels for GSV and alternative methods") %>% 
+      set_label("tab:coverage-allmethods")
+
 ```
@@
 By definition, 95% of 95% confidence intervals ought to contain the true value, on average. This is
-called "achieving nominal coverage". GSV intervals are far from this. The confidence intervals are
-too narrow. This problem holds across all simulated probabilities of the low outcome, confidence
-levels, and sample sizes.^[See the appendix.]
-
-Why does this happen? We can get a clue by running the GSV method when there are 10 reports of
-"heads" out of 10 for a fair coin flip (*R = N = 10, P = 0.5*). The resulting point estimate is that
-100% of subjects lied. The upper and lower 99% confidence intervals are also 100%. Naïvely, this
-might seem wrong. Can we rule out that 8 subjects lied, and the two honest subjects both saw heads?
-
-In fact, the GSV method works like this. First, given *R* reports of heads, the probability that a
-total of *T* "true" heads were observed is calculated as:
-
-\begin{equation}
-\label{eqn:truncated-binom}
-\textrm{Prob}(T \textrm{ heads}| R; N, P) = \frac{
-  \textrm{binom}(T,N, 1 - P)
-}{
-  \sum^R_{k=0}\textrm{binom}(k,N, 1 - P)
-}
-\end{equation}
-
-This is the binomial distribution, truncated at *R* because by assumption, nobody "lies downward"
-and reports tails when they really saw heads.
-
-Next, from *T* the number of lies told is calculated as $R - T$; and the proportion of lies told
-is:
-
-\begin{equation}
-\textit{Lies} = \frac{R-T}{N-T} 
-\end{equation}
-
-because $N - T$ people saw the low outcome and had the chance to lie. Combining this
-with the truncated binomial gives a cumulative distribution function of the proportion of liars.
-This is then used to estimate means and confidence intervals.
-
-Putting these together, for $R = N = 10$, the estimated distribution of liars is calculated as follows:
-
-* With probability $\frac{1}{1024}$, there were really 10 heads. Nobody lied in the
-sample.^[But the proportion of people who lied *out of those who saw tails* is undefined, because
-noone saw tails. The GSV software seems to resolve this by fixing the proportion of lies to 100%.]
-
-* Otherwise, 1 or more people saw tails, and they all lied. The proportion of liars is 100%.
-
-Hence, the lower and upper confidence intervals are all 100%.
-
-There are two problems with this approach. One is statistical, one is conceptual.
-
-```{r heads-10-10-calcs}
-
-heads_10 <- sim_est %>% 
-      filter(N == 10, R == 10, P == 0.5) %>% 
-      select(lambda, heads) 
-h10 <- heads_10$heads
-l10 <- heads_10$lambda
-
-inv_prob_h <- round(1/mean(h10 == 10), 0)
-inv_prob_h_l20 <- round(1/mean(h10[l10 == 0.2] == 10), 0)
-
-```
-
-First, if 10 out of 10 heads are reported, you should learn two things. On the one hand, there are
-probably many liars in your sample. On the other hand, probably a lot of coins really landed heads.
-The probability distribution in equation (\ref{eqn:truncated-binom}) does not take account of this.
-In particular, for *R = N*, it reduces to the binomial distribution. This is not correct. For
-example, in my simulations with $P = 0.5$, the overall probability that there were 10 heads when $R
-= N = 10$ was about 1 in `r inv_prob_h`, not 1 in 1024. When $\lambda = 0.2$, it was about 1 in 
-`r inv_prob_h_l20`. The same is true at the other end of the scale: when *R* is low, we indeed learn
-that $T \le R$ but also that the overall distribution is not shaped like the prior.
-
-Second, more importantly, the GSV approach estimates *Lies*, the distribution of the proportion of 
-*lies actually told*, among the subsample of people who saw tails. But we are not usually interested
-in the proportion of lies actually told. We care about the probability that people in the
-sample would lie if they saw tails --  $\lambda$ in equation (\ref{eqn:lambda}). This $\lambda$ can
-be interpreted in different ways. It could be that on seeing a tail, each person in the sample lies
-with probability $\lambda$. Or it could be that the sample is drawn from a population of whom
-$\lambda$ are (always) liars, and $1 - \lambda$ are truth-tellers. *Lies*, on the other hand,
-has no interpretation in the population, because the rest of the population has no chance to tell a lie
-in the experiment. Indeed, when GSV run Monte Carlo simulations, they themselves check their
-confidence intervals against $\lambda$ (which they call $Q$).
-
-The fact that some people saw heads, and had no reason to lie, is just a nuisance for estimation.
-Similarly, we are not interested, per se, in whether more lies were actually told in one group than
-another. Suppose that 9 out of 10 people saw heads. Only one person had a reason to lie, so by
-definition, *Lies* will be either 0 or 1. This will almost certainly be different from the value of
-*Lies* in another group where there were fewer heads. But that tells us very little, either about the 
-samples as a whole, or about the population they come from.
-
-*Lies* can be treated as an estimate of $\lambda$. It is unbiased: it is an estimate of 
-$\lambda$ in the random sample of $N - T$ people who saw tails. But it can be a very noisy estimate. 
-Again, suppose 10 heads out of 10 are reported, and 9 heads were really observed. *Lies* is 100%. 
-But it is 100% of just one person.
-
-The first of these two problems means that the GSV distribution of *Lies* is wrong. In the appendix
-I show that their estimator can have substantial bias. In fact, it performs worse than the naïve
-estimator from equation (\ref{eqn:naive-estimator}), $\frac{R-(1-P)}{P}$. Since the true value of
-*Lies* is an unbiased estimator of $\lambda$, the GSV estimator is also a biased estimator of
-$\lambda$, as we will see. Also, the GSV confidence intervals do not always achieve nominal coverage
-of *Lies*. When the number of heads reported is either high or low, the percentage of confidence
-intervals containing *Lies* may fall below the nominal value.
-
-The second problem means that the GSV confidence intervals are not correct for $\lambda$. We can
-tell that the second problem matters, because the confidence interval coverage of $\lambda$ is much
-worse than coverage of *Lies*.
-
-```{r disagg-coverage}
-
-disagg <- sim_est %>% 
-      filter(method=="gsv") %>% 
-      group_by(
-        `R/N:` = R/N, N, P, CI
-      ) %>% 
-      summarize(mean_in_ci = mean(within_ci, na.rm = TRUE), prop = n()/nrow(.)) %>% 
-      mutate(CI = paste0("CI ", CI, "%")) %>% 
-      spread(CI, mean_in_ci) %>% 
-      mutate(ok  = `CI 95%` > 0.95)
-
-prop_ok <- disagg %>%  
-      ungroup() %>% 
-      summarize(prop_ok = sum(prop[ok])) %>% 
-      pull(prop_ok)
-```
-
-The problem is especially bad when there are many reports of heads. In this case there were probably
-many true heads, so *T* is high and the true sample size $N - T$ is low. Table \ref{tab:coverage-rn}
-shows this. It splits the simulations by the proportion of reported heads, *R/N*. Coverage levels
-fall off sharply as *R/N* increases. For fair coin flips, *R/N* is typically greater than
-0.5, in the simulations and in reality.
-
-```{r coverage-rn}
-coverage_rn <- sim_est %>% 
-      filter(method=="gsv") %>% 
-      group_by(
-        `R/N:` = factor(Hmisc::cut2(R/N, cuts = c(0, 1/4, 1/2, 3/4, 1)))      
-      ) %>% 
-      mutate(pct_cases = n()/nrow(.)) %>% 
-      group_by(`R/N:`, CI) %>% 
-      summarize(
-        mean_in_ci  = mean(within_ci, na.rm = TRUE), 
-        `Percentage of cases` = pct_cases[1]
-      ) %>% 
-      mutate(CI = paste0("CI ", CI, "%")) %>% 
-      spread(CI, mean_in_ci)
-
-as_huxtable(coverage_rn, add_colnames = TRUE) %>% 
-      set_caption("GSV confidence interval coverage by proportion of heads reported ($R/N$)") %>% 
-      set_label("tab:coverage-rn") %>% 
-      set_escape_contents(2:3, 1, FALSE) %>% 
-      set_number_format(-1, -1, list(pct_format)) %>% 
-      theme_plain() %>% 
-      set_right_border(-1, 2, 0.4)
-```
-
-# Alternative methods
-
-Can we do better? Start with the probability of getting *R* reports of heads in total, given
+called "achieving nominal coverage". GSV confidence intervals are
+too narrow.^[This problem holds across all simulated probabilities of the low outcome, confidence
+levels, and sample sizes. See the appendix.]
+
+To deal with this problem, I test two alternative methods for calculating confidence intervals
+on my simulated data. The first ("Frequentist") is the standard method of deriving confidence intervals from a binomial test. The second is a Bayesian method.
+
+To understand the statistics, start with the probability of getting *R* reports of heads in total, given
 $\lambda$. Since individuals report heads either if they see heads with probability $1-P$, or if
@@
 \begin{equation}
+\label{eqn:binom}
 \textrm{Pr}(R|\lambda; N,P) = \textrm{binom}(R, N, (1 - P) + \lambda P)
@@
 
-That immediately suggests the first method, which is to estimate the parameter of this distribution,
-$(1 - P) + \lambda P$, from the proportion of heads reported in the sample, then back out $\lambda$.
-This is the conventional method of e.g. @abeler2016preferences. It is justified if the sample is
-large, because this will lessen sampling variation in the proportion of actual heads observed.
-Similarly, if the sample is large enough, we can generate hypothesis tests for a value of $\lambda$
--- e.g., zero -- by using the tails of the binomial distribution. And we can back out confidence
-bounds for $\lambda$ from confidence bounds for the population proportion of heads reported in the
-same way. As GSV point out, in small samples, this method runs the risk that the sample proportion
-of high outcomes will be different from its expected value.^[In particular, this method can estimate
-confidence bounds for $\lambda$ lower than 0. If so, we can set them to 0.]   We'll see whether this
-matters.
+That immediately suggests the "Frequentist" method, which is to estimate the parameter of this
+distribution, $(1 - P) + \lambda P$, from the proportion of heads reported in the sample, then back
+out $\lambda$. This is the conventional method of e.g. @abeler2016preferences. It is justified if
+the sample is large, because this will lessen sampling variation in the proportion of actual heads
+observed. Similarly, if the sample is large enough, we can generate hypothesis tests for a value of
+$\lambda$ -- e.g., zero -- by using the tails of the binomial distribution. And we can back out
+confidence bounds for $\lambda$ from confidence bounds for the population proportion of heads
+reported in the same way. As GSV point out, in small samples, this method runs the risk that the
+sample proportion of high outcomes will be different from its expected value.^[In particular, this
+method can estimate confidence bounds for $\lambda$ lower than 0. If so, we can set them to 0.]
+We'll see whether this matters.
 
@@
 @agresti1998approximate. Here, I use the binomial exact test of @clopper1934use, which is 
-known to be conservative. I call this the "frequentist" method.
-
-The second method is to use Bayes' rule. Start with a prior probability density function over
-the probability of liars, $\phi(\lambda)$. The posterior probability is then:
+known to be conservative.
+
+The second method uses Bayes' rule. Start with a prior probability density function over
+$\lambda$, $\phi(\lambda)$. The posterior probability is then:
 
 \begin{equation}
+\label{eqn:bayes}
 \phi(\lambda | R; N,P) = \frac{
@@
 }{
-  \int_0^1 \textrm{Pr}(R|\lambda'; N,P) \phi(\lambda) \; \textrm{d}\lambda
+  \int_0^1 \textrm{Pr}(R|\lambda'; N,P) \phi(\lambda') \; \textrm{d}\lambda'
 }
@@
 
-From this, one can derive confidence intervals and expected values in the usual way.^[R code to do
-this is available at https://github.com/hughjonesd/GSV-comment. ] Technically, they are Bayesian
-"credible" intervals. I use Highest Posterior Density intervals [@hyndman1996computing], rather than
-the central confidence interval. This allows the intervals to include endpoints of the distribution,
-which is important when e.g. testing for $\lambda = 0$.
+From this, one can derive confidence intervals and expected values in the usual way. Technically,
+they are Bayesian "credible" intervals. I used Highest Posterior Density intervals
+[@hyndman1996computing], rather than the central confidence interval. This allows the intervals to
+include endpoints of the distribution, which is important when e.g. testing for $\lambda = 0$.
 
@@
 
-I ran these estimation methods on my simulated data. Results are shown in Table
-\ref{tab:coverage-allmethods}. Both frequentist and  Bayesian methods mostly achieve the nominal
+Results in Table
+\ref{tab:coverage-allmethods} show that both frequentist and  Bayesian methods mostly achieve the nominal
 confidence level, with more than 90/95/99% of intervals containing the true value of *Liars*. The
@@
 
-```{r coverage-allmethods}
-ht_overall %>% 
-      set_caption("Coverage levels for GSV and alternative methods") %>% 
-      set_label("tab:coverage-allmethods")
-```
-
-Frequentist confidence intervals could be less accurate when N is low, since that leads to more
+Frequentist confidence intervals could be less accurate when $N$ is low, since that leads to more
 sampling variation in the number of true heads. Table \ref{tab:coverage-N} checks this by looking
 separately at simulations with *N = 10* and *N = 50*. Frequentist 99% confidence intervals indeed
-appear slightly too narrow for this range. Bayesian confidence intervals are fine. Both alternatives
-perform much better than the GSV approach.
+appear slightly too narrow for this range. Bayesian confidence intervals are fine.
 
@@
 
-```{r benndorf-recalc}
-bennd <- update_prior(57, 98, 5/6, dunif)
-bennd_bounds <- dist_hdr(bennd, 0.95)
-bennd_bounds <- pct_format(bennd_bounds)
-bennd_trad <- binom.test(57, 98)$conf.int
-bennd_trad <- pct_format(bennd_trad)
-```
-
-@benndorf2017experienced use the GSV method to calculate confidence intervals for the proportion of
-liars in a lying task with a die roll ($P = 5/6$). From 57 reports of the best outcome, out of 98
-subjects, they calculate a lying rate of 49.68%, with a 95% CI of (45.3%, 53.95%). Using the
-Bayesian method with a uniform prior, the confidence interval becomes (`r bennd_bounds[1]`, 
-`r bennd_bounds[2]`), about twice as big. Obviously, this matters for e.g. sample size calculations.
+# Understanding the GSV approach
+
+Why does the GSV method produce narrow confidence intervals? We can get a clue by running the GSV method when there are 10 reports of
+"heads" out of 10 for a fair coin flip (*R = N = 10, P = 0.5*). The resulting point estimate is that
+100% of subjects lied. The upper and lower 99% confidence intervals are also 100%.
+
+This is calculated as follows. First, given *R* reports of heads, the probability that a
+total of $T$ "true" heads were observed is calculated as:
+
+\begin{equation}
+\label{eqn:truncated-binom}
+\textrm{Prob}(T \textrm{ heads}| R; N, P) = \frac{
+  \textrm{binom}(T, N, 1 - P)
+}{
+  \sum^R_{k=0}\textrm{binom}(k, N, 1 - P)
+}
+\end{equation}
+
+This is the binomial distribution, truncated at *R* because by assumption, nobody "lies downward"
+and reports tails when they really saw heads.
+
+Next, from *T* the number of lies told is calculated as $R - T$; and the proportion of lies told
+is:
+
+\begin{equation}
+\label{eqn:lies}
+\textit{Lies} = \frac{R-T}{N-T} 
+\end{equation}
+
+because $N - T$ people saw the low outcome and had the chance to lie. Combining this
+with the truncated binomial gives a cumulative distribution function of *Lies*.
+This is then used to estimate means and confidence intervals.
+
+Putting these together, for $R = N = 10$, the estimated distribution of *Lies* is calculated as follows:
+
+* With probability $\frac{1}{1024}$, there were really 10 heads. Nobody lied in the
+sample.^[But the proportion of people who lied *out of those who saw tails* is undefined, because
+noone saw tails. The GSV software seems to resolve this by fixing the proportion of lies to 100%.]
+
+* Otherwise, 1 or more people saw tails, and they all lied. The proportion of liars is 100%.
+
+Hence, the lower and upper confidence intervals are all 100%.
+
+There are two problems with this approach, one statistical, and one conceptual.
+
+```{r heads-10-10-calcs}
+
+heads_10 <- sim_est %>% 
+      filter(N == 10, R == 10, P == 0.5) %>% 
+      select(lambda, heads) 
+h10 <- heads_10$heads
+l10 <- heads_10$lambda
+
+inv_prob_h <- round(1/mean(h10 == 10), 0)
+inv_prob_h_l20 <- round(1/mean(h10[l10 == 0.2] == 10), 0)
+
+```
+
+First, if many heads are reported, you should learn two things. On the one hand, there are probably
+many liars in your sample. On the other hand, probably a lot of coins really landed heads. The
+probability distribution in equation (\ref{eqn:truncated-binom}) does not take account of this.
+
+For example, suppose we are certain that everyone in the sample is a liar who always reports heads.
+In this case, observing $R = N = 10$ gives us no information about the true number of heads. The
+posterior probability that $T = 10$ is then indeed 1/1024, the same as the prior. Now suppose we
+know that nobody in the sample is a liar. Then on observing $R = 10$, we are sure that there were
+truly 10 heads: the posterior that $T = 10$ is 1. If exactly 5 out of 10 subjects are liars, then
+observing $R = 10$ means that all 5 truth tellers really saw heads. The posterior probability that
+$T = 10$ is then $1/32$, the chance that all 5 liars saw heads. And so on.
+
+When we are uncertain about the number of liars, our posterior that $T = 10$ will be some weighted
+combination of these beliefs. Unless we are certain everyone in the sample is a liar, the
+probability that $T = 10$ will be greater than 1 in 1024. Equation (\ref{eqn:truncated-binom}) is
+therefore not correct. In this case, it is equivalent to assuming that everybody in the sample is a liar,
+whose report is uninformative about the true number of heads. One then uses the prior distribution
+of heads to estimate the proportion of those who actually saw tails and lied.
+
+Indeed, in the simulations with $P =
+0.5$ and across all values of $\lambda$, the overall probability that there were 10 true heads,
+conditional on $R = N = 10$, was about 1 in `r inv_prob_h`, not 1 in 1024. Fixing $\lambda = 0.2$,
+it was about 1 in `r inv_prob_h_l20`.
+
+This problem means that the GSV estimator of *Lies* is biased. In the appendix
+I show that the GSV estimator can have substantial bias, and performs worse than the naïve
+estimator from equation (\ref{eqn:naive-estimator}), $\frac{R/N-(1-P)}{P}$. Also, the GSV confidence intervals do not always achieve nominal coverage
+of *Lies*. When the number of heads reported is either high or low, the percentage of confidence
+intervals containing *Lies* may fall below the nominal value.
+
+There is a second, more important problem. The GSV approach attempts to estimate *Lies* in equation
+(\ref{eqn:lies}). This is the  proportion of *lies actually told*, among the subsample of people who
+saw tails. But we are not usually interested in the proportion of lies actually told. We care about
+the probability that a subject in the sample would lie if they saw tails --  $\lambda$ in equation
+(\ref{eqn:lambda}). This $\lambda$ can be interpreted in different ways. Maybe on seeing a tail,
+each person in the sample lies with probability $\lambda$. Or maybe the sample is drawn from a
+population of whom $\lambda$ are (always) liars, and $1 - \lambda$ are truth-tellers. *Lies* has no
+interpretation in the population, because the rest of the population has no chance to tell a lie in
+the experiment.
+
+*Lies* can be treated as an estimate of $\lambda$. It is unbiased: it estimates $\lambda$ from the
+random, and randomly-sized, sample of $N - T$ people who saw tails. But it can be a very noisy
+estimate. Again, suppose 10 heads out of 10 are reported, and 9 heads were really observed. *Lies*
+is 100%. But it is 100% of just one person.
+
+This means that even the correct confidence intervals for *Lies* would not be correct for $\lambda$.
+For example, if 3 out of 3 subjects report heads, the GSV software reports a lower bound of 100% for
+any confidence interval. Indeed, since anyone who had the opportunity to lie clearly did so, this is
+the correct lower bound (if we arbitrarily define *Lies = 1* when $T = N$). But it
+makes no sense as a confidence interval for $\lambda$: we clearly can't rule out that one or two
+subjects truly saw heads, and would have reported tails if they had seen tails.
+
+```{r disagg-coverage}
+
+disagg <- sim_est %>% 
+      filter(method=="gsv") %>% 
+      group_by(
+        `R/N:` = R/N, N, P, CI
+      ) %>% 
+      summarize(mean_in_ci = mean(within_ci, na.rm = TRUE), prop = n()/nrow(.)) %>% 
+      mutate(CI = paste0("CI ", CI, "%")) %>% 
+      spread(CI, mean_in_ci) %>% 
+      mutate(ok  = `CI 95%` > 0.95)
+
+prop_ok <- disagg %>%  
+      ungroup() %>% 
+      summarize(prop_ok = sum(prop[ok])) %>% 
+      pull(prop_ok)
+```
+
+Because of this problem, the GSV confidence interval coverage of $\lambda$ is much worse
+than its coverage of *Lies*.The issue is especially serious when there are many reports of heads. In
+this case there were probably many true heads, so *T* is high and the true sample size $N - T$ is
+low, making *Lies* a noisy estimate of $\lambda$. Table \ref{tab:coverage-rn} shows this. It splits
+the simulations by the proportion of reported heads, *R/N*. GSV coverage levels fall off sharply as
+*R/N* increases. Note that for fair coin flips, *R/N* is usually greater than 0.5, both in the
+simulations and in reality.
+
+```{r coverage-rn}
+coverage_rn <- sim_est %>% 
+      filter(method=="gsv") %>% 
+      group_by(
+        `R/N` = factor(Hmisc::cut2(R/N, cuts = c(0, 1/4, 1/2, 3/4, 1)))      
+      ) %>% 
+      mutate(pct_cases = n()/nrow(.)) %>% 
+      group_by(`R/N`, CI) %>% 
+      summarize(
+        mean_in_ci  = mean(within_ci, na.rm = TRUE), 
+        `Percentage of simulations` = pct_cases[1]
+      ) %>% 
+      mutate(CI = paste0("CI ", CI, "%")) %>% 
+      spread(CI, mean_in_ci)
+
+as_huxtable(coverage_rn, add_colnames = TRUE) %>% 
+      set_caption("GSV confidence interval coverage by proportion of heads reported ($R/N$)") %>% 
+      set_label("tab:coverage-rn") %>% 
+      set_escape_contents(2:3, 1, FALSE) %>% 
+      set_number_format(-1, -1, list(pct_format)) %>% 
+      theme_plain() %>% 
+      set_right_border(-1, 2, 0.4) %>% 
+      set_width(0.75)
+```
 
@@
 
-We can also compare the accuracy of point estimates of *Liars*. Table \ref{tab:bias} shows bias
-(the estimated value minus the true value of $\lambda$) for different methods by different *N*.
-The Bayesian method is always the least biased until $N = 500$, and the GSV method is the most biased.
-
-Table \ref{tab:mse} shows the mean squared error for methods by different *N*. For low *N*,
-the best method is Bayesian and the worst is Frequentist, with GSV in between. When *N* gets large all
+We can also compare the accuracy of point estimates of $\lambda$ between GSV, Frequentist and
+Bayesian methods. Table \ref{tab:bias} shows bias (the estimated value minus the true value of
+$\lambda$) for different methods by different *N*. The Bayesian method is always the least biased
+until $N = 500$, and the GSV method is the most biased.
+
+Table \ref{tab:mse} shows the mean squared error for methods by different *N*. For low *N*, the best
+method is Bayesian and the worst is Frequentist, with GSV in between. When *N* gets large all
 methods give about the same estimates and are equally accurate.
@@
 80%.^[When *L/N = 1*, all subjects deterministically report heads, and both Frequentist and
-Bayesian point estimates are exactly correct.] So, the Bayesian method is likely to be best unless
+GSV point estimates are exactly correct.] So, the Bayesian method is likely to be best unless
 one is sure that the true *L/N* is rather high.
@@
 
-# Power tests
-
-```{r power-tests}
-power_l_25 <- power_calc(N = 100, P = 0.5, lambda = 0.25)
-power_l_10 <- power_calc(N = 100, P = 0.5, lambda = 0.10)
-```
-
-GSV argue that existing sample sizes may be too small to reject "no lying" ($\lambda = 0$). 
-We can check this with the Bayesian method by simulations. With a uniform prior and an $N$ of 100, 
-the Bayesian method has `r pct_format(power_l_25)` power to detect $\lambda$ of 25% and 
-`r pct_format(power_l_10)` power to detect $\lambda$ of 10%. So, on this we agree.
-
-# Empirical Bayes
+# Comparing different groups
 
@@
 
-```{r hj-data}
-
-load("honesty.RData")
-dfr <- dfr %>% 
-      filter(heads %in% 1:2, ! is.na(resnat) , age %in% 2:6)
-
-nats <- dfr %>%  
-      group_by(resnat) %>% 
-      summarize(
-        heads = sum(heads==1), 
-        N = n(),
-        prop_heads = heads/N,
-        prop_liars = 2*prop_heads - 1
-      )
-
-pp <- suppressWarnings(MASS::fitdistr(nats$prop_liars, "beta", start = list(
-        shape1 = 1, shape2 = 1
-      )))
-pooled_prior <- function (x) dbeta(x, pp$estimate["shape1"], pp$estimate["shape2"])
-
-distribs <- apply(nats[, c("heads", "N")], 1, function (r) {
-  N <- r["N"]
-  update_prior(
-      heads = r["heads"],
-      N = N,
-      P = 0.5, 
-      prior = pooled_prior
-  )
-})
-
-names(distribs) <- nats$resnat
-
-nat_means <- sapply(distribs, dist_mean)
-nat_cis <- sapply(distribs, dist_hdr, conf_level = 0.95)
-rownames(nat_cis) <- c("ci.low", "ci.high")
-
-nats <- cbind(nats, t(nat_cis), mean = nat_means)
-
-nats %<>% arrange(mean)
-
-# nats$resnat <- factor(nats$resnat, levels = nats$resnat)
-```
-
-For example, @hugh2016honesty estimates the dishonesty rates of 15 nations using a coin flip
-experiment. We can fit a beta distribution using the 15 observations of *2R/N - 1*. This will be
-our prior.
-
-```{r hj2016-pic, fig.cap = "Posterior means and confidence intervals for proportion dishonest in 15 countries. Crosses are naïve estimates.", fig.align="center", fig.width=5.5, fig.height=4}
-
-ggplot(nats, aes(x = factor(resnat, levels = resnat), y = mean, fill = mean)) +
-      geom_col(alpha = 0.8) +
-      geom_linerange(aes(ymin = ci.low,ymax = ci.high)) +
-      geom_point(aes(y = prop_liars), shape = 4, size = 3, colour = "red") +
-      xlab("Nation") + ylab("Prop. liars") +
-      scale_fill_viridis_c(option = "A", guide = "none") + 
-      theme_light()+
-      coord_flip()
-
-```
-
-Results are shown in Figure \ref{fig:hj2016-pic}, with means and 95% confidence intervals. There is
-some "shrinkage" towards the pooled mean from the naïve per-country estimates found by calculating
-*2R/N - 1* separately for each country). One of the strengths of empirical Bayes,  as
-@casella1985introduction points out, is that it "anticipates regression to the mean". That is, as
-there is noise in the data, the most and least honest groups in the data probably had some extreme
-error terms. So the British people in the sample may be less honest, and the Chinese people more
-honest, than the per-group data suggest.
-
-# Bayesian hypothesis testing
-
 We can also test hypotheses using the Bayesian approach. If two samples are independent, then the 
 probability that e.g. the true proportion of liars in sample 1 is smaller than in sample 2 can be
-calculated from the marginal distributions in each sample:
-
-\[
+calculated from the posterior distributions for each sample:
+
+\begin{equation}
+\label{eqn:hypothesis-testing}
 \int^1_0 \int_0^{\lambda_1} \phi(\lambda_1)\phi(\lambda_2) \; \mathrm{d}\lambda_2 \mathrm{d}\lambda_1
-\]
-
-Table \ref{tab:country-comparisons} shows Bayesian comparisons for selected countries. Even though
-estimates have "shrunk" towards the pooled mean from the naive estimates, differences remain
-significant, partly because the pooled prior has made posterior confidence intervals narrower.
-Similarly, we can calculate the full distribution of the differences between countries.
-
-```{r country-comparisons}
-
-prob_country_more <- function (ctry1, ctry2) {
-  compare_dists(distribs[[ctry1]], distribs[[ctry2]])
-}
-
-ctry_comp <- outer(nats$resnat, nats$resnat, Vectorize(prob_country_more))
-diag(ctry_comp) <- NA
-rownames(ctry_comp) <- nats$resnat
-colnames(ctry_comp) <- nats$resnat
-
-selected <- c("GB", "ZA", "GR", "BR", "CN")
-ctry_comp <- ctry_comp[selected, selected]
-cc_hux <- as_huxtable(ctry_comp, add_colnames = TRUE, add_rownames = TRUE) %>% 
-      set_caption("Bayesian country comparisons. 
-            Cells give the probability that the row country has higher proportion of liars.") %>% 
-      set_label("tab:country-comparisons") %>% 
-      set_na_string("--") %>% 
-      set_number_format("%.3f") %>% 
-      set_align(-1, -1, ".") %>% 
-      theme_plain() %>% 
-      set_bold(everywhere, 1, TRUE)
-
-cc_hux[1, 1] <- ''
-
-cc_hux
-
-```
-
-```{r GB-vs-RU-pic, fig.cap = "Probability distribution of difference in proportion of liars, GB vs RU", fig.width=4, fig.height=3, fig.align="left", eval = FALSE}
-
-diff_GB_RU <- difference_dist(distribs$GB, distribs$RU)
-curve(diff_GB_RU, xlim = c(-1, 1), ylab = "Density", xlab = expression(lambda[GB] - lambda[RU]))
-```
-
-```{r banerjee-recalc, cache = cache_results}
-
-paste_combn <- function (x, y, flip = FALSE) {
- res <- outer(x, y, FUN = paste0)
- if (! flip) res <- t(res)
- c(res)
-}
-
-sigstar <- function (x) {
-  symnum(x, corr = FALSE, 
-          cutpoints = c(0, .001, .01, .05, 1),
-          symbols = c("***", "**", "*", "")
-        )
-}
-
-treats <- paste_combn(c("T1", "T2", "T2-winners", "T2-losers"), c("-GC-", "-SC-"))
-treats <- paste_combn(treats, c("Same", "Other"))
-treats <- c("T0-GC-Same", "T0-SC-Same", treats)
-treats <- paste_combn(treats, c("-Aligned", "-Unaligned"), flip = TRUE)
-
-banerjee <- data.frame(
-  Treatment = treats,
-  N       = c(84, 84, rep(c(43, 41, 41, 43, 12,  17, 33, 22), each = 2),
-              90, 78, rep(c(42, 42, 40, 44, 12, 15, 32, 28), each = 2)),
-  pct_gt3 = c(77.38, 77.38, 83.72, 65.12, 80.49, 73.17, 75.61, 53.66, 88.37, 81.40, 58.33, 50.00, 
-              70.59, 52.94, 87.88, 45.45, 68.18, 72.73,
-              68.89, 66.67, 57.14, 73.81, 57.14, 66.67, 60.0, 77.5, 56.82, 59.09, 33.33, 41.67,
-              40.00, 73.33, 53.12, 93.75, 60.71, 75.00
-            )
-)
-
-banerjee %<>% mutate(
-        N_gt3 = round(pct_gt3/100*N, 0)
-      ) %>% 
-      extract(Treatment, c("Treatment", "Target", "Payoffs"), regex = "(.*)-([:alnum:]+)-([:alnum:]+)")
-
-banerjee_gsv_cis <- apply(banerjee %>% select(N_gt3, N), 1, function(x) {
-  prop_liars_ci_gsv(0.95, x["N_gt3"], x["N"], 0.5)
-})
-
-rownames(banerjee_gsv_cis) <- c("gsv_lo", "gsv_hi")
-banerjee %<>% cbind(t(round(banerjee_gsv_cis, 2) * 100))
-
-# didn't converge to give finite density at 0!
-# pp <- suppressWarnings(MASS::fitdistr(pmax(0.03, 2 * banerjee$N_gt3/banerjee$N - 1), "beta", start = list(
-#         shape1 = 1, shape2 = 1
-#       )))
-# pooled_prior <- function (x) dbeta(x, pp$estimate["shape1"], pp$estimate["shape2"])
-
-banerjee_bayes_cis  <- apply(banerjee %>% select(N_gt3, N), 1, function(x) {
-  pstr <- update_prior(x["N_gt3"], x["N"], 0.5, prior = dunif)
-  dist_hdr(pstr, 0.95)
-})
-
-rownames(banerjee_bayes_cis) <- c("bayes_lo", "bayes_hi")
-banerjee %<>% cbind(t(round(banerjee_bayes_cis, 2) * 100))
-
-bj_wide <- banerjee %>% 
-      reshape2::melt(id.vars = c("Treatment", "Target", "Payoffs")) %>% 
-      reshape2::dcast(Treatment + Payoffs ~ ...)
-
-same_other_p <- apply(bj_wide %>% select(matches("(Other|Same)_N")), 1, function (x) {
-  if (is.na(x["Other_N_gt3"])) return(rep(NA, 2))
-  pstr_other <- update_prior(x["Other_N_gt3"], x["Other_N"], 0.5, prior = dunif)
-  pstr_same <- update_prior(x["Same_N_gt3"], x["Same_N"], 0.5, prior = dunif)
-  diff_dist <- difference_dist(pstr_other, pstr_same)
-  dist_hdr(diff_dist, 0.95, bounds = c(-1, 1))
-})
-
-rownames(same_other_p) <- c("diff_lo", "diff_hi")
-same_other_p <- t(same_other_p)
-bj_wide %<>% cbind(same_other_p)
-bj_wide %<>% select(Treatment, Payoffs, diff_lo, diff_hi)
-
-banerjee %<>% left_join(bj_wide, by = c("Treatment", "Payoffs"))
-banerjee %<>% mutate(
-        GSV_CIs      = sprintf("%s -- %s", gsv_lo, gsv_hi),
-        Bayesian_CIs = sprintf("%s -- %s", bayes_lo, bayes_hi),
-        diff_ci      = ifelse(is.na(diff_lo), "", 
-                               sprintf("%.0f -- %.0f", diff_lo * 100, diff_hi * 100)),
-        diff_ci      = ifelse(diff_lo > 0 | diff_hi < 0, paste(diff_ci, "*"), diff_ci )
-      )
-```
-
-```{r banerjee-recalc-table}
-
-group_cols <- c("Treatment", "Payoffs", "Diff. 95% CI", "N")
-banerjee %>% 
-      select(
-        Treatment,
-        Payoffs,
-        Target,
-        "Pct > 3"        = pct_gt3, 
-        N, 
-        "GSV 95% CI"   = `GSV_CIs`, 
-        "Bayes 95% CI" = `Bayesian_CIs`,
-        "Diff. 95% CI" = `diff_ci`
-      ) %>%
-      as_huxtable(add_colnames = TRUE) %>% 
-      set_rowspan(evens, group_cols, 2) %>% 
-      set_rowspan(grepl("T0", banerjee$Treatment), group_cols, 1) %>% 
-      set_all_border_colors("grey70") %>% 
-      theme_plain() %>% 
-      set_top_border(evens, everywhere, 0.4) %>%
-      set_bottom_border(evens, group_cols, 0.4) %>%
-      set_bottom_border(grepl("T0", banerjee$Treatment), group_cols, 0) %>%
-      set_valign(everywhere, group_cols, "middle") %>% 
-      set_background_color(NA) %>% 
-      set_top_padding(8) %>% 
-      set_bottom_padding(4) %>% 
-      set_font_size(10) %>% 
-      set_caption("Confidence intervals from Banerjee et al. 2018, original and recalculated") %>% 
-      set_label("tab:banerjee-recalc")
-
-```
+\end{equation}
+
+# Applications
+
+```{r benndorf-recalc}
+bennd <- update_prior(57, 98, 5/6, dunif)
+bennd_bounds <- dist_hdr(bennd, 0.95)
+bennd_bounds <- pct_format(bennd_bounds)
+bennd_trad <- binom.test(57, 98)$conf.int
+bennd_trad <- pct_format(bennd_trad)
+```
+
+@benndorf2017experienced use the GSV method to calculate confidence intervals for the proportion of
+liars in a lying task with a die roll ($P = 5/6$). From 57 reports of the best outcome, out of 98
+subjects, they calculate a lying rate of 49.68%, with a 95% CI of (45.3%, 53.95%). Using the
+Bayesian method with a uniform prior, the confidence interval becomes (`r bennd_bounds[1]`, 
+`r bennd_bounds[2]`), about twice as big.
 
 @banerjee2018spillover use the GSV method to estimate confidence intervals for proportion of liars
-in a die roll task. They estimate the proportion of liars who report a die roll above 3 
-($P = 0.5$), for several treatments. Table \ref{tab:banerjee-recalc} shows GSV confidence intervals,
-along with recalculated Bayesian confidence intervals, and confidence intervals for the difference
-between lying to the "Same" and "Other" caste. Here, I used a non-informative prior rather than
-a pooled prior, letting the algorithm maintain an "open mind" about treatment effects.
-
-The Bayesian confidence intervals are much larger
-than GSV confidence intervals. Only a couple of significant results survive. (Note that
-significance tests in the original paper were done with standard frequentist techniques, not the
-GSV method.) More importantly, it is clear that the N is rather low to make useful inferences
-about the differences between groups. For example, for the T2-winners-GC group in the "aligned
-payoffs" treatment, differences in lying could be as much as 40% in either direction.
+in a die roll task. They estimate the proportion of liars who report a die roll above 3 ($P = 0.5$),
+for several treatments. Table \ref{tab:banerjee-recalc} in the appendix shows GSV confidence
+intervals, along with recalculated Bayesian confidence intervals (from a uniform prior), and
+confidence intervals for the difference between lying to the "Same" and "Other" caste. The Bayesian
+confidence intervals are much larger than GSV confidence intervals. Only a couple of significant
+results survive. (Note that significance tests in the original paper were done with standard
+frequentist techniques, not the GSV method.) More importantly, the N is rather low
+to make useful inferences about the differences between groups. For example, for the T2-winners-GC
+group in the "aligned payoffs" treatment, differences in lying could be as much as 40% in either
+direction.
+
+@hugh2016honesty estimates the dishonesty rates of 15 nations using a coin flip experiment. I use
+empirical Bayes to check these results. For my prior over $\lambda$, I fit a beta distribution
+using the 15 observations of *2R/N - 1*. I then updated this prior separately for each country to
+find new confidence intervals and point estimates of the means.^[Results available on request.]
+There is some "shrinkage" towards the pooled mean from the naïve per-country estimates found by
+calculating *2R/N - 1* separately for each country. One of the strengths of empirical Bayes, as
+@casella1985introduction points out, is that it "anticipates regression to the mean". Using equation
+(\ref{eqn:hypothesis-testing}), I calculated the probability of different $\lambda$ values for
+each pair of countries in the data. Reassuringly, there were still significant differences between
+countries.
+
+# Software
+
+The Bayesian methods described here are implemented in R code, available at https://github.com/hughjonesd/GSV-comment. In this section I give some simple examples of how
+to use it. More details are available at the website.
+
+To load the code, download the file "bayesian-heads-cts.R" from github, and source it in the R
+command line:
+
+```{r code-example-1, eval = FALSE, echo = TRUE}
+source("bayesian-heads-cts.R")
+```
+
+Suppose 33 people report heads out of an N of 50, where the probability of the bad outcome is 0.5.
+To create a posterior distribution over $\lambda$, we use the `update_prior()` function:
+
+```{r code-example-2, echo = TRUE}
+updated <- update_prior(heads = 33, N = 50, P = 0.5, prior = dunif)
+```
+
+Here we've started with a uniform prior, using  R's builtin `dunif()` function.
+
+To calculate the point estimate of lambda, call the `dist_mean()` function on the updated posterior:
+
+```{r code-example-3, echo = TRUE}
+dist_mean(updated)
+```
+
+To calculate the 95% confidence interval (the highest density region), use `dist_hdr()`:
+
+```{r code-example-4, echo = TRUE}
+dist_hdr(updated, 0.95)
+```
+
+```{r power-tests}
+power_l_25 <- power_calc(N = 100, P = 0.5, lambda = 0.25, nsims = 500)
+power_l_10 <- power_calc(N = 100, P = 0.5, lambda = 0.10, nsims = 500)
+```
+
+Lastly, we can run power tests by simulating multiple experiments. GSV argue that existing sample
+sizes may be too small to reject "no lying" ($\lambda = 0$). With a uniform prior and an $N$ of 100,
+the Bayesian method has `r pct_format(power_l_25)` power to detect $\lambda$ of 25% and 
+`r pct_format(power_l_10)` power to detect $\lambda$ of 10%. So, this paper confirms that important
+point. To run power calculations, use `power_calc()`. Here, we calculate the power to detect
+$\lambda = 0.1$ in a sample of 300, where the probability of the bad outcome is 0.5, with an alpha
+level of 0.05 and a uniform prior:
+
+```{r code-example-5, echo = TRUE}
+power_calc(N = 300, P = 0.5, lambda = 0.1, prior = dunif, alpha = 0.05)
+```
 
@@
 
-These results suggest some recommendations when you are analysing a coin-flip
+These results suggest some recommendations when designing and analysing a coin-flip
 style experiment.
 
-1. Do not use the GSV method. Confidence intervals are always too narrow, risking false inferences.
+1. Use power tests to ensure your N is big enough.
 
@@
 
-Lastly, here is a simple experimental design to avoid these statistical shenanigans. Ask a group of *N*
-experimental subjects, not to flip a coin, but to draw a black or white ball, without replacement,
-from an urn containing *N* balls, of which *T* are white. Pay them if they report a white ball. You
-will then know -- not estimate -- that the proportion of lies told is $(R - T)/(N - T)$, and this
-will also be the proportion of liars, in a sample of exactly $N - T$ subjects. You can compare
-different samples, or test for no lying, using a straightforward chi-squared test.
-So, you can simultaneously estimate the proportion of lies, and of the lying liars who tell them.
+Lastly, here is an idea for a simple experimental design to avoid these statistical shenanigans. Ask a
+group of *N* experimental subjects, not to flip a coin, but to draw a black or white ball, without
+replacement, from an urn containing *N* balls, of which *T* are white. Pay them if they report a
+white ball. (Obviously, don't let them observe previous draws.) You will then know -- not estimate --
+that the proportion of lies told is $(R - T)/(N - T)$, and this will also be the proportion of
+liars, in a sample of exactly $N - T$ subjects. You can compare different samples, or test for no
+lying, with a straightforward chi-squared test. The experimenter now knows exactly the
+number of liars, and subjects will understand this, which may change the incentives to lie
+ (maybe subjects don't like giving the experimenter certain knowledge that somebody lied).
+But it simplifies the statistics. This design allows the experimenter to learn the exact proportion 
+of lies, and the lying liars who tell them.
 
@@
 
-scale_colour_methods <- scale_color_brewer(type = "qual", palette = 2)
+scale_colour_methods <- scale_color_brewer(type = "qual", palette = 2, 
+      aesthetics = c("colour", "fill"))
 ```
@@
 
-ggplot(bias_lambda, aes(Method, Bias, colour = Method)) + 
-      geom_point() + scale_x_discrete(breaks = NULL) +
+ggplot(bias_lambda, aes(Method, Bias, fill = Method)) + 
+      geom_col() + scale_x_discrete(breaks = NULL) +
       facet_grid(N ~ P, labeller = "label_both", scales = "free") +
@@
 
+## Banerjee et al. results
+
+Table \ref{tab:banerjee-recalc} recalculates confidence intervals from @banerjee2018spillover using
+data in their Tables 6A and 6B.
+
+```{r banerjee-recalc, cache = cache_results}
+
+paste_combn <- function (x, y, flip = FALSE) {
+ res <- outer(x, y, FUN = paste0)
+ if (! flip) res <- t(res)
+ c(res)
+}
+
+sigstar <- function (x) {
+  symnum(x, corr = FALSE, 
+          cutpoints = c(0, .001, .01, .05, 1),
+          symbols = c("***", "**", "*", "")
+        )
+}
+
+treats <- paste_combn(c("T1", "T2", "T2-winners", "T2-losers"), c("-GC-", "-SC-"))
+treats <- paste_combn(treats, c("Same", "Other"))
+treats <- c("T0-GC-Same", "T0-SC-Same", treats)
+treats <- paste_combn(treats, c("-Aligned", "-Unaligned"), flip = TRUE)
+
+banerjee <- data.frame(
+  Treatment = treats,
+  N       = c(84, 84, rep(c(43, 41, 41, 43, 12,  17, 33, 22), each = 2),
+              90, 78, rep(c(42, 42, 40, 44, 12, 15, 32, 28), each = 2)),
+  pct_gt3 = c(77.38, 77.38, 83.72, 65.12, 80.49, 73.17, 75.61, 53.66, 88.37, 81.40, 58.33, 50.00, 
+              70.59, 52.94, 87.88, 45.45, 68.18, 72.73,
+              68.89, 66.67, 57.14, 73.81, 57.14, 66.67, 60.0, 77.5, 56.82, 59.09, 33.33, 41.67,
+              40.00, 73.33, 53.12, 93.75, 60.71, 75.00
+            )
+)
+
+banerjee %<>% mutate(
+        N_gt3 = round(pct_gt3/100*N, 0)
+      ) %>% 
+      extract(Treatment, c("Treatment", "Target", "Payoffs"), regex = "(.*)-([:alnum:]+)-([:alnum:]+)")
+
+banerjee_gsv_cis <- apply(banerjee %>% select(N_gt3, N), 1, function(x) {
+  prop_liars_ci_gsv(0.95, x["N_gt3"], x["N"], 0.5)
+})
+
+rownames(banerjee_gsv_cis) <- c("gsv_lo", "gsv_hi")
+banerjee %<>% cbind(t(round(banerjee_gsv_cis, 2) * 100))
+
+# didn't converge to give finite density at 0!
+# pp <- suppressWarnings(MASS::fitdistr(pmax(0.03, 2 * banerjee$N_gt3/banerjee$N - 1), "beta", start = list(
+#         shape1 = 1, shape2 = 1
+#       )))
+# pooled_prior <- function (x) dbeta(x, pp$estimate["shape1"], pp$estimate["shape2"])
+
+banerjee_bayes_cis  <- apply(banerjee %>% select(N_gt3, N), 1, function(x) {
+  pstr <- update_prior(x["N_gt3"], x["N"], 0.5, prior = dunif)
+  dist_hdr(pstr, 0.95)
+})
+
+rownames(banerjee_bayes_cis) <- c("bayes_lo", "bayes_hi")
+banerjee %<>% cbind(t(round(banerjee_bayes_cis, 2) * 100))
+
+bj_wide <- banerjee %>% 
+      reshape2::melt(id.vars = c("Treatment", "Target", "Payoffs")) %>% 
+      reshape2::dcast(Treatment + Payoffs ~ ...)
+
+same_other_p <- apply(bj_wide %>% select(matches("(Other|Same)_N")), 1, function (x) {
+  if (is.na(x["Other_N_gt3"])) return(rep(NA, 2))
+  pstr_other <- update_prior(x["Other_N_gt3"], x["Other_N"], 0.5, prior = dunif)
+  pstr_same <- update_prior(x["Same_N_gt3"], x["Same_N"], 0.5, prior = dunif)
+  diff_dist <- difference_dist(pstr_other, pstr_same)
+  dist_hdr(diff_dist, 0.95, bounds = c(-1, 1))
+})
+
+rownames(same_other_p) <- c("diff_lo", "diff_hi")
+same_other_p <- t(same_other_p)
+bj_wide %<>% cbind(same_other_p)
+bj_wide %<>% select(Treatment, Payoffs, diff_lo, diff_hi)
+
+banerjee %<>% left_join(bj_wide, by = c("Treatment", "Payoffs"))
+banerjee %<>% mutate(
+        GSV_CIs      = sprintf("%s -- %s", gsv_lo, gsv_hi),
+        Bayesian_CIs = sprintf("%s -- %s", bayes_lo, bayes_hi),
+        diff_ci      = ifelse(is.na(diff_lo), "", 
+                               sprintf("%.0f -- %.0f", diff_lo * 100, diff_hi * 100)),
+        diff_ci      = ifelse(diff_lo > 0 | diff_hi < 0, paste(diff_ci, "*"), diff_ci )
+      )
+```
+
+```{r banerjee-recalc-table}
+
+group_cols <- c("Treatment", "Payoffs", "Diff. 95% CI", "N")
+banerjee %>% 
+      select(
+        Treatment,
+        Payoffs,
+        Target,
+        "Pct > 3"        = pct_gt3, 
+        N, 
+        "GSV 95% CI"   = `GSV_CIs`, 
+        "Bayes 95% CI" = `Bayesian_CIs`,
+        "Diff. 95% CI" = `diff_ci`
+      ) %>%
+      as_huxtable(add_colnames = TRUE) %>% 
+      set_rowspan(evens, group_cols, 2) %>% 
+      set_rowspan(grepl("T0", banerjee$Treatment), group_cols, 1) %>% 
+      set_all_border_colors("grey70") %>% 
+      theme_plain() %>% 
+      set_top_border(evens, everywhere, 0.4) %>%
+      set_bottom_border(evens, group_cols, 0.4) %>%
+      set_bottom_border(grepl("T0", banerjee$Treatment), group_cols, 0) %>%
+      set_valign(everywhere, group_cols, "middle") %>% 
+      set_background_color(NA) %>% 
+      set_top_padding(8) %>% 
+      set_bottom_padding(4) %>% 
+      set_font_size(10) %>% 
+      set_caption("Confidence intervals from Banerjee et al. 2018, original and recalculated") %>% 
+      set_label("tab:banerjee-recalc")
+
+```
+
 \FloatBarrier

### 2019-03-01 response-to-reviewers.Rmd
final commits before submitting revision

@@
 ---
-title: "Untitled"
+title: "True Lies: Response to Reviewers"
 author: "David Hugh-Jones"
@@
 
+Dear Nikos,
+
+Thank you for the chance to revise this manuscript. I here respond to your comments and those of 
+both reviewers.
+
 > The most obvious comment that both reviewers made is one of etiquette: you are unnecessarily harsh
@@
 
-[TODO]
+I have tried to be nicer, while simultaneously making it clear that using GSV is not a good idea.
+I've changed my conclusion.
 
 > I also like R2’s suggestion about either providing power calculations (see the example table this
-> reviewer provided) and/or an online calculator that you will discuss in your paper. Finally, please
+> reviewer provided) and/or an online calculator that you will discuss in your paper.
+
+I now give examples of how to use my freely available R software to do power calculations,
+and to analyse data from experiments.
+
+> Finally, please
 > ensure that you address R1’s comments on clarity.
 
-[Already in software]
+I have done my best. See below.
 
-* Reviewer 1
+With best wishes,
 
-> I think that the statistical argument could be explained more clearly... I would encourage the 
-> author to expand this part of the paper to explain things more clearly.
+David Hugh-Jones
 
-[Use bits of R1's example]
+# Reviewer 1
 
-I also think that it would be important to explain more clearly how the statistical and conceptual arguments relate to the lack of nominal coverage of the estimator and its biasedness.
-This is not very clear at the moment - I am referring in particular to the last four paragraphs of page 4.
-In particular, I struggle to see how the two arguments can help explain the poor nominal coverage of the GSV method.
-In those paragraphs, it would also be useful to make a clearer distinction between the GSV method as an estimator of the proportion of lies actually told in the sample ("Lies") - and the problems that arise there; and the method as an estimate of the proportion of liars in the sample ("lambda").
-At the moment the paper goes back and forth between the problems that arise in either case, which is confusing.
+My thanks go to reviewer 1 for his or her useful comments. I respond to individual points below.
 
-This is also true in the following sections ("Alternative methods" and "Point estimates").
-As far as I understand, the exercise here consists in comparing across methods the coverage and point estimates of lambda (this is confusingly referred to as "Liars" in this part of the paper).
-It would be useful to point this out more clearly.
+> I think that the statistical argument could be explained more clearly...
 
-I also thought that the part on "empirical Bayes" is not very well explained.
-Indeed, I wondered whether the inclusion of this section may detract from the overall value of the paper, since it becomes slightly less focused.
-The same goes for table 9 and corresponding text in the paper - it seems that this goes somewhat beyond the scope of the paper - which in my opinion works best as a comment focused on the GSV method, rather than its applications in subsequent papers.
+R1's understanding of the statistical argument is correct. I have given some similar examples. 
+I hope this clarifies the argument, but I am open to further 
+suggestions in case it is still a tough read.
 
-Regarding the conclusions, I liked the prescriptive approach of the paper.
-However, I think that the first precept, "Do not use the GSV method", is perhaps too strong.
-I think that the simulations presented in the paper convinced me that GSV is not a good method to estimate the proportion of liars ("lambda"), espcially in comparison with the alternative methods - but I am less convinced that the method is a terrible estimator of the proportion of lies actually told in the sample ("Lies").
-The simulations in the Appendix do not seem to show a very large bias or dramatic drops in coverage in this case.
-So, in my view, the first precept could perhaps be rephrased as "Do not use the GSV method if you are interested in estimating the proportion of liars in your sample".
+> I also think that it would be important to explain more clearly how the statistical and conceptual
+> arguments relate to the lack of nominal coverage of the estimator and its biasedness. This is not
+> very clear at the moment - I am referring in particular to the last four paragraphs of page 4. In
+> particular, I struggle to see how the two arguments can help explain the poor nominal coverage of
+> the GSV method.
 
-I also liked the thought experiment presented in the concluding section.
-However, one important point to make here is that, in such an experiment, each subject would face a different truthful distribution (and the experiment would not be able to control or observe which subject faced which distribution).
-We know from existing research that the underlying distribution matters for the willingness to lie.
-So this is a caveat to keep in mind when estimating the proportion of lies via this method.
+I've added an example, as follows:
 
-Finally, I have some additional minor comments:
-- p. 1, footnote 1: the acronym GSV is used before it has been explained
-- p. 4: line 33, equation 1 should contain R/N, not R.
-- p. 4, table 3: what does "Percentage of cases" mean?
-- Figure 3 in the Appendix, the horizontal axis is missing
+"For example, if 3 out of 3 subjects report heads, the GSV software reports a lower bound of 100% for
+any confidence interval. Indeed, since anyone who had the opportunity to lie clearly did so, this is
+the correct lower bound (assuming we arbitrarily set *Lies = 1* in the case that $T = N$). But it
+makes no sense as a confidence interval for $\lambda$: we clearly can't rule out that one or two
+subjects truly saw heads, and would have reported tails if they had seen tails."
 
-* Reviewer 2
+> In those paragraphs, it would also be useful to make a clearer distinction between the GSV method as
+> an estimator of the proportion of lies actually told in the sample ("Lies") - and the problems that
+> arise there; and the method as an estimate of the proportion of liars in the sample ("lambda"). At
+> the moment the paper goes back and forth between the problems that arise in either case, which is
+> confusing.
 
-Power Calculations: I believe one area that would be extremely useful for future research would be to provide some power calculations based on your proposed method (either frequentist or Bayesian).
+I've reorganized this section to avoid the back and forth.
 
-[Give example in main paper]
+> This is also true in the following sections ("Alternative methods" and "Point estimates"). As far 
+> as I understand, the exercise here consists in comparing across methods the coverage and point 
+> estimates of lambda (this is confusingly referred to as "Liars" in this part of the paper). 
+> It would be useful to point this out more clearly.
 
-Online Calculator: Another way the paper could be extremely valuable for future researchers would be, like GSV, to provide an online lying calculator so that researchers can easily use your improved method.
-I worry otherwise that while readers might find your paper interesting, if it is not trivial to apply (which I suspect will be the case for many), then they might not use your method.
-I will leave it up to you, but either a stand- alone piece of software, or possibly even a STATA routine if that is possible (which I would think would be preferable).
-In any case, I believe this would be an enormous improvement to the value of your paper (and citations).
+I've corrected the mistaken terminology.
 
-[Maybe turn stuff into R package? Or just put some examples into the main paper.]
+> I also thought that the part on "empirical Bayes" is not very well explained. Indeed, I wondered
+> whether the inclusion of this section may detract from the overall value of the paper, since it
+> becomes slightly less focused. The same goes for table 9 and corresponding text in the paper - it
+> seems that this goes somewhat beyond the scope of the paper - which in my opinion works best as a
+> comment focused on the GSV method, rather than its applications in subsequent papers.
 
-Suggested experiment in the concluding section: While I like the objective of the suggested experiment, I do not think the design works as I think it changes the nature/implication of lying...
-in the second experiment, if a subject gets the white ball but lies and reports black, then there is only one outcome for the experiment: both subjects will report black, and it will be with certainty that the experimenter will know one of the subjects will have lied.
-This seems like it a potentially important difference that could affect the willingness of subjects to lie.
-Having more subjects in the room does not change the basic point that in your proposed setup that any subject that lies will make it clear to the experimenter that someone is lying, whereas in the current approach one subject lying does not guarantee the experimenter will detect lying.
-I see no way to avoid this without some form of deception.
+I have made the empirical Bayes section much shorter, just briefly describing the approach. I've kept
+the discussion of applications, because it is important to point out where the GSV method
+has led researchers astray, but I have now put all this discussion in one place, including a brief
+discussion of empirical Bayes results for Hugh-Jones (2016).
 
-[It's a fair point. Even if the number of white balls is unknown, subjects know the experimenter
-knows. But, in a large session, this is perhaps not a big issue.
-Acknowledge this point in a footnote. But, still worth making the suggestion.]
+> However, I think that the first precept, "Do not use the GSV method", is perhaps too strong. I think
+> that the simulations presented in the paper convinced me that GSV is not a good method to estimate
+> the proportion of liars ("lambda"), espcially in comparison with the alternative methods - but I am
+> less convinced that the method is a terrible estimator of the proportion of lies actually told in
+> the sample ("Lies"). The simulations in the Appendix do not seem to show a very large bias or
+> dramatic drops in coverage in this case.
 
-Tone down the negative attention to GSV, and get directly to your solution.
-Your method is the critical contribution, and make it central.
-Comparisons of the CIs in the simulations make this immediately clear.
-As I mentioned above, I believe that GSV made an important contribution by pointing out the lack of a good statistical inference method for estimating the distribution of lying in the literature, and your contribution is an obvious advance that gets the CIs to be essentially what we would expect.
-Hopefully, researchers in this literature will adopt an appropriate statistical inference.
-The likely two most important practical contributions from GSV is quite notably extended here: many studies likely have been under-powered to find significant differences, and closely related, many null results could thus likely be due to low power.
-Addressing my first two recommendations above (power and a calculator) will help the literature not fall prey to these mistakes.
+I have removed this comment. I still would not use GSV to estimate "Lies". When the number of
+reports is high, confidence intervals remain much too narrow (coverage of 70% or less), even with
+a large N. See Figure 5 in the new paper. The bias is also never better than the naive estimator
+and often worse.
 
-[TODO. Maybe have less on GSV.]
+> I also liked the thought experiment presented in the concluding section. However, one important
+> point to make here is that, in such an experiment, each subject would face a different truthful
+> distribution (and the experiment would not be able to control or observe which subject faced which
+> distribution). We know from existing research that the underlying distribution matters for the
+> willingness to lie. So this is a caveat to keep in mind when estimating the proportion of lies via
+> this method.
+
+I hope I am getting this right: although previous draws change the true distribution, if subjects do
+not observe the outcome of previous draws, then their expectation should always be that they have a
+$T/N$ chance of getting a white ball. See also reviewer 2's comment.
+
+> Finally, I have some additional minor comments:
+
+> - p. 1, footnote 1: the acronym GSV is used before it has been explained
+> - p. 4: line 33, equation 1 should contain R/N, not R.
+
+Fixed.
+
+> - p. 4, table 3: what does "Percentage of cases" mean?
+
+It was the percentage of simulation runs which had e.g. $R/N$ between 0 and 0.25. I
+have clarified this.
+
+> - Figure 3 in the Appendix, the horizontal axis is missing
+
+The x axis serves only to separate Bayesian, Frequentist and GSV methods. I've used a bar 
+chart to lessen any ambiguity.
+
+# Reviewer 2
+
+Thank you to reviewer 2 for his or her helpful suggestions.
+
+> Power Calculations: I believe one area that would be extremely useful for future research would be 
+> to provide some power calculations based on your proposed method (either frequentist or Bayesian).
+
+> Online Calculator: Another way the paper could be extremely valuable for future researchers would 
+> be, like GSV, to provide an online lying calculator so that researchers can easily use your 
+> improved method.
+
+Agreed. My original R software is available online. I now include an example of
+how to use it for power calculations, point estimates, and confidence intervals.
+
+> Suggested experiment in the concluding section: While I like the objective of the suggested
+> experiment, I do not think the design works as I think it changes the nature/implication of lying...
+> in the second experiment, if a subject gets the white ball but lies and reports black, then there is
+> only one outcome for the experiment: both subjects will report black, and it will be with certainty
+> that the experimenter will know one of the subjects will have lied. This seems like it a potentially
+> important difference that could affect the willingness of subjects to lie.
+
+This is a fair point and I don't see a way round this disadvantage either. I think the idea is worth
+floating, but I have pointed out this weakness:
+
+"Because the experimenter now knows exactly the number of liars, and liars themselves will
+understand this, this changes the incentives to lie slightly (maybe subjects don't like giving the
+experimenter certain knowledge that somebody lied)."
+
+> Tone down the negative attention to GSV, and get directly to your solution. Your method is the 
+> critical contribution, and make it central. Comparisons of the CIs in the simulations make this
+> immediately clear.
+
+I am now politer to GSV and focus more on my alternative. I do want to make it clear that GSV 
+confidence intervals are a step backward from what was out there already, and it would be a bad
+idea to use them (I did point this out to the authors in 2016...!) But I now get quickly to the 
+Bayesian method and leave discussion of GSV to later.

### 2019-03-01 GSV-comment-brief.Rmd
final commits before submitting revision

@@
     latex_engine: xelatex
+    keep_tex: true
   tufte::tufte_handout:

### 2019-05-30 GSV-comment-brief.Rmd
changes for revision 2:  - change Liars to lambda  - remove experiment suggestion

@@
 \ref{tab:coverage-allmethods} show that both frequentist and  Bayesian methods mostly achieve the nominal
-confidence level, with more than 90/95/99% of intervals containing the true value of *Liars*. The
+confidence level, with more than 90/95/99% of intervals containing the true value of $\lambda$. The
 exception is the frequentist 99% confidence interval, which is too narrow.
@@
 
-Lastly, here is an idea for a simple experimental design to avoid these statistical shenanigans. Ask a
-group of *N* experimental subjects, not to flip a coin, but to draw a black or white ball, without
-replacement, from an urn containing *N* balls, of which *T* are white. Pay them if they report a
-white ball. (Obviously, don't let them observe previous draws.) You will then know -- not estimate --
-that the proportion of lies told is $(R - T)/(N - T)$, and this will also be the proportion of
-liars, in a sample of exactly $N - T$ subjects. You can compare different samples, or test for no
-lying, with a straightforward chi-squared test. The experimenter now knows exactly the
-number of liars, and subjects will understand this, which may change the incentives to lie
- (maybe subjects don't like giving the experimenter certain knowledge that somebody lied).
-But it simplifies the statistics. This design allows the experimenter to learn the exact proportion 
-of lies, and the lying liars who tell them.
-
 \FloatBarrier
@@
 Figure \ref{fig:errors-by-true-prop} shows mean squared error by estimation method and $\lambda$,
-for *N* of 10 and 50. The Bayesian method is best for all values of *Liars* up to 80%.
+for *N* of 10 and 50. The Bayesian method is best for all values of $\lambda$ up to 80%.
 

### 2019-07-06 bayesian-heads-cts.R
Mention truelies package when bayesian-heads-cts.R is sourced

@@ -4,6 +4,12 @@
 
 library(hdrcde)
 
+message("Code for Bayesian estimation in lying experiments is now available in
+a standalone R package. See https://github.com/hughjonesd/truelies or type
+  install.packages('truelies')
+to install the latest stable version from CRAN.")
+
+
 #' Calculate the probability of observing `heads`
 #' good outcomes out of `N` total outcomes, conditional
 #' on subjects lying with prob `lambda` if they see heads.

### 2019-08-26 GSV-comment-brief.Rmd
Mention truelies package when bayesian-heads-cts.R is sourced
Add DESCRIPTION, remove checkpoint
add binder comment to Rmd file

@@
 # set to TRUE to (re)create the simulations CSV file, then stop:
+# NB: you can't do this within binder AFAIK
 rerun_java <- FALSE
@@
 ci_levels <- c(90L, 95L, 99L)
-
-library(checkpoint)
-checkpoint("2018-11-03", scanForPackages = cache_results)
 
@@
 
-source("bayesian-heads-cts.R")
+suppressMessages(source("bayesian-heads-cts.R"))
 source("GSV-heads.R")

### 2019-08-26 GSV-comment-brief.Rmd
remove Times New Roman from fonts

@@
 fontsize: 12pt
-mainfont: Times New Roman
-mathfont: Times New Roman
 ---
